### 2024-12-15 paper/main.tex
recompiled with updated fig 6

\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

\usepackage{xcolor}

\setcitestyle{notesep={; }}

% supplemental tables
\newcommand{\questions}{1}
\newcommand{\topics}{2}
\newcommand{\matchTab}{3}

% supplemental figures
\newcommand{\topicWordWeights}{1}
\newcommand{\topicWeights}{2}
\newcommand{\forcesCorrs}{3}
\newcommand{\bosCorrs}{4}
\newcommand{\jaccard}{5}
\newcommand{\ldaVsBERT}{6}
\newcommand{\individualKnowledgeMapsA}{7}
\newcommand{\individualKnowledgeMapsB}{8}
\newcommand{\individualKnowledgeMapsC}{9}
\newcommand{\individualLearningMapsA}{10}
\newcommand{\individualLearningMapsB}{11}

\newcommand{\U}{{\fontfamily{serif}\selectfont\ensuremath{\mathrm{U}}}}

% simple command for inline comments
\newcommand{\comment}[1]{}
% italicize section names in \nameref and place in \mbox to prevent bug when
% text is split across lines or pages
\NewCommandCopy{\oldnameref}{\nameref}
\renewcommand{\nameref}[1]{\mbox{\textit{\oldnameref{#1}}}}

\doublespacing
\linenumbers

\title{Text embedding models yield high-resolution insights into conceptual
knowledge from short multiple-choice quizzes}

\author{Paxton C. Fitzpatrick\textsuperscript{1},
Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
Jeremy.R.Manning@Dartmouth.edu}}

\date{}

\begin{document}
\maketitle

\begin{abstract}\noindent We develop a mathematical framework, based on natural
language processing models, for tracking and characterizing the acquisition of
conceptual knowledge. Our approach embeds each concept in a high-dimensional
representation space, where nearby coordinates reflect similar or related
concepts. We test our approach using behavioral data from participants who
answered small sets of multiple-choice quiz questions interleaved between
watching two course videos from the Khan Academy platform. We apply our
framework to the videos' transcripts and the text of the quiz questions to
quantify the content of each moment of video and each quiz question. We use
these embeddings, along with participants' quiz responses, to track how the
learners' knowledge changed after watching each video. Our findings show how a
small set of quiz questions may be used to obtain rich and meaningful
high-resolution insights into what each learner knows, and how their knowledge
changes over time as they learn.

\textbf{Keywords: education, learning, knowledge, concepts, natural language processing}

\end{abstract}

\section*{Introduction}

Suppose that a teacher had access to a complete, tangible ``map'' of everything
a student knows. Defining what such a map might even look like, let alone how it
might be constructed or filled in, is itself a non-trivial problem. But if a
teacher \textit{were} to gain access to such a map, how might it change their
ability to teach that student? Perhaps they might start by checking how well
the student knows the to-be-learned information already, or how much they know
about related concepts. For some students, they could potentially optimize
their teaching efforts to maximize efficiency by focusing primarily on
not-yet-known content. For other students (or other content areas), it might be
more effective to optimize for direct connections between already known content
and new material. Observing how the student's knowledge changed over time, in
response to their teaching, could also help to guide the teacher towards the
most effective strategy for that individual student.

A common approach to assessing a student's knowledge is to present them with a
set of quiz questions, calculate the proportion they answer correctly, and
provide them with feedback in the form of a simple numeric or letter grade.
While such a grade can provide \textit{some} indication of whether the student
has mastered the to-be-learned material, any univariate measure of performance
on a complex task sacrifices certain relevant information, risks conflating
underlying factors, and so on. For example, consider the relative utility of
the theoretical map described above that characterizes a student's knowledge in
detail, versus a single annotation saying that the student answered 85\% of
their quiz questions correctly, or that they received a `B'. Here, we show that
the same quiz data required to compute proportion-correct scores or letter
grades can instead be used to obtain far more detailed insights into what a
student knew at the time they took the quiz.

Designing and building procedures and tools for mapping out knowledge touches
on deep questions about what it means to learn. For example, how do we acquire
conceptual knowledge? Memorizing course lectures or textbook chapters by rote
can lead to the superficial \textit{appearance} of understanding the underlying
content, but achieving true conceptual understanding seems to require something
deeper and richer. Does conceptual understanding entail connecting newly
acquired information to the scaffolding of one's existing knowledge or
experience~\citep{BlayEtal06,CaraMaho03, ConsEtal16, DeacEtal04, SimoEtal04,
HuebWill18}? Or weaving a lecture's atomic elements (e.g., its component words)
into a structured network that describes how those individual elements are
related~\citep{LeeChen22, vanPEtal21}? Conceptual understanding could also
involve building a mental model that transcends the meanings of those
individual atomic elements by reflecting the deeper meaning underlying the
gestalt whole~\citep{Kint70, Macl05, ScotEtal07, TulcEtal23}.

The difference between ``understanding'' and ``memorizing,'' as framed
by researchers in education, cognitive psychology, and cognitive
neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08,
  Macl05}, has profound analogs in the fields of natural language
processing and natural language understanding. For example,
considering the raw contents of a document (e.g., its constituent
symbols, letters, and words) might provide some clues as to what the
document is about, just as memorizing a passage might provide some
ability to answer simple questions about it. However, text embedding
models~\citep[e.g.,][]{LandDuma97, DeerEtal90, BleiEtal03,
  BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20, ViswEtal17} also
attempt to capture the deeper meaning \textit{underlying} those atomic
elements. These models consider not only the co-occurrences of those
elements within and across documents, but (in many cases) also
patterns in how those elements appear across different scales (e.g.,
sentences, paragraphs, chapters, etc.), the temporal and grammatical
properties of the elements, and other high-level characteristics of
how they are used~\citep{Mann23b, Mann21a}.
To be clear, this is not to say that text embedding models themselves
are capable of ``understanding'' deep conceptual meaning in any
traditional sense. But rather, their ability to capture the underlying
\textit{structure} of text documents beyond their surface-level contents
provides a computational framework through which those documents'
deeper conceptual meanings may be quantified, explored, and understood.
According to these models,
the deep conceptual meaning of a document may be captured by a feature
vector in a high-dimensional representation space, wherein nearby
vectors reflect conceptually related documents. A model that succeeds
at capturing an analogue of ``understanding'' is able to assign nearby
feature vectors to two conceptually related documents, \textit{even
  when the specific words contained in those documents have limited
  overlap}. In this way, ``concepts'' are defined implicitly by the
model's geometry~\citep[e.g., how the embedding coordinate of a given
word or document relates to the coordinates of other text
embeddings; ][]{PianHill22}.

Given these insights, what form might a representation of the sum total of a
person's knowledge take? First, we might require a means of
systematically describing or representing (at least some subset of) the nearly infinite set of possible
things a person could know. Second, we might want to account for potential
associations between different concepts. For example, the concepts of ``fish''
and ``water'' might be associated in the sense that fish live in water. Third,
knowledge may have a critical dependency structure, such that knowing about a
particular concept might require first knowing about a set of other concepts.
For example, understanding the concept of a fish swimming in water first
requires understanding what fish and water \textit{are}. Fourth, as we learn,
our ``current state of knowledge'' should change accordingly. Learning new
concepts should both update our characterizations of ``what is known'' and also
unlock any now-satisfied dependencies of those newly learned concepts so that
they are ``tagged'' as available for future learning.

Here we develop a framework for modeling how conceptual knowledge is acquired
during learning. The central idea behind our framework is to use text embedding
models to define the coordinate systems of two maps: a \textit{knowledge
map} that describes the extent to which each concept is currently known, and
a \textit{learning map} that describes changes in knowledge over time. Each
location on these maps represents a single concept, and the maps' geometries
are defined such that related concepts are located nearby in space. We use this
framework to analyze and interpret behavioral data collected from an experiment
that had participants answer sets of multiple-choice questions about a series of
recorded course lectures.

Our primary research goal is to advance our understanding of what it means to
acquire deep, real-world conceptual knowledge. Traditional laboratory
approaches to studying learning and memory (e.g., list-learning studies) often
draw little distinction between memorization and understanding. Instead, these
studies typically focus on whether information is effectively encoded or
retrieved, rather than whether the information is \textit{understood}.
Approaches to studying conceptual learning, such as category learning
experiments, can begin to investigate the distinction between memorization and
understanding, often by training participants to distinguish arbitrary or
random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82,
Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the objective of
real-world training, or learning from life experiences more generally, is often
to develop new knowledge that may be applied in \textit{useful} ways in the
future. In this sense, the gap between modern learning theories and modern
pedagogical approaches that inform classroom learning strategies is enormous:
most of our theories about \textit{how} people learn are inspired by
experimental paradigms and models that have only peripheral relevance to the
kinds of learning that students and teachers actually seek~\citep{Macl05,
HallGree08}. To help bridge this gap, our study uses course materials from real
online courses to inform, fit, and test models of real-world conceptual
learning. We also provide a demonstration of how our models can be used to
construct ``maps'' of what students know, and how their knowledge changes with
training. In addition to helping to visually capture knowledge (and changes in
knowledge), we hope that such maps might lead to real-world tools for improving
how we educate. Taken together, our work shows that existing course materials
and evaluative tools like short multiple-choice quizzes may be leveraged to
gain highly detailed insights into what students know and how they learn.

\section*{Results}

At its core, our main modeling approach is based around a simple assumption
that we sought to test empirically: all else being equal, knowledge about a
given concept is predictive of knowledge about similar or related concepts.
From a geometric perspective, this assumption implies that knowledge is
fundamentally ``smooth.'' In other words, as one moves through a space
representing an individual's knowledge (where similar concepts occupy nearby
coordinates), their ``level of knowledge'' should change relatively gradually.
To begin to test this smoothness assumption, we sought to track participants'
knowledge and how it changed over time in response to training. Two overarching
goals guide our approach. First, we want to gain detailed insights into what
learners know at different points in their training. For example, rather than
simply reporting on the proportions of questions participants answer correctly
(i.e., their overall performance), we seek estimates of their knowledge about a
variety of specific concepts. Second, we want our approach to be potentially
scalable to large numbers of diverse concepts, courses, and students. This
requires that the conceptual content of interest be discovered
\textit{automatically}, rather than relying on manually produced ratings or
labels.

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/experiment}

    \caption{\textbf{Experimental paradigm.} Participants alternate between
    completing three 13-question multiple-choice quizzes and watching two Khan
    Academy lectures. Each quiz contains a mix of 5 questions about Lecture~1,
    5 questions about Lecture~2, and 3 questions about general physics
    knowledge. The specific questions reflected on each quiz, and the orders of
    each quiz's questions, were randomized across participants.}

    \label{fig:experiment}
\end{figure}

We asked participants in our study to complete brief multiple-choice quizzes
before, between, and after watching two lecture videos from the Khan
Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}). The first lecture
video, entitled \textit{Four Fundamental Forces}, discussed the four
fundamental forces in physics: gravity, strong and weak interactions, and
electromagnetism. The second, entitled \textit{Birth of Stars}, provided an
overview of our current understanding of how stars form. We selected these
particular lectures to satisfy three general criteria. First, we wanted both
lectures to be accessible to a broad audience (i.e., with minimal prerequisite
knowledge) so as to limit the impact of prior training on participants'
abilities to learn from the lectures. To this end, we selected two introductory
videos that were intended to be viewed at the start of students' training in
their respective content areas. Second, we wanted the two lectures to have some
related content, so that we could test our approach's ability to distinguish
similar conceptual content. To this end, we chose two videos from the same Khan
Academy course domain, ``Cosmology and Astronomy.'' Third, we sought to
minimize dependencies and specific overlap between the videos. For example, we
did not want participants' abilities to understand one video to (directly)
influence their abilities to understand the other. To satisfy this last
criterion, we chose videos from two different lecture series (Lectures~1 and 2
were from the ``Scale of the Universe'' and ``Stars, Black Holes, and
Galaxies'' series, respectively).

We also wrote a set of multiple-choice quiz questions that we hoped would
enable us to evaluate participants' knowledge about each individual lecture,
along with related knowledge about physics concepts not specifically presented
in either video (see Supp.~Tab.~\questions~for the full list of questions in
our stimulus pool). Participants answered questions randomly drawn from each
content area (Lecture~1, Lecture~2, and general physics knowledge) on each of
the three quizzes. Quiz~1 was intended to assess participants' ``baseline''
knowledge before training, Quiz~2 assessed knowledge after watching the
\textit{Four Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed
knowledge after watching the \textit{Birth of Stars} video (i.e., Lecture~2).

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/sliding_windows}

    \caption{\textbf{Modeling course content.} \textbf{A. Building a document
    pool from sliding windows of text.} We decompose each lecture's transcript
    into a series of overlapping sliding windows. The full set of transcript
    snippets (across all windows) may be treated as a set of ``documents'' for
    training a text embedding model. \textbf{B. Constructing lecture content
    \textit{trajectories}.} After training the model on the sliding windows
    from both lectures, we transform each lecture into a ``trajectory'' through
    text embedding space by joining the embedding coordinates of successive
    sliding windows parsed from its transcript. \textbf{C. Embedding multiple
    lectures and questions in a shared space.} We apply the same model (trained
    on the two lectures' windows) to both lectures, along with the text of each
    question in our pool (Supp.~Tab.~\questions), to project them into a shared
    text embedding space. This results in one trajectory per lecture and one
    coordinate for each question. Here, we have projected the 15-dimensional
    embeddings onto their first 3 principal components for visualization.}

    \label{fig:sliding-windows}
\end{figure}

To study in detail how participants' conceptual knowledge changed over the
course of the experiment, we first sought to model the conceptual content
presented to them at each moment throughout each of the two lectures. We
adapted an approach we developed in prior work~\citep{HeusEtal21} to identify
the latent themes in the lectures using a topic model~\citep{BleiEtal03}.
Briefly, topic models take as input a collection of text documents, and learn a
set of ``topics'' (i.e., latent themes) from their contents. Once fit, a topic
model can be used to transform arbitrary (potentially new) documents into sets
of ``topic proportions,'' describing the weighted blend of learned topics
reflected in their texts. We parsed automatically generated transcripts of the
two lectures into overlapping sliding windows, where each window contained the
text of the lecture transcript from a particular time span. We treated the set
of text snippets (across all of these windows) as documents to fit the model
(Fig.~\ref{fig:sliding-windows}A; see~\nameref{subsec:topic-modeling}).
Transforming the text from every sliding window with the model yielded a
number-of-windows by number-of-topics (15) topic-proportions matrix describing
the unique mixture of broad themes from both lectures reflected in each
window's text. Each window's ``topic vector'' (i.e., column of the
topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
space whose axes are topics discovered by the model. Within this space, each
lecture's sequence of topic vectors (i.e., corresponding to its transcript's
overlapping text snippets across sliding windows) forms a \textit{trajectory}
that captures how its conceptual content unfolds over time
(Fig.~\ref{fig:sliding-windows}B). We resampled these trajectories to a
resolution of one topic vector for each second of video (i.e., 1~Hz).

We hypothesized that a topic model trained on transcripts of the two lectures
should also capture the conceptual knowledge probed by each quiz question. If
indeed the topic model could capture information about the deeper conceptual
content of the lectures (i.e., beyond surface-level details such as particular
word choices), then we should be able to recover a correspondence between each
lecture and questions \textit{about} each lecture. Importantly, such a
correspondence could not solely arise from superficial text matching between
lecture transcripts and questions, since the lectures and questions often used
different words (Supp.~Fig.~\jaccard) and phrasings. Simply comparing the
average topic weights from each lecture and question set (averaging across time
and questions, respectively) reveals a striking correspondence
(Supp.~Fig.~\topicWeights). Specifically, the average topic weights from Lecture~1 are
strongly correlated with the average topic weights from Lecture~1 questions
($r(13) = 0.809,~p < 0.001$, 95\% confidence interval (CI)~$= [0.633,~0.962]$),
and the average topic weights from Lecture~2 are strongly correlated with the
average topic weights from Lecture~2 questions ($r(13) = 0.728,~p = 0.002$,
95\% CI~$= [0.456,~0.920]$). At the same time, the average topic weights from
the two lectures are \textit{negatively} correlated with the average topic weights from their non-matching
question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = -0.547,~p =
0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions:
$r(13) = -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the
topic model also exhibits some degree of specificity. The full set of pairwise
comparisons between average topic weights for the lectures and question sets is
reported in Supplementary Figure~\topicWeights.

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/active-topics}

    \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic
    weight variability}. The bar plots display the variance of each topic's
    weight across lecture timepoints (top row) and questions (bottom row);
    colors denote topics. The top-weighted words from the most ``expressive''
    (i.e., variable across observations) topic from each lecture are displayed
    in the upper right (orange: topic 2; yellow-green: topic 4). The
    top-weighted words from the full set of topics may be found in
    Supplementary Table~\topics. \textbf{B. Relationships between topic weight
    variability.} Pairwise correlations between the distributions of topic
    weight variance for each lecture and question set. Each row and column
    corresponds to a bar plot in Panel A.}

    \label{fig:topics}
\end{figure}

Another, more sensitive, way of summarizing the conceptual content of the
lectures and questions is to look at \textit{variability} in how topics are
weighted over time and across different questions (Fig.~\ref{fig:topics}).
Intuitively, the variability in the expression of a given topic relates to how
much ``information''~\citep{Fish22} the lecture (or question set) reflects
about that topic. For example, suppose a given topic is weighted on heavily
throughout a lecture. That topic might be characteristic of some aspect or
property of the lecture \textit{overall} (conceptual or otherwise), but unless
the topic's weights changed in meaningful ways over time, the topic would be a
poor indicator of any \textit{specific} conceptual content in the lecture. We
therefore also compared the variances in topic weights (across time or
questions) between the lectures and questions. The variability in topic
expression (over time and across questions) was similar for the Lecture~1 video
and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the
Lecture~2 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$=
[0.539,~0.958]$). Simultaneously, as reported in Figure~\ref{fig:topics}B, the
variabilities in topic expression across \textit{different} videos and
lecture-specific questions (i.e., Lecture~1 video vs.~Lecture~2 questions;
Lecture~2 video vs.~Lecture~1 questions) were negatively correlated, and
neither video's topic variability was reliably correlated with the topic
variability across general physics knowledge questions. Taken together, the
analyses reported in Figure~\ref{fig:topics} and Supplementary
Figure~\topicWeights~indicate that a topic model fit to the videos' transcripts
can also reveal correspondences (at a coarse scale) between the lectures and
questions.

While an individual lecture may be organized around a single broad theme at a
coarse scale, at a finer scale, each moment of a lecture typically covers a
narrower range of content. Given the correspondence we found between the
variabilities in topic expression across moments of each lecture and questions
from its corresponding set (Fig.~\ref{fig:topics}), we wondered whether the
text embedding model might additionally capture these conceptual relationships
at a finer scale. For example, if a particular question asks about the content
from one small part of a lecture, we wondered whether the text embeddings could
be used to automatically identify the ``matching'' moment(s) in the lecture. To
explore this, we computed the correlation between each question's topic weights
and the topic weights for each second of its corresponding lecture, and found
that each question appeared to be temporally specific
(Fig.~\ref{fig:question-correlations}). In particular, most questions' topic
vectors were maximally correlated with a well-defined (and relatively narrow)
range of timepoints from their corresponding lectures, and the correlations
fell off sharply outside of that range (Supp.~Figs.~\forcesCorrs,~\bosCorrs).
We also qualitatively examined the best-matching intervals for each question by
comparing the question's text to the transcribed text from the most-correlated parts of the
lectures (Supp.~Tab.~\matchTab). Despite that the questions were excluded from
the text embedding model's training set, in general we found (through manual
inspection) a close correspondence between the conceptual content that each
question probed and the content covered by the best-matching moments of the
lectures. Two representative examples are shown at the bottom of
Figure~\ref{fig:question-correlations}.

\begin{figure}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/lecture-question-similarity}

    \caption{\textbf{Which parts of each lecture are captured by each
    question?} Each panel displays time series plots showing how each question's
    topic vector correlates with each video timepoint's topic vector (Panel
    \textbf{A.}: correlations for the \textit{Four Fundamental Forces} lecture
    and associated questions; Panel \textbf{B.}: correlations for the
    \textit{Birth of Stars} lecture and associated questions). The colors
    denote question identities. The diamonds in each panel denote the moment of
    peak correlation between the indicated question and the lecture trajectory.
    The associated questions' text and snippets of the lectures' transcripts
    from the surrounding 30 seconds, are displayed at the bottom of the
    figure.}

    \label{fig:question-correlations}
\end{figure}

The ability to quantify how much each question is ``asking about'' the content
from each moment of the lectures could enable high-resolution insights into
participants' knowledge. Traditional approaches to estimating how much a
student ``knows'' about the content of a given lecture entail administering some form of assessment (e.g., a quiz) and computing the
proportion of correctly answered questions. But if two students receive
identical scores on such an exam, might our modeling framework help us to gain more
nuanced insights into the \textit{specific} content that each student has
mastered (or failed to master)? For example, a student who misses three
questions that were all about the same concept (e.g., concept $A$) will have
gotten the same \textit{proportion} of questions correct as another student who
missed three questions about three \textit{different} concepts (e.g., $A$, $B$,
and $C$). But if we wanted to help these two students fill in the ``gaps'' in
their understandings, we might do well to focus specifically on concept $A$ for
the first student, but to also add in materials pertaining to concepts $B$ and
$C$ for the second student. In other words, raw ``proportion-correct'' measures
may capture \textit{how much} a student knows, but not \textit{what} they know.
We wondered whether our modeling framework might enable us to (formally and
automatically) infer participants' knowledge at the scale of individual
concepts (e.g., as captured by a single moment of a lecture).

We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
responses to a small set of multiple-choice questions to estimate how much the
participant ``knows'' about the concept reflected by any arbitrary coordinate
$x$ in text embedding space (e.g., the content reflected by any moment in a
lecture they had watched; see \nameref{subsec:traces}). Essentially, the
estimated knowledge at coordinate $x$ is given by the weighted
proportion of quiz questions the participant answered correctly, where the
weights reflect how much each question is ``about'' the content at $x$. When we
apply this approach to estimate the participant's knowledge about the content
presented in each moment of each lecture, we can obtain a detailed time course
describing how much ``knowledge'' that participant has about the content
presented at any part of the lecture. As shown in
Figure~\ref{fig:knowledge-timeseries}A and C, we can apply this approach
separately for the questions from each quiz participants took throughout the
experiment. From just a few questions per quiz (see~\nameref{subsec:traces}),
we obtain a high-resolution snapshot (at the time each quiz was taken) of what
the participants knew about any moment's content, from either of the two
lectures they watched (comprising a total of 1,100 samples across the two
lectures).

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/content-mastery}

    \caption{\textbf{Estimating knowledge about the content presented at each
    moment of each lecture.} \textbf{A. Knowledge about the time-varying
    content of \textit{Four Fundamental Forces}}. Each trace displays the
    weighted proportion of correctly answered questions about the content
    reflected in each moment of the lecture (see \nameref{subsec:traces}),
    using responses from a single quiz (color). The traces are averaged across
    participants. \textbf{B. Average estimated knowledge about \textit{Four
    Fundamental Forces}.} Each bar displays the across-timepoint average
    knowledge, estimated using the responses to one quiz's questions.
    \textbf{C. Knowledge about the time-varying content of \textit{Birth of
    Stars}}. The panel is in the same format as Panel A, but here the knowledge
    estimates are for the moment-by-moment content of the \textit{Birth of
    Stars} lecture. \textbf{D. Average estimated knowledge about \textit{Birth
    of Stars}.} The panel is in the same format as Panel B, but here the
    knowledge estimates are for the content of the \textit{Birth of Stars}
    lecture. All panels: error ribbons and error bars denote 95\% confidence
    intervals, estimated across participants.}

    \label{fig:knowledge-timeseries}
\end{figure}

While the time courses in Figure~\ref{fig:knowledge-timeseries}A and C provide
detailed \textit{estimates} about participants' knowlege, these estimates are
of course only \textit{useful} to the extent that they accurately reflect what
participants actually know. As one sanity check, we anticipated that the
knowledge estimates should reflect a content-specific ``boost'' in
participants' knowledge after watching each lecture. In other words, if
participants learn about each lecture's content upon watching it,
the knowledge estimates should capture that. After watching the \textit{Four
Fundamental Forces} lecture, participants should exhibit more knowledge for the
content of that lecture than they had before, and that knowledge should persist
for the remainder of the experiment. Specifically, knowledge about that
lecture's content should be relatively low when estimated using Quiz~1
responses, but should increase when estimated using Quiz~2 or 3 responses
(Fig.~\ref{fig:knowledge-timeseries}B). Indeed, we found that participants'
estimated knowledge about the content of \textit{Four Fundamental Forces}
was substantially higher on Quiz~2 versus Quiz~1 ($t(49) = 8.764,~p < 0.001$)
and on Quiz~3 versus Quiz~1 ($t(49) = 10.519,~p < 0.001$). We found no reliable
differences in estimated knowledge about that lecture's content on Quiz~2
versus 3 ($t(49) = 0.160,~p = 0.874$). Similarly, we hypothesized (and
subsequently confirmed) that participants should show greater estimated
knowledge about the content of the \textit{Birth of Stars} lecture after
(versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
Specifically, since participants watched that lecture after taking Quiz~2 (but
before Quiz~3), we hypothesized that their knowledge estimates should be
relatively low on Quizzes~1 and 2, but should show a ``boost'' on Quiz~3.
Consistent with this prediction, we found no reliable differences in estimated
knowledge about the \textit{Birth of Stars} lecture content on Quizzes~1 versus
2 ($t(49) = 1.013,~p = 0.316$), but the estimated knowledge was substantially
higher on Quiz~3 versus 2 ($t(49) = 10.561,~p < 0.001$) and Quiz~3 versus 1
($t(49) = 8.969,~p < 0.001$).

If we are able to accurately estimate a participant's knowledge about the
content tested by a given question, our estimates of their knowledge should
carry some predictive information about whether they are likely to answer that
question correctly or incorrectly. We developed a statistical approach to test
this claim. For each quiz question a participant answered, in turn, we used
Equation~\ref{eqn:prop} to estimate their knowledge at the given question's
embedding space coordinate based on other questions that participant answered
on the same quiz. We repeated this for all participants, and for each of the
three quizzes. Then, separately for each quiz, we fit a generalized linear
mixed model (GLMM) with a logistic link function to explain the likelihood of
correctly answering a question as a function of estimated knowledge for its
embedding coordinate, while accounting for random variation among participants
and questions (see \nameref{subsec:glmm}). To assess the predictive value of
the knowledge estimates, we compared each GLMM to an analogous (i.e., nested)
``null'' model that did not consider estimated knowledge using parametric
bootstrap likelihood-ratio tests.

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.75\textwidth]{figs/predict-knowledge-questions}
    \caption{\textbf{Predicting success on held-out questions using estimated
    knowledge.} We used generalized linear mixed models (GLMMs) to model the
    likelihood of correctly answering a quiz question as a function of
    estimated knowledge for its embedding coordinate (see
    \nameref{subsec:glmm}). Separately for each quiz (column), we examined this
    relationship based on three different sets of knowledge estimates:
    knowledge for each question based on all other questions the same
    participant answered on the same quiz (``All questions''; top row),
    knowledge for each question about one lecture based on all other questions
    (from the same participant and quiz) about the \textit{same} lecture
    (``Within-lecture''; middle rows), and knowledge for each question about
    one lecture based on all questions (from the same participant and quiz)
    about the \textit{other} lecture (``Across-lecture''; bottom rows). The
    backgrounds in each panel display kernel density estimates of the relative
    observed proportions of correctly (blue) versus incorrectly (red) answered
    questions, for each level of estimated knowledge along the $x$-axis. The
    black curves display the (population-level) GLMM-predicted probabilities of
    correctly answering a question as a function of estimated knowledge. Error
    ribbons denote 95\% confidence intervals.}

    \label{fig:predictions}
\end{figure}

We carried out three different versions of the analyses described above,
wherein we considered different sources of information in our estimates of
participants' knowledge for each quiz question. First, we estimated knowledge
at each question's embedding coordinate using \textit{all} other questions
answered by the same participant on the same quiz (``All questions'';
Fig.~\ref{fig:predictions}, top row). This test was intended to assess the
overall predictive power of our approach. Second, we estimated knowledge for
each question about a given lecture using only the other questions (from the
same participant and quiz) about that \textit{same} lecture
(``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows). This test was
intended to assess the \textit{specificity} of our approach by asking whether
our predictions could distinguish between questions about different content
covered by the same lecture. Third, we estimated knowledge for each question
about one lecture using only questions (from the same participant and quiz)
about the \textit{other} lecture (``Across-lecture'';
Fig.~\ref{fig:predictions}, bottom rows). This test was intended to assess the
\textit{generalizability} of our approach by asking whether our predictions
held across the content areas of the two lectures.

In performing these analyses, our null hypothesis is that the knowledge
estimates we compute based on the quiz questions' embedding coordinates do
\textit{not} provide useful information about participants' abilities to answer
those questions. What result might we expect to see if this is the case? To
gain an intuition for this scenario, consider the expected outcome if we
carried out these same analyses using a simple proportion-correct measure in
lieu of our knowledge estimates. Suppose a participant correctly answered $n$
out of $q$ questions on a given quiz. If we hold out a single
\textit{correctly} answered question, the proportion of remaining questions
answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a
single \textit{incorrectly} answered question, the proportion of remaining
questions answered correctly would be $\frac{n}{q - 1}$. In this way, the
proportion of correctly answered remaining questions is always \textit{lower}
when the held-out question was answered correctly than when it was answered
incorrectly. Because our knowledge estimates are computed as a weighted version
of this same proportion-correct score (where each held-in question's weight
reflects its embedding-space distance from the held-out question; see
Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
distributed), then we should expect to see this same inverse relationship
between estimated knowledge and performance, on average. On the other hand, if
the spatial relationships among the quiz questions' embeddings \textit{are}
predictive of participants' knowledge about the questions' content, then we
would expect \textit{higher} estimated knowledge for held-out correctly (versus
incorrectly) answered questions.

Before presenting our results, it is worth considering three possible
explanations of why a participant might answer a given question correctly or
incorrectly. One possibility is that the participant simply \textit{guessed}
the answer. A second is that they selected the incorrect answer by mistake,
despite ``knowing'' the correct answer (or vice versa). In both of these
scenarios, the participant's knowledge about the question's content should be
uninformative about their observed response. A third possibility is that the
participant's response reflects their \textit{actual} knowledge about the
question's content. In this case, we \textit{might} expect to see a positive
relationship between the participant's knowledge and their likelihood of
answering the question correctly. However, in order to see this positive
relationship, the participant's knowledge must be structured in a way that is
reflected (at least partially) by the embedding space. In other words, if the
participant's performance reflects their true knowledge, but our text embedding
space does not sufficiently capture the structure of that knowledge, then the
knowledge estimates we generate will not be predictive of the participant's
performance. In the extreme, if the embedding space is completely unstructured
with respect to the content of the quiz questions, then we would expect to see
the negative relationship between estimated knowledge and performance that we
described above.

When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
question based on all other Quiz~1 questions, we observed an outcome consistent
with our null hypothesis: higher estimated knowledge at the embedding
coordinate of a held-out question was associated with a lower likelihood of
answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
\textit{not} provide useful information about participants' Quiz~1 performance
when we aggregated across all question content areas. We speculated that this
might either indicate that the knowledge estimates are uninformative in
general, or about Quiz~1 performance in particular. This would be expected, for
example, if participants were guessing about the answers to the Quiz~1
questions (prior to having watched either lecture). When we repeated this
analysis for Quizzes~2 and~3, we found that higher estimated knowledge
for a given question predicted a \textit{greater} likelihood of answering it correctly
(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
results suggest that our knowledge estimates reliably predict participants'
performance on individual held-out quiz questions, but only after participants
have received at least some training.

We observed a similar pattern of results when used this approach to estimate
participants' knowledge about held-out questions from one lecture using their
performance on other questions from the \textit{same} lecture. Specifically,
for Quiz~1 questions (i.e., prior to watching either), participants' estimated
knowledge for the embedding coordinates of held-out \textit{Four Fundamental
Forces}-related questions estimated using other \textit{Four Fundamental
Forces}-related questions did not reliably predict whether those questions were
answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI}
= [2.091,\ 2.622],\ p = 0.138$). The same was true of knowledge estimates for
held-out \textit{Birth of Stars}-related questions based on other \textit{Birth
of Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\
\textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$). As in our analysis that
included all questions, we speculate that these ``null'' results might reflect
some degree of random guessing on Quiz~1. When we repeated these within-lecture
analyses using questions from Quiz~2 (which participants took immediately after
viewing \textit{Four Fundamental Forces} but prior to viewing \textit{Birth of
Stars}), we found that they now reliably predicted success on \textit{Four
Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\
95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p < 0.001$) but not on
\textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\
95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.054$). Here, we speculate that
participants might have been guessing about the \textit{Birth of Stars} content
(e.g., prior to having watched it), whereas they might have been drawing on
some structured knowledge about the \textit{Four Fundamental Forces} content
(e.g., from having just watched it). When we applied this approach to Quiz~3
responses (given immediately after viewing \textit{Birth of Stars}), we found
that within-lecture knowledge estimates for \textit{Birth of Stars}-related
questions could now reliably predict success on those questions ($OR = 5.467,\
\lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.005$).
However, within-lecture knowledge estimates for \textit{Four Fundamental
Forces} questions answered on Quiz~3 were no longer directly related to the
likelihood of successfully answering them and instead exhibited the inverse
relationship we would expect to arise from unstructured knowledge (with respect
to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\
\textnormal{CI} = [10.695, 23.096],\ p < 0.001$). Speculatively, we suggest
that this may reflect participants forgetting some of the \textit{Four
Fundamental Forces} content (e.g., perhaps in favor of prioritizing encoding
the just-watched \textit{Birth of Stars} content in preparation for the third
quiz). If this forgetting happens in a relatively ``random'' way (with respect
to spatial distance within the embedding space), then it could explain why some
held-out questions about \textit{Four Fundamental Forces} were answered
incorrectly, even if questions at nearby coordinates (i.e., about similar
content) were answered correctly. This might lead our approach to over-estimate
knowledge for held-out questions about ``forgotten'' knowledge that
participants answered incorrectly. Taken together, these within-lecture results
suggest that our approach can distinguish between questions about different
content covered by a single lecture when participants have sufficiently
structured knowledge about its contents, though this specificity may decrease
with time since the relevant material was learned.

Finally, we used this approach to estimate participants' knowledge about
held-out questions from one lecture using their performance on questions from
the \textit{other} lecture. Here we again observed a similar pattern of
results, though with some notable differences. On Quiz~1, we found that
participants' abilities to correctly answer questions about \textit{Four
Fundamental Forces} could be predicted from their responses to questions about
\textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\
\textnormal{CI} = [6.224, 7.524],\ p = 0.038$) and similarly, that their
ability to correctly answer \textit{Birth of Stars}-related questions could be
predicted from their responses to \textit{Four Fundamental Forces}-related
questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\ \textnormal{CI} = [5.656,
6.843],\ p = 0.042$). Given the results from our analyses that included all
questions and within-lecture predictions, we were surprised to find that the
knowledge estimates could reliably (if weakly) predict participants'
performance across content from different lectures. It is possible that this
result reflects a combination of random guessing prior to training (leading to
a weak effect size), alongside some coarse-scale structured knowledge that
participants had about the content prior to watching either lecture. When we
repeated this analysis using questions from Quiz~2, we found participants'
responses to \textit{Four Fundamental Forces}-related questions did
\textit{not} reliably predict their success on \textit{Birth of Stars}-related
questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027,
3.600],\ p = 0.124$), nor did their responses to \textit{Birth of
Stars}-related questions reliably predict their success on \textit{Four
Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\
95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.093$). These ``prediction
failures'' appear to come from the fact that any signal derived from
participants' knowledge about the content of the \textit{Birth of Stars}
lecture (prior to watching it) is overwhelmed by the much more dramatic increase in
their knowledge about the content of the \textit{Four Fundamental Forces}
(which they watched just prior to taking Quiz~2). This is reflected in their
Quiz~2 performance for questions about each lecture (mean proportion correct
for \textit{Four Fundamental Forces}-related questions on Quiz~2: $0.77$; mean
proportion correct for \textit{Birth of Stars}-related questions on Quiz~2:
$0.36$). When we carried out these across-lecture knowledge predictions using
questions from Quiz~3 (when participants had now viewed \textit{both}
lectures), we could again reliably predict success on questions about both
\textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\
\textnormal{CI} = [9.126, 18.476],\ p = 0.003$) and \textit{Birth of Stars}
($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\
p = 0.016$) using responses to questions about the other lecture's content.
Across all three versions of these analyses, our results suggest that (by and
large) our knowledge estimates can reliably predict participants' abilities to
answer individual quiz questions, distinguish between questions about similar
content, and generalize across content areas, provided that participants' quiz
responses reflect a minimum level of ``real'' knowledge about both content on
which these predictions are based and that for which they are made.

That the knowledge predictions derived from the text embedding space reliably
distinguish between held-out correctly versus incorrectly answered questions
(Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
space can help explain what participants know. But how far does this
explanatory power extend? For example, suppose we know that a participant
correctly answered a question at embedding coordinate $x$. As we move farther
away from $x$ in the embedding space, how does the likelihood that the
participant knows about the content at a given location ``fall off'' with
distance? Conversely, suppose the participant instead answered that same
question \textit{in}correctly. Again, as we move farther away from $x$ in the
embedding space, how does the likelihood that the participant does \textit{not}
know about a coordinate's content change with distance? We reasoned that,
assuming our embedding space is capturing something about how individuals
actually organize their knowledge, a participant's ability to answer questions
embedded very close to $x$ should tend to be similar to their ability to answer
the question embedded \textit{at} $x$. Whereas at another extreme, once we
reach some sufficiently large distance from $x$, our ability to infer whether
or not a participant will correctly answer a question based on their ability to
answer the question at $x$ should be no better than guessing based on their
\textit{overall} proportion of correctly answered questions. In other words,
beyond the maximum distance at which the participant's ability to answer the
question at $x$ is informative of their ability to answer a second question at
location $y$, then guessing the outcome at $y$ based on $x$ should be no more
successful than guessing based on a measure that does not consider embedding
space distance.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/knowledge-smoothness}

    \caption{\textbf{Knowledge falls off gradually in text embedding space.}
    \textbf{A. Performance versus distance.} For each participant, for each
    correctly answered question (blue) or incorrectly answered question (red),
    we computed the proportion of correctly answered questions within a given
    distance of that question's embedding coordinate. We used these proportions
    as a proxy for participants' knowledge about the content within that region
    of the embedding space. We repeated this analysis for all questions and
    participants, and separately for each quiz (column). The black lines denote
    the average proportion correct across \textit{all} questions included in
    the analysis at the given distance. \textbf{B. Maximum distance for which
    performance is reliably different from the average.} We used a bootstrap
    procedure (see~\nameref{subsec:smoothness}) to estimate the point at which
    the blue and red lines in Panel A reliably diverged from the black line. We
    repeated this analysis separately for correctly and incorrectly answered
    questions from each quiz. \textbf{All panels.} Error ribbons denote
    bootstrap-estimated 95\% confidence intervals.}

    \label{fig:smoothness}
\end{figure}

With these ideas in mind, we asked: conditioned on answering a question
correctly, what proportion of all questions (within some radius, $r$, of that
question's embedding coordinate) were answered correctly? We plotted this
proportion as a function of $r$. Similarly, we could ask, conditioned on
answering a question incorrectly, how the proportion of correct responses
changed with $r$. As shown in Figure~\ref{fig:smoothness}, we found that quiz
performance falls off smoothly with distance, and the ``rate'' of the falloff
does not appear to change across the different quizzes, as measured by the
distance at which performance becomes statistically indistinguishable from a
simple proportion correct score (see~\nameref{subsec:smoothness}). This
suggests that, at least within the region of text embedding space covered by
the questions our participants answered (and as characterized using our topic
model), the rate at which knowledge changes with distance is relatively
constant, even as participants' overall level of knowledge varies across
quizzes or regions of the embedding space.

Knowledge estimates need not be limited to the content of the lectures. As
illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
estimating knowledge from a small number of quiz questions may be extended to
\textit{any} content, given its text embedding coordinate. To visualize how
knowledge ``spreads'' through text embedding space to content beyond the
lectures participants watched, we first fit a new topic model to the lectures'
sliding windows with $k = 100$~topics. Conceptually, increasing the
number of topics used by the model functions to increase the ``resolution'' of
the embedding space, providing a greater ability to estimate knowledge for
content that is highly similar to (but not precisely the same as) that
contained in the two lectures. We note that we used these 2D maps solely for
visualization; all relevant comparisons, distance computations, and statistical
tests we report above were carried out in the original 15-dimensional space,
using the 15-topic model. Aside from increasing the number of topics from 15 to
100, all other procedures and model parameters were carried over from the
preceding analyses. As in our other analyses, we resampled each lecture's topic
trajectory to 1~Hz and projected each question into a shared text embedding
space.

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/knowledge_and_learning_maps}

    \caption{\textbf{Mapping out the geometry of knowledge and learning.}
    \textbf{A. Average ``knowledge maps'' estimated using each quiz.} Each map
    displays a 2D projection of the estimated knowledge about the content
    reflected by \textit{all} regions of topic space (see
    \nameref{subsec:knowledge-maps}). The topic trajectories of the two
    lectures are indicated by dotted lines (blue: Lecture 1; green: Lecture 2),
    and the coordinates of each question are indicated by dots (light blue:
    Lecture 1-related; light green: Lecture 2-related; purple: general physics
    knowledge). Each map reflects an average across all participants. For
    individual participants' maps, see Supplementary
    Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
    and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
    estimated between each successive pair of quizzes.} The learning maps
    follow the same general format as the knowledge maps in Panel A, but here
    the shading at each coordinate indicates the \textit{difference} between
    the corresponding coordinates in the indicated \textit{pair} of knowledge
    maps---i.e., how much the estimated knowledge ``changed'' between the two
    quizzes. Each map reflects an average across all participants. For
    individual participants' maps, see Supplementary
    Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
    Word clouds for sampled points in topic space.} Each word cloud displays
    the weighted blend of words underlying the topic proportions represented at
    the corresponding colored star's location on the maps. In each word cloud,
    the words' relative sizes correspond to their relative weights at the
    starred location, and their colors indicate their relative weights in
    \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}
    (green) lectures, on average, across all timepoints' topic vectors.}

    \label{fig:knowledge-maps}
    \end{figure}

We projected the resulting 100-dimensional topic vectors (for each second of
video and each quiz question) onto a shared 2-dimensional plane (see
\nameref{subsec:knowledge-maps}). Next, we sampled points from a $100 \times
100$ grid of coordinates that evenly tiled a rectangle enclosing the 2D
projections of the videos and questions. We used
Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
these 10,000 sampled locations, and averaged these estimates across
participants to obtain an estimated average \textit{knowledge map}
(Fig.~\ref{fig:knowledge-maps}A). Intuitively, the knowledge map constructed
from a given quiz's responses provides a visualization of how ``much''
participants knew about any content expressible by the fitted text embedding
model at the point in time when they completed that quiz.

Several features of the resulting knowledge maps are worth noting. The average
knowledge map estimated from Quiz~1 responses (Fig.~\ref{fig:knowledge-maps}A,
leftmost map) shows that participants tended to have relatively little
knowledge about any parts of the text embedding space (i.e., the shading is
relatively dark everywhere). The knowledge map estimated from Quiz~2 responses
shows a marked increase in knowledge on the left side of the map (around
roughly the same range of coordinates traversed by the \textit{Four Fundamental
Forces} lecture, indicated by the dotted blue line). In other words,
participants' estimated increase in knowledge is localized to conceptual
content that is nearby (i.e., related to) the content from the lecture they
watched prior to taking Quiz~2. This localization is non-trivial: these
knowledge estimates are informed only by the embedded coordinates of the
\textit{quiz questions}, not by the embeddings of either lecture (see
Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz~3
responses shows a second increase in knowledge, localized to the region
surrounding the embedding of the \textit{Birth of Stars} lecture participants
watched immediately prior to taking Quiz~3.

Another way of visualizing these content-specific increases in knowledge after
participants viewed each lecture is displayed in
Figure~\ref{fig:knowledge-maps}B. Taking the point-by-point difference between
the knowledge maps estimated from responses to a successive pair of quizzes
yields a \textit{learning map} that describes the \textit{change} in knowledge
estimates from one quiz to the next. These learning maps highlight that the
estimated knowledge increases we observed across maps were specific to the
regions around the embeddings of each lecture, in turn.

Because the 2D projection we used to construct the knowledge and learning maps
is invertible, we may gain additional insights into these maps' meanings by
reconstructing the original high-dimensional topic vector for any location on
the map we are interested in. For example, this could serve as a useful tool
for an instructor looking to better understand which content areas a student
(or a group of students) knows well (or poorly). As a demonstration, we show
the top-weighted words from the blends of topics reconstructed from three
example locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near
the \textit{Four Fundamental Forces} embedding (yellow), a second point near
the \textit{Birth of Stars} embedding (orange), and a third point between the
two lectures' embeddings (pink). As shown in the word clouds in the panel, the
top-weighted words at the example coordinate near the \textit{Four Fundamental
Forces} embedding tended to be weighted more heavily by the topics expressed in
that lecture. Similarly, the top-weighted words at the example coordinate near
the \textit{Birth of Stars} embedding tended to be weighted more heavily by the
topics expressed in \textit{that} lecture. And the top-weighted words at the
example coordinate between the two lectures' embeddings show a roughly even mix
of words most strongly associated with each lecture.

\section*{Discussion}

We developed a computational framework that uses short multiple-choice quizzes
to gain nuanced insights into what learners know and how their knowledge
changes with training. First, we show that our approach can automatically match
the conceptual knowledge probed by individual quiz questions to the
corresponding moments in lecture videos when those concepts were presented
(Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
estimate moment-by-moment ``knowledge traces'' that reflect the degree of
knowledge participants have about each video's time-varying content, and
capture temporally specific increases in knowledge after viewing each lecture
(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
Finally, we use our framework to construct visual maps that provide snapshot
estimates of how much participants know about any concept within the scope of
our text embedding model, and how much their knowledge of those concepts
changes with training (Fig.~\ref{fig:knowledge-maps}).

We view our work as making several contributions to the study of how people
acquire conceptual knowledge. First, from a methodological standpoint, our
modeling framework provides a systematic means of mapping out and
characterizing knowledge in maps that have infinite (arbitrarily many) numbers
of coordinates, and of ``filling out'' those maps using relatively small
numbers of multiple choice quiz questions. Our experimental finding that we can
use these maps to predict responses to held-out questions has several
psychological implications as well. For example, concepts that are assigned to
nearby coordinates by the text embedding model also appear to be ``known to a
similar extent'' (as reflected by participants' responses to held-out
questions; Fig.~\ref{fig:predictions}). This suggests that participants also
\textit{conceptualize} similarly the content reflected by nearby embedding
coordinates. How participants' knowledge falls off with spatial distance is
captured by the knowledge maps we infer from their quiz responses
(e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words,
our study shows that knowledge about a given concept implies knowledge about
related concepts, and we also show how estimated knowledge falls off with
distance in text embedding space.

In our study, we characterize the ``coordinates'' of participants' knowledge
using a relatively simple ``bag of words'' text embedding model~\citep[LDA;
][]{BleiEtal03}. More sophisticated text embedding models, such as
transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23}
can learn complex grammatical and semantic relationships between words,
higher-order syntactic structures, stylistic features, and more. We considered
using transformer-based models in our study, but we found that the text
embeddings derived from these models were surprisingly uninformative with
respect to differentiating or otherwise characterizing the conceptual content
of the lectures and questions we used. We suspect that this reflects a broader
challenge in constructing models that are high-resolution within a given domain
(e.g., the domain of physics lectures and questions) \textit{and} sufficiently
broad so as to enable them to cover a wide range of domains. For example, we
found that the embeddings derived even from much larger and more modern models
like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17}, LLaMa~\citep{TouvEtal23},
and others that are trained on enormous text corpora, end up yielding poor
resolution within the content space spanned by individual course videos
(Supp.~Fig.~\ldaVsBERT). Whereas the LDA embeddings of the lectures and
questions are ``near'' each other (i.e., the convex hull enclosing the two
lectures' trajectories is highly overlapping with the convex hull enclosing the
questions' embeddings), the BERT embeddings of the lectures and questions are
instead largely distinct (top row of Supp.~Fig.~\ldaVsBERT). The LDA embeddings
of the questions for each lecture and the corresponding lecture's trajectory
are also similar. For example, as shown in Fig.~\ref{fig:sliding-windows}C, the
LDA embeddings for \textit{Four Fundamental Forces} questions (blue dots)
appear closer to the \textit{Four Fundamental Forces} lecture trajectory (blue
line), whereas the LDA embeddings for \textit{Birth of Stars} questions (green
dots) appear closer to the \textit{Birth of Stars} lecture trajectory (green
line). The BERT embeddings of the lectures and questions do not show this
property (Supp.~Fig.~\ldaVsBERT). We also examined per-question ``content
matches'' between individual questions and individual moments of each lecture
(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The time series plot of
individual questions' correlations are different from each other when computed
using LDA (e.g., the traces can be clearly visually separated), whereas the
correlations computed from BERT embeddings of different questions all look very
similar. This tells us that LDA is capturing some differences in content
between the questions, whereas BERT is not. The time series plots of individual
questions' correlations have clear ``peaks'' when computed using LDA, but not
when computed using BERT. This tells us that LDA is capturing a ``match''
between the content of each question and a relatively well-defined time window
of the corresponding lectures. The BERT embeddings appear to blur together the
content of the questions versus specific moments of each lecture. Finally, we
also compared the pairwise correlations between embeddings of questions within
versus across content areas (i.e., content covered by the individual lectures,
lecture-specific questions, and by the ``general physics knowledge''
questions). The LDA embeddings show a strong contrast between same-content
embeddings versus across-content embeddings. In other words, the embeddings of
questions about the \textit{Four Fundamental Forces} material are highly
correlated with the embeddings of the \textit{Four Fundamental Forces} lecture,
but not with the embeddings of \textit{Birth of Stars}, questions about
\textit{Birth of Stars}, or general physics knowledge questions. We see a
similar pattern with the LDA embeddings of the \textit{Birth of Stars}
questions (Fig.~\ref{fig:topics}, Supp.~Fig.~\topicWeights). In contrast, the
BERT embeddings are all highly correlated with each other (Supp.
Fig.~\ldaVsBERT). Taken together, these comparisons illustrate how LDA (trained
on the specific content in question) provides both coverage of the requisite
material and specificity at the level of the content covered by individual
questions. BERT, on the other hand, essentially assigns both lectures and all
of the questions (which are all broadly about ``physics'') into a tiny region
of its embedding space, thereby blurring out meaningful distinctions between
different specific concepts covered by the lectures and questions. We note that
these are not criticisms of BERT (or other large language models trained on
large and diverse corpora). Rather, our point is that simple fine-tuned models
trained on a relatively small but specialized corpus can outperform much more
complicated models trained on much larger corpora, when we are specifically
interested in capturing subtle conceptual differences at the level of a single
course lecture or question. Of course if our goal had been to find a model that
generalized to many different content areas, we would expect our approach to
perform comparatively poorly relative to BERT or other much larger models. We
suggest that bridging the tradeoff between high resolution within each content
area versus the ability to generalize to many different content areas will be
an important challenge for future work in this domain.

Another application for large language models that does \textit{not} require
explicitly modeling the content of individual lectures or questions is to
leverage the models' abilities to generate text. For example, generative text
models like ChatGPT~\citep{ChatGPT} and LLaMa~\citep{TouvEtal23} are already
being used to build a new generation of interactive tutoring
systems~\citep[e.g.,][]{MannEtal23b}. Unlike the approach we have taken here,
these generative text model-based systems do not explicitly model what learners
know, or how their knowledge changes over time with training. One could imagine
building a hybrid system that combines the best of both worlds: a large
language model that can \textit{generate} text, combined with a smaller model
that can \textit{infer} what learners know and how their knowledge changes over
time. Such a hybrid system could potentially be used to build the next
generation of interactive tutoring systems that are able to adapt to learners'
needs in real time, and that are able to provide more nuanced feedback about
what learners know and what they do not know.

At the opposite end of the spectrum from large language models, one could also
imagine \textit{simplifying} some aspects of our LDA-based approach by
computing simple word overlap metrics. For example, the Jaccard similarity
between text $A$ and $B$ is computed as the number of unique words in the
intersection of words from $A$ and $B$ divided by the number of unique words in
the union of words from $A$ and $B$. In a supplementary analysis (Supp.
Fig.~\jaccard), we compared the LDA-based question-lecture matches we reported
in Figure~\ref{fig:question-correlations} with the Jaccard similarities between
each question and each sliding window of text from the corresponding lecture.
As shown in Supplementary Figure~\jaccard, this simple word-matching approach
does not appear to capture the same level of specificity as the LDA-based
approach. Whereas the LDA-based approach often yields a clear peak in the
time series of correlations between each question and the corresponding lecture,
the Jaccard similarity-based approach does not. Furthermore, these LDA-based
matches appear to capture conceptual overlaps between the questions and
lectures (Supp.~Tab.~\matchTab), whereas simple word matching does not. For
example, one of the example questions examined in Supplementary
Figure~\jaccard~asks ``Which of the following occurs as a cloud of atoms gets
more dense?'' The LDA-based matches identify lecture timepoints where the
relevant \textit{topics} are discussed (e.g., when words like ``cloud,''
``atom,'' ``dense,'' etc., are mentioned \textit{together}). The Jaccard
similarity-based matches, on the other hand, are strong when \textit{any} of
these words are mentioned, even if they do not occur together.

We view our approach as occupying a sort of ``sweet spot,'' between much larger
language models and simple word matching-based approaches, that enables us to
capture the relevant conceptual content of course materials at an appropriate
semantic scale. Our approach enables us to accurately and consistently identify
each question's content in a way that also matches up with what is presented in
the lectures. In turn, this enables us to construct accurate predictions about
participants' knowledge of the conceptual content tested by held-out questions
(Fig.~\ref{fig:predictions}).

One limitation of our approach is that topic models contain no explicit
internal representations of more complex aspects of ``knowledge,'' like
knowledge graphs, dependencies or associations between concepts, causality, and
so on. These representations might (in principle) be added as extensions to our
approach to more accurately and precisely capture, characterize, and track
learners' knowledge. However, modeling these aspects of knowledge will likely
require substantial additional research effort.

Within the past several years, the global pandemic forced many educators to
suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21,
Whal20}. This change in world circumstances is happening alongside (and perhaps
accelerating) geometric growth in the availability of high-quality online
courses from platforms such as Khan Academy~\citep{Khan04},
Coursera~\citep{Youn12}, EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}.
Continued expansion of the global internet backbone and improvements in
computing hardware have also facilitated improvements in video streaming,
enabling videos to be easily shared and viewed by increasingly large segments
of the world's population. This exciting time for online course instruction
provides an opportunity to re-evaluate how we, as a global community, educate
ourselves and each other. For example, we can ask: what defines an effective
course or training program? Which aspects of teaching might be optimized and/or
augmented by automated tools? How and why do learning needs and goals vary
across people? How might we lower barriers to receiving a high-quality
education?

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real
classrooms~\citep{Kauf03}. In part, this has led to a recent resurgence of
``naturalistic'' or ``observational'' experimental paradigms that attempt to
better reflect more ethologically valid phenomena that are more directly
relevant to real-world situations and behaviors~\citep{NastEtal20}. In turn,
this has brought new challenges in data analysis and interpretation. A key step
towards solving these challenges will be to build explicit models of real-world
scenarios and how people behave in them (e.g., models of how people learn
conceptual content from real-world courses, as in our current study). A second
key step will be to understand which sorts of signals derived from behaviors
and/or other measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22,
MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these
models. A third major step will be to develop and employ reliable ways of
evaluating the complex models and data that are a hallmark of naturalistic
paradigms.

Beyond specifically predicting what people \textit{know}, the fundamental ideas
we develop here also relate to the notion of ``theory of mind'' of other
individuals~\citep{GoldWinn12, KansEtal15, Melt11}. Considering others' unique
perspectives, prior experiences, knowledge, goals, etc., can help us to more
effectively interact and communicate~\citep{ShaoEtal18, StepBaer06, Ratk18}.
One could imagine future extensions of our work (e.g., analogous to the
knowledge and learning maps shown in Fig.~\ref{fig:knowledge-maps}), that
attempt to characterize how well-aligned different people's knowledge bases or
backgrounds are. In turn, this might be used to model how knowledge (or other
forms of communicable information) flows not just between teachers and
students, but between friends having a conversation, individuals on a first
date, participants at a business meeting, doctors and patients, experts and
non-experts, political allies or adversaries, and more. For example, the extent
to which two people's knowledge maps ``match'' or ``align'' in a given region
of text embedding space might serve as a predictor of how effectively they will
be able to communicate about the corresponding conceptual content.

Ultimately, our work suggests a rich new line of questions about the geometric
``form'' of knowledge, how knowledge changes over time, and how we might map
out the full space of what an individual knows. Our finding that detailed
estimates about knowledge may be obtained from short quizzes shows one way that
traditional approaches to evaluation in education may be extended. We hope that
these advances might help pave the way for new approaches to teaching or
delivering educational content that are tailored to individual students'
learning needs and goals.

\section*{Materials and methods}

\subsection*{Participants}

We enrolled a total of 50 Dartmouth undergraduate students in our study.
Participants received optional course credit for enrolling. We asked each
participant to complete a demographic survey that included questions about
their age, gender, native spoken language, ethnicity, race, hearing, color
vision, sleep, coffee consumption, level of alertness, and several aspects of
their educational background and prior coursework.

Participants' ages ranged from 18 to 22 years (mean: 19.52 years; standard
deviation: 1.09 years). A total of 15 participants reported their gender as
male and 35 participants reported their gender as female. A total of 49
participants reported their native language as ``English'' and 1 reported
having another native language. A total of 47 participants reported their
ethnicity as ``Not Hispanic or Latino'' and three reported their ethnicity as
``Hispanic or Latino.'' Participants reported their races as White (32
participants), Asian (14 participants), Black or African American (5
participants), American Indian or Alaska Native (1 participant), and Native
Hawaiian or Other Pacific Islander (1 participant). (Note that some
participants selected multiple racial categories.)

A total of 49 participants reporting having normal hearing and 1 participant
reported having some hearing impairment. A total of 49 participants reported
having normal color vision and 1 participant reported being color blind.
Participants reported having had, on the night prior to testing, 2--4 hours of
sleep (1 participant), 4--6 hours of sleep (9 participants), 6--8 hours of
sleep (35 participants), or $8+$ hours of sleep (5 participants). They reported
having consumed, on the same day and leading up to their testing session, 0
cups of coffee (38 participants), 1 cup of coffee (10 participants), 3 cups of
coffee (1 participant), or $4+$ cups of coffee (1 participant).

No participants reported that their focus was currently impaired (e.g., by
drugs or alcohol). Participants reported their current level of alertness, and
we converted their responses to numerical scores as follows: ``very sluggish''
(-2), ``a little sluggish'' (-1), ``neutral'' (0), ``fairly alert'' (1), and
``very alert'' (2). Across all participants, a range of alertness levels were
reported (range: -2--1; mean: -0.10; standard deviation: 0.84).

Participants reported their undergraduate major(s) as ``social sciences'' (28
participants), ``natural sciences'' (16 participants), ``professional'' (e.g.,
pre-med or pre-law; 8 participants), ``mathematics and engineering'' (7
participants), ``humanities'' (4 participants), or ``undecided'' (3
participants). Note that some participants selected multiple categories for
their undergraduate major(s). We also asked participants about the courses they
had taken. In total, 45 participants reported having taken at least one Khan
Academy course in the past, and 5 reported not having taken any Khan Academy
courses. Of those who reported having watched at least one Khan Academy course,
7 participants reported having watched 1--2 courses, 11 reported having watched
3--5 courses, 8 reported having watched 5--10 courses, and 19 reported having
watched 10 or more courses. We also asked participants about the specific
courses they had watched, categorized under different subject areas. In the
``Mathematics'' area, participants reported having watched videos on AP
Calculus AB (21 participants), Precalculus (17 participants), Algebra 2 (14
participants), AP Calculus BC (12 participants), Trigonometry (11
participants), Algebra 1 (10 participants), Geometry (8 participants),
Pre-algebra (7 participants), Multivariable Calculus (5 participants),
Differential Equations (5 participants), Statistics and Probability (4
participants), AP Statistics (2 participants), Linear Algebra (2 participants),
Early Math (1 participant), Arithmetic (1 participant), and other videos not
listed in our survey (5 participants). In the ``Science and engineering'' area,
participants reported having watched videos on Chemistry, AP Chemistry, or
Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II
(18 participants); Biology, AP Biology; or High school Biology (15
participants); Health and Medicine (1 participant); or other videos not listed
in our survey (5 participants). We also asked participants whether they had
specifically seen the videos used in our experiment. Of the 45 participants who
reported having having taken at least one Khan Academy course in the past, 44
participants reported that they had not watched the \textit{Four Fundamental
Forces} video, and 1 participant reported that they were not sure whether they
had watched it. All participants reported that they had not watched the
\textit{Birth of Stars} video. When we asked participants about non-Khan
Academy online courses, they reported having watched or taken courses on
Mathematics (15 participants), Science and engineering (11 participants), Test
preparation (9 participants), Economics and finance (3 participants), Arts and
humanities (2 participants), Computing (2 participants), and other categories
not listed in our survey (17 participants). Finally, we asked participants
about in-person courses they had taken in different subject areas. They
reported taking courses in Mathematics (38 participants), Science and
engineering (37 participants), Arts and humanities (34 participants), Test
preparation (27 participants), Economics and finance (26 participants),
Computing (14 participants), College and careers (7 participants), or other
courses not listed in our survey (6 participants).

\subsection*{Experiment}\label{subsec:experiment}

We hand-selected two course videos from the Khan Academy platform: \textit{Four
Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
nuclear force, and the strong nuclear force; duration: 10 minutes and 29
seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
duration: 7 minutes and 57 seconds). All participants viewed the videos in the
same order (i.e., \textit{Four Fundamental Forces} followed by \textit{Birth of
Stars}).

We then hand-created 39 multiple-choice questions: 15 about the conceptual
content of \textit{Four Fundamental Forces} (i.e., Lecture~1), 15 about the
conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). To help broaden the
set of lecture-specific questions, our team worked through each lecture in
small segments to identify what each segment was ``about'' conceptually, and
then write a question about that concept. The general physics questions were
drawn our team's prior coursework and areas of interest, along with internet
searches and brainstorming with the project team and other members of J.R.M.'s
lab. Although we attempted to design the questions to test ``conceptual
knowledge,'' we note that estimating the specific ``amount'' of conceptual
understanding that each question ``requires'' to answer is somewhat subjective,
and might even come down to the ``strategy'' a given participant uses to answer
the question at that particular moment. The full set of questions and answer
choices may be found in Supplementary Table~\questions.  The final set of
questions (and response options) was reviewed and approved by J.R.M. before we
collected or analyzed the text or experimental data.

Over the course of the experiment, participants completed three 13-question
multiple-choice quizzes: the first before viewing Lecture~1, the second between
Lectures~1 and 2, and the third after viewing Lecture~2 (see
Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
participant, were randomly chosen from the full set of 39, with the constraints
that (a) each quiz contained exactly 5 questions about Lecture~1, 5 questions
about Lecture~2, and 3 questions about general physics knowledge, and (b) each
question appear exactly once for each participant. The orders of questions on
each quiz, and the orders of answer options for each question, were also
randomized. We obtained informed consent from all participants, and our
experimental protocol was approved by the Committee for the Protection of Human
Subjects at Dartmouth College. We used this experiment to develop and test our
computational framework for estimating knowledge and learning.

\subsection*{Analysis}

\subsubsection*{Statistics}

All of the statistical tests performed in our study were two-sided. The 95\%
confidence intervals we reported for each correlation were estimated by
generating 10,000 bootstrap distributions of correlation coefficients by
sampling (with replacement) from the observed data.

\subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}

We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
each moment of the two lectures and each question in our pool in a common
representational space. Briefly, our approach uses a topic model~\citep[Latent
Dirichlet Allocation; ][]{BleiEtal03} trained on a set of documents, to
discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is
defined as a distribution of weights over words in the model's vocabulary
(i.e., the union of all unique words, across all documents, excluding ``stop
words.''). Conceptually, each topic is intended to give larger weights to words
that are semantically related (as inferred from their tendency to co-occur in
the same document). After fitting a topic model, each document in the training
set, or any \textit{new} document that contains at least some of the words in
the model's vocabulary, may be represented as a $k$-dimensional vector
describing how much the document (most probably) reflects each topic. To select
an appropriate $k$ for our model, as a starting point, we identified the
minimum number of topics that yielded at least one ``unused'' topic (i.e., in
which all words in the vocabulary were assigned uniform weights) after
training. This indicated that the number of topics was sufficient to capture
the set of latent themes present in the two lectures (from which we constructed
our document corpus, as described below). We found this value to be $k = 15$
topics. We found that with a limited number of additional adjustments
following~\citet{BoydEtal14}, such as removing corpus-specific stop-words, the
model yielded (subjectively) sensible and coherent topics. The distribution of
weights over words in the vocabulary for each discovered topic is shown in
Supplementary Figure~\topicWordWeights, and each topic's top-weighted words may
be found in Supplementary Table~\topics.

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy provides professionally created, manual transcriptions
of all videos for closed captioning. However, such transcripts would not be
readily available in all contexts to which our framework could potentially be
applied. Khan Academy videos are hosted on the YouTube platform, which
additionally provides automated captions. We opted to use these automated
transcripts~\citep[which, in prior work, we have found to be of sufficiently
near-human quality to yield reliable data in behavioral
studies; ][]{ZimaEtal18} when developing our framework in order to make
it more directly extensible and adaptable by others in the future.

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo18}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between the timestamps for its first
and last lines. This $w$ parameter was chosen to match the same number of words
per sliding window (rounded to the nearest whole word, and before
preprocessing) as the sliding windows we defined in our prior
work~\citep[][i.e., 185 words per sliding window]{HeusEtal21}.

These sliding windows ramped up and down in length at the beginning and end of
each transcript, respectively. In other words, each transcript's first sliding
window covered only its first line, the second sliding window covered the first
two lines, and so on. This ensured that each line from the transcripts appeared
in the same number ($w$) of sliding windows. We next performed a series of
standard text preprocessing steps: normalizing case, lemmatizing, removing
punctuation and removing stop-words. We constructed our corpus of stop words by
augmenting the Natural Language Toolkit~\citep[NLTK; ][]{BirdEtal09} English
stop word list with the following additional words, selected using one of the
approaches suggested by~\citet{BoydEtal14}: ``actual,'' ``actually,'' ``also,''
``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
remaining words, and lasting for an average of 62.22~seconds. We treated the
text from each sliding window as a single ``document,'' and combined these
documents across the two videos' windows to create a single training corpus for
the topic model.

After fitting a topic model to the two videos' transcripts, we could use the
trained model to transform arbitrary (potentially new) documents into
$k$-dimensional topic vectors. A convenient property of these topic vectors is
that documents that reflect similar blends of topics (i.e., documents that
reflect similar themes, according to the model) will yield similar coordinates
(in terms of correlation, cosine similarity, Kullback-Leibler divergence,
Euclidean distance, or other geometric measures). In general, the similarity
between different documents' topic vectors may be used to characterize the
similarity in conceptual content between the documents.

We transformed each sliding window's text into a topic vector, and then used
linear interpolation (independently for each topic dimension) to resample the
resulting time series to one vector per second. We also used the fitted model to
obtain topic vectors for each question in our pool (see Supp.~Tab.~\questions).
Taken together, we obtained a \textit{trajectory} for each video, describing
its path through topic space, and a single coordinate for each question
(Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
questions using a common model enables us to compare the content from different
moments of videos, compare the content across videos, and estimate potential
associations between specific questions and specific moments of video.

\subsubsection*{Estimating dynamic knowledge traces}\label{subsec:traces}

We used the following equation to estimate each participant's knowledge about
timepoint $t$ of a given lecture, $\hat{k}(t)$:
\begin{equation}
    \hat{k}\left(f(t, L)\right) = \frac{\sum_{i \in \mathrm{correct}}\mathrm{ncorr}\left(f(t, L), f(i, Q)\right)}{\sum_{j = 1}^N \mathrm{ncorr}\left(f(t, L), f(j, Q)\right)},
    \label{eqn:prop}
\end{equation}
where

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints in the given lecture, and all five questions \textit{about} that lecture appearing on the given quiz.
We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.

Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
vectors (e.g., the topic vector from one timepoint in a lecture, $x$, and the
topic vector for one question, $y$), normalized by the minimum and maximum
correlations (across all timepoints $t$ and questions $Q$) to range between 0
and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
proportion of correctly answered questions about the content presented at
timepoint $t$, where the weights are given by the normalized correlations
between timepoint $t$'s topic vector and the topic vectors for each question.
The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
correlations) ensures that every question contributes some non-negative amount
to the knowledge estimate.

\subsubsection*{Generalized linear mixed models}\label{subsec:glmm}

In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed
whether estimates of participants' knowledge at the embedding coordinates of
individual quiz questions could be used to reliably predict their ability to
correctly answer those questions. In essence, we treated each question a given
participant answered on a given quiz as a ``lecture'' consisting of a single
timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's
knowledge for its embedding coordinate based on their performance on all
\textit{other} questions they answered on that same quiz (``All questions'';
Fig.~\ref{fig:predictions}, top row). Additionally, for each lecture-related
question (i.e., excluding questions about general physics knowledge), we
computed analogous knowledge estimates based on all other questions the
participant answered on the same quiz about (1) the same lecture as the target
question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2)
the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions},
bottom rows).

In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and
separately for each of the three quizzes (i.e., column in
Fig.~\ref{fig:predictions}), we then fit a generalized linear mixed model
(GLMM) with a logistic link function to the set of knowledge estimates for all
questions that participants answered on the given quiz. We implemented these
models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and
fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
Specifically, we initially fit each model with the maximal random effects
structure afforded by our design, which we identified as:
\[
    \mathtt{accuracy \sim knowledge + (knowledge\ \vert\ participant) + (knowledge\ \vert\ question)}
\]
where ``\texttt{accuracy}'' is a binary value indicating whether each target
question was answered correctly or incorrectly, ``\texttt{knowledge}'' is
estimated knowledge at each target question's embedding coordinate,
``\texttt{participant}'' is a unique identifier assigned to each participant,
and ``\texttt{question}'' is a unique identifier assigned to each quiz
question. For models we fit using knowledge estimates for target questions
about multiple content areas (i.e., in the ``All questions'' version of the
analysis), we also included an additional random effect term,
$\mathtt{(knowledge\ \vert\ lecture)}$, where ``\texttt{lecture}'' is a
categorical value denoting whether the target question was about \textit{Four
Fundamental Forces}, \textit{Birth of Stars}, or general physics knowledge.
Note that with our coding scheme, identifiers for each \texttt{question} are
implicitly nested within levels of \texttt{lecture} and do not require explicit
nesting in our model formula. We then iteratively removed random effects from 
the maximal model until it successfully converged with a full rank (i.e., non-singular) 
random effects variance-covariance matrix.

To assess the predictive value of our knowledge estimates, we compared each
GLMM's ability to discriminate between correctly and incorrectly answered
questions to that of an analogous model that did \textit{not} consider estimated
knowledge. Specifically, we used the same sets of observations with which we
fit each ``full'' model to fit a second ``null'' model, with the formula:
\[
    \mathtt{accuracy \sim (1\ \vert\ participant) + (1\ \vert\ question)}
\]
where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above. 
As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' is as defined above. 
We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 
Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrap procedure~\citep{DaviHink97,HaleHojs14}. 
For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
We then re-fit both the null and full models to this simulated sample and compared them via an LRT.
This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
We computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r+1}{n+1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than our observed value and $n$ is the number of simulations we ran (1,000).

\subsubsection*{Estimating the ``smoothness'' of knowledge}\label{subsec:smoothness}

In the analysis reported in Figure~\ref{fig:smoothness}A, we show how
participants' ability to correctly answer quiz questions changes as a function
of distance from a given correctly or incorrectly answered reference question.
We used a bootstrap-based approach to estimate the maximum distances over which
these proportions of correctly answered questions could be reliably
distinguished from participants' overall average proportion of correctly
answered questions.

For each of 10,000 iterations, we drew a random subsample (with replacement) of
50 participants from our dataset. Within each iteration, we first computed the
95\% confidence interval (CI) of the across-subsample-participants mean
proportion correct on each of the three quizzes, separately. To compute this
interval for each quiz, we repeatedly (1,000 times) subsampled participants
(with replacement, from the outer subsample for the current iteration) and
computed the mean proportion correct of each of these inner subsamples. We then
identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles
of the resulting distributions of 1,000 means. These three intervals (one for
each quiz) served as our thresholds for confidence that the proportion correct
within a given distance from a reference question was reliably different (at
the $p < 0.05$ significance level) from the average proportion correct across
all questions on the given quiz.

Next, for each participant in the current subsample, and for each of the three
quizzes they completed (separately), we iteratively treated each of the 15
questions appearing on the given quiz as the ``reference'' question. We
constructed a series of concentric 15-dimensional ``spheres'' centered on the
reference question's embedding space coordinate, where each successive sphere's
radius increased by 0.01 (correlation distance) between 0 and 2, inclusive
(i.e., tiling the range of possible correlation distances with 201 spheres in
total). We then computed the proportion of questions enclosed within each
sphere that the participant answered correctly, and averaged these per-radius
proportion correct scores across reference questions that were answered
correctly, and those that were answered incorrectly. This resulted in two
number-of-spheres sequences of proportion-correct scores for each subsample
participant and quiz: one derived from correctly answered reference questions,
and one derived from incorrectly answered reference questions.

We computed the across-subsample-participants mean proportion correct for each
radius value (i.e., sphere) and ``correctness'' of reference question. This
yielded two sequences of proportion-correct scores for each quiz, analogous to
the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the
present subsample. For each quiz, we then found the minimum distance from the
reference question (i.e., sphere radius) at which each of these two sequences
of per-radius proportion correct scores intersected the 95\% confidence
interval for the overall proportion correct (i.e., analogous to the black error
bands in Fig.~\ref{fig:smoothness}A).

This resulted in two ``intersection'' distances for each quiz (for correctly
answered and incorrectly answered reference questions). Repeating this full
process for each of the 10,000 bootstrap iterations output two distributions of
intersection distances for each of the three quizzes. The means and 95\%
confidence intervals for these distributions are plotted in
Figure~\ref{fig:smoothness}B.

\subsubsection*{Creating knowledge and learning map visualizations}\label{subsec:knowledge-maps}

An important feature of our approach is that, given a trained text embedding
model and participants' quiz performance on each question, we can estimate
their knowledge about \textit{any} content expressible by the embedding
model---not solely the content explicitly probed by the quiz questions, or even
appearing in the lectures. To visualize these estimates
(Fig.~\ref{fig:knowledge-maps}, Supp.
Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
and~\individualLearningMapsB), we used Uniform Manifold Approximation and
Projection~\citep[UMAP; ][]{McInEtal18a, McInEtal18b} to construct a 2D
projection of the text embedding space. Whereas our main analyses used a
15-topic embedding space, we used a 100-topic embedding space for these
visualizations. This change in the number of topics overcame an undesirable
behavior in the UMAP embedding procedure, whereby embedding coordinates for the
15-topic model tended to be ``clumped'' into separated clusters, rather than
forming a smooth trajectory through the 2D space. When we increased the number
of topics to 100, the embedding coordinates in the 2D space formed a smooth
trajectory through the space, with substantially less clumping
(Fig.~\ref{fig:knowledge-maps}). Creating a ``map'' by sampling this
100-dimensional space at high resolution to obtain an adequate set of topic
vectors spanning the embedding space would be computationally intractable.
However, sampling a 2D grid is trivial.

At a high level, the UMAP algorithm obtains low-dimensional embeddings by
minimizing the cross-entropy between the pairwise (clustered) distances between
the observations in their original (e.g., 100-dimensional) space and the
pairwise (clustered) distances in the low-dimensional embedding space (in our
approach, the embedding space is 2D). In our implementation, pairwise distances
in the original high-dimensional space were defined as 1 minus the correlation
between each pair of coordinates, and pairwise distances in the low-dimensional
embedding space were defined as the Euclidean distance between each pair of
coordinates.

In our application, all of the coordinates we embedded were topic vectors,
whose elements are always non-negative and sum to one. Although UMAP is an
invertible transformation at the embedding locations of the original data,
other locations in the embedding space will not necessarily follow the same
implicit ``rules'' as the original high-dimensional data. For example,
inverting an arbitrary coordinate in the embedding space might result in
negative-valued vectors, which are incompatible with the topic modeling
framework. To protect against this issue, we log-transformed the topic vectors
prior to embedding them in the 2D space. When we inverted the embedded vectors
(e.g., to estimate topic vectors or word clouds, as in
Fig.~\ref{fig:knowledge-maps}C), we passed the inverted (log-transformed)
values through the exponential function to obtain a vector of non-negative
values, and normalized them to sum to one.

After embedding both lectures' topic trajectories and the topic vectors of
every question, we defined a rectangle enclosing the 2D projections of the
lectures' and quizzes' embeddings. We then sampled points from a regular $100
\times 100$ grid of coordinates that evenly tiled this enclosing rectangle. We
sought to estimate participants' knowledge (and learning, i.e., changes in
knowledge) at each of the resulting 10,000 coordinates.

To generate our estimates, we placed a set of 39 radial basis functions (RBFs)
throughout the embedding space, centered on the 2D projections for each
question (i.e., we included one RBF for each question). At coordinate $x$, the
value of an RBF centered on a question's coordinate $\mu$, is given by:
\begin{equation}
    \mathrm{RBF}(x, \mu, \lambda) = \exp\left\{-\frac{||x - \mu||^2}{\lambda}\right\}.
    \label{eqn:rbf}
\end{equation}
The $\lambda$ term in the RBF equation controls the ``smoothness'' of the
function, where larger values of $\lambda$ result in smoother maps. In our
implementation we used $\lambda = 50$.  Next, we estimated the ``knowledge''
at each coordinate, $x$, using:
\begin{equation}
    \hat{k}(x) = \frac{\sum_{i \in \mathrm{correct}} \mathrm{RBF}(x, q_i, \lambda)}{\sum_{j = 1}^N \mathrm{RBF}(x, q_j, \lambda)}.
    \label{eqn:rbf-knowledge}
\end{equation}
Intuitively, Equation~\ref{eqn:rbf-knowledge} computes the weighted proportion of
correctly answered questions, where the weights are given by how nearby (in the 2D space)
each question is to the $x$.  We also defined \textit{learning maps} as the coordinate-by-coordinate
differences between any pair of knowledge maps.  Intuitively, learning maps reflect the \textit{change}
in knowledge across two maps.

\section*{Author contributions}

Conceptualization: P.C.F., A.C.H., and J.R.M. Methodology: P.C.F., A.C.H., and
J.R.M. Software: P.C.F. Validation: P.C.F. Formal analysis: P.C.F. Resources: P.C.F.,
A.C.H., and J.R.M. Data curation: P.C.F. Writing (original draft): J.R.M. Writing
(review and editing): P.C.F., A.C.H., and J.R.M. Visualization: P.C.F. and J.R.M.
Supervision: J.R.M. Project administration: P.C.F. Funding acquisition: J.R.M.

\section*{Data availability}

All of the data analyzed in this manuscript may be found at
https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.

\section*{Code availability}

All of the code for running our experiment and carrying out the analyses may be
found at https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.

\section*{Acknowledgements}

We acknowledge useful discussions, assistance in setting up an earlier
(unpublished) version of this study, and assistance with data collection
efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal Jha, Caroline
Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was supported in part
by NSF CAREER Award Number 2145172 to J.R.M. The content is solely the
responsibility of the authors and does not necessarily represent the official
views of our supporting organizations. The funders had no role in study design,
data collection and analysis, decision to publish, or preparation of the
manuscript.

\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
\end{document}

### 2024-12-15 paper/supplement.tex
made supp fig title bolding consistent

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{booktabs}
\usepackage{longtable}

\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}

\newcommand{\topicVariability}{3}
\newcommand{\knowledgeMaps}{7}
\newcommand{\topicModelMethods}{\textit{Constructing text embeddings of multiple lectures and questions}}

\title{\textit{Supplementary materials for}: Text embedding models yield 
high-resolution insights into conceptual knowledge from short multiple-choice
quizzes}

\author{Paxton C. Fitzpatrick\textsuperscript{1},
Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
Jeremy.R.Manning@Dartmouth.edu}}

\date{}

\begin{document}

\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter

\begin{titlepage}
\maketitle
\end{titlepage}

\begin{tiny}
\renewcommand*{\arraystretch}{1.4}
\begin{longtable}{|r|p{0.375in}|p{1.275in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|}
\hline
    \textbf{ID} & \textbf{Question set} &                                                                                                                                                                                                                                                                         \textbf{Question} &                                                                                                                                     \textbf{Correct response} &                                                                                                     \textbf{Alternative 1} &                                                                                                                          \textbf{Alternative 2} &                                                                                                                                 \textbf{Alternative 3} \\\hline
    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice? &                                           Neither you nor your computer has enough mass to cause a noticeable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline
    2     &     FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction? &                          A neutron in a radioactive Cesium atom is converted into a proton, leading to the release of a few particles &  Light from the sun collides with a satellite orbiting Earth and exerts a small push on the satellite &  Two protons bound together in a Helium nucleus resist separation despite a repulsive electromagnetic force acting on them &                                                   A distant galaxy exerts a small but detectable gravitational pull on the  Earth \\\hline
    3     &     FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity? &                                                                                                    10,\-000,\-000,\-000,\-000,\-000,\-000,\-000,\-000 &                                                                                                    10 &                                                                                                                  1,000,000 &                                                                                  The Weak Interaction is less strong than gravity \\\hline
    4     &     FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction? &                                                                         The weak interaction only acts over extremely small distances &                The weak interaction between you and your computer is counteracted by the other forces &                                                                                   You and your computer have no net charge &                                            Neither you nor your computer has enough mass to induce a significant Weak Interaction \\\hline
    5     &     FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force? &                                            Gravity is only ever attractive while the electromagnetic force can both attract and repel &                                           Gravity is a much more powerful force than electromagnetism &           Gravity can only act over large distances while the electromagnetic force can act over large and small distances &                   The electromagnetic force can only act over small distances while gravity can act over small or large distances \\\hline
    6     &     FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                            View them in different frames of reference &                              Switch which charges we call positive and which charges we call negative &                                        Consider both the effects over small distances and the effects over large distances &                                                           Consider both the attractive and repulsive properties of the two forces \\\hline
    7     &     FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus? &                                                                                        The Strong Force and the Electromagnetic Force &                                                                      Gravity and the Weak Interaction &                                                                                      Gravity and the Electromagnetic Force &                                                                                         The Strong Force and the Weak Interaction \\\hline
    8     &     FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge? &  Positive and negative charges cancel out and become a neutral charge when they combine while masses only grow larger as they combine &                                                    Masses tend to repel while charges tend to attract &                                                                         Masses tend to attract while charges tend to repel &       The gravitational interaction acting between masses is stronger than the electromagnetic interaction acting between charges \\\hline
    9     &     FFF &  In your body, there are a tremendous amount of negatively-charged electrons. Your computer also contains a huge number of negatively-charged electrons. We know that like charges repel, but you and your computer are not repelled apart. Which of the following explains why? &                                    The electrons' negative charges are balanced by the positive charges of an equal number of protons &                                         An attractive gravitational force balances out this repulsion &                                                              The Electromagnetic force only acts over very small distances &                                                                     The Electromagnetic force only acts over very large distances \\\hline
    10    &     FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force? &                                                                                               Both act only over very small distances &                                                      Both are stronger than the Electromagnetic force &                                                                                               Both are weaker than Gravity &                                                                     Both are responsible for attractions between distant galaxies \\\hline
    11    &     FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force? &                                                                                                                          Strong Force &                                                                                               Gravity &                                                                                                           Weak Interaction &                                                                                            Electromagnetic Force is the strongest \\\hline
    12    &     FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity? &                                                                                                                                 10\textasciicircum 38 &                                                                                                   100 &                                                                                                                      10\textasciicircum 18 &                                                                                           The Strong Force is weaker than gravity \\\hline
    13    &     FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects? &                                                                            The objects would have to be extremely close to each other &                                                          The objects would have to have the same mass &                                                            The objects would have to be extremely far away from each other &                                                                                   The objects would have to have different masses \\\hline
    14    &     FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth? &                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
    15    &     FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to? &                                      The repulsion of objects with similar charge and the attraction of objects with different charge &          The repulsion of objects with similar mass and the attraction of objects with different mass &                 The repulsion of objects with similar temperature and the attraction of objects with different temperature &                                The repulsion of objects with similar density and the attraction of objects with different density \\\hline
    16    &     BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms? &                                                                                 The atoms move to the center of the mass of the atoms &                                          The atoms move away from the center of the mass of the atoms &                                                                  The atoms spin around the center of the mass of the atoms &                                                                                         Gravity has no effect on a cloud of atoms \\\hline
    17    &     BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense? &                                                                                                                 Temperature increases &                                                                                 Temperature decreases &                                                                                                             Mass increases &                                                                                                                    Mass decreases \\\hline
    18    &     BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star? &                                                                                                                     10 Million Kelvin &                                                                                              0 Kelvin &                                                                                                              10,000 Kelvin &                                                                                                                 10 Billion Kelvin \\\hline
    19    &     BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force? &                                                                                                    High temperature and high pressure &                                                                     Low temperature and high pressure &                                                                                          High temperature and low pressure &                                                                                                  Low temperature and low pressure \\\hline
    20    &     BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity? &                                                           Energy released from the fusion of hydrogen atoms provides outward pressure &                                    The fusion of hydrogen atoms decreases the temperature of the star &                                                                               The gravitational pull of other stars nearby &                                                                                                              The Weak Interaction \\\hline
    21    &     BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars? &                                                                                                               Fusion occurs very fast &                                                                               Fusion occurs very slow &                                                                                         Fusion occurs in the reverse order &                                                                                                      Fusion does not occur at all \\\hline
    22    &     BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together? &                                                                                                                             Deuterium &                                                                                                Oxygen &                                                                                                                     Helium &                                                                                                                         Beryllium \\\hline
    23    &     BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together? &                                                                                                                      The Strong Force &                                                                             The Electromagnetic Force &                                                                                                                    Gravity &                                                                                                              The Weak Interaction \\\hline
    24    &     BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus? &                                                                                           The mass of the combined nucleus is smaller &                                                            The mass of the combined nucleus is larger &                                                                               The mass of the combined nucleus is the same &                                                                                It is not possible for two nuclei to fuse together \\\hline
    25    &     BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun? &                                                                     Hydrogen atoms in the Sun are fusing together and becoming Helium &                                                                        The Sun is a supermassive star &                                     The Sun does not experience the force of Gravity but does experience the Coulomb Force &                                                                                 The Sun is comprised of 10 million Hydrogen atoms \\\hline
    26    &     BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together? &                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
    27    &     BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases? &                                                                                                                 Temperature increases &                                                                                      Volume increases &                                                                                                             Mass increases &                                                                                                                 None of the above \\\hline
    28    &     BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion? &                                                                                                                                Helium &                                                                                                Oxygen &                                                                                                                     Cesium &                                                                                                                            Carbon \\\hline
    29    &     BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun? &                                                                                                                    Main sequence star &                                                                                     Supermassive star &                                                                                                  Alternative sequence star &                                                                                                                 None of the above \\\hline
    30    &     BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction? &                                                                                                                              Ignition &                                                                                            Combustion &                                                                                                              Decomposition &                                                                                                                      Displacement \\\hline
    31    &      GPK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest? &                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\\hline
    32    &      GPK &                                                                                                                                                                                                                          Which of the following defines what element an atom is? &                                                                                                                 Its number of protons &                                                                                Its number of neutrons &                                                                                                    Its number of electrons &                                                                                                                          Its mass \\\hline
    33    &      GPK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron. What changes as a result of this conversion? &                                                                                                                    The atom's element &                                                                The atom's mass (in atomic mass units) &                                                                                                        The atom's velocity &                                                                                                                The atom's density \\\hline
    34    &      GPK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest? &                                                                                                  Star, solar system, galaxy, universe &                                                             Galaxy, solar system, Milky Way, universe &                                                                                         Planet, galaxy, star, solar system &                                                                                             Earth, solar system, universe, galaxy \\\hline
    35    &      GPK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom? &                                                                                                                  Protons and neutrons &                                                                                          Only protons &                                                                                                             Only electrons &                                                                                                            Neutrons and electrons \\\hline
    36    &      GPK &                                                                                                                                                                                                                                       Which of the following has the least mass? &                                                                                                                           An electron &                                                                                              A proton &                                                                                                                  A neutron &                                                                                                                   A hydrogen atom \\\hline
    37    &      GPK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy? &                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\\hline
    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter ``m'' represent? &                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\\hline
    39    &      GPK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur? &                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\\hline

    \caption{\textbf{Question pool.} Each participant completed three quizzes consisting 
    of 13 multiple-choice questions randomly selected from the question pool. Each 
    quiz included 5 questions about the \textit{Four Fundamental Forces} lecture 
    (FFF), 5 questions about the \textit{Birth of Stars} lecture (BoS), and 3 questions 
    about general physics knowledge (GPK). Each question appeared on at most 
    one quiz (for each participant).}

    \label{tab:questions}
    \end{longtable}
\end{tiny}

\begin{table}[tp]
    \centering
    \begin{tiny}
    \begin{tabular}{|r|l|l|l|l|l|l|l|l|l|l|}
    \hline
    \textbf{Topic} & \textbf{1} & \textbf{2} &      \textbf{3} &  \textbf{4} & \textbf{5} & \textbf{6} &    \textbf{7} &  \textbf{8} & \textbf{9} &     \textbf{10} \\\hline
             1 &       star &     helium &            main &        mass &     atomic &   sequence &           get &      energy &       fuse &        hydrogen \\\hline
             2 &     charge &      force &            mass &     gravity &     strong &    attract &         large &    strength &   distance & electromagnetic \\\hline
             3 &       huge &      force & electromagnetic &       macro &        way &      scale & concentration &       apply &       kind &          charge \\\hline
             4 &       atom &      dense &              go &    hydrogen &       slow &        get &          huge &    condense &       mass &           would \\\hline
             5 &     fusion &        get &       threshold &        core &      occur &       mass &     something &       start &    several &         jupiter \\\hline
             6 &     enough &   ignition &          proton &       force &        get &      close &       nucleus &     coulomb &     fusion &           would \\\hline
             7 &     energy &   pressure &        ignition &        mass &     little &       keep &       provide &      fusion &        get &        hydrogen \\\hline
             8 &     proton &       weak &         neutron & interaction &        one &         go &       nucleon &      cesium &      extra &             get \\\hline
            10 &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &         say &   distance &         combine \\\hline
            11 &        one &   hydrogen &          helium &          go &     proton &    neutron &          keep &      atomic &     detail &            fuse \\\hline
            12 &    gravity &      force &            weak & interaction &      apply &   strength &      distance &         ten &   relative &            next \\\hline
            13 &      force &         go &   electrostatic &        call &     charge &     magnet &          side &     coulomb &       know &       different \\\hline
            14 &      force &       atom &         nucleus &    electron &       much &   hydrogen &           get &      around &    coulomb &          charge \\\hline
            15 &      force &      scale &         gravity &       start &       weak &      orbit &          keep & fundamental &     around &        surprise \\\hline
    \end{tabular}    
    \end{tiny}

    \caption{\textbf{Topics.} We fit a topic model with $k = 15$ topics
    to sliding windows parsed from the two course video transcripts
    (see~\topicModelMethods), and identified 14 topics with non-zero weights.
    The table displays the 10 top-weighted words (columns) from each of the
    topics (rows) discovered by the model. The weights of these words are shown
    in Supplementary Figure~\ref{fig:topic-word-distributions}.}

    \label{tab:topics}
\end{table}

\newpage

\begin{tiny}
    \renewcommand*{\arraystretch}{1.4}
    \begin{longtable}{|r|p{0.375in}|p{1.275in}|p{3.5in}|}
        \hline
        \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Matched lecture transcript text} \\\hline
        1  &          FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction... \\\hline
2  &          FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[01:22.439--03:05.1]} ...this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate... \\\hline
3  &          FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this... \\\hline
4  &          FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[00:00.03--02:42.9]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an... \\\hline
5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline
6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in... \\\hline
7  &          FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[07:10.13--08:35.24]} ...reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances... \\\hline
8  &          FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[08:24.11--10:26.27]} ...just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances so if you get two of these protons close enough together and the strong force only applies over very very very small distances subatomic I should even say sub nucleic distances then the strong interaction comes into play so then you have the strong interaction actually keeping these charges together and once again just to keep it in in in mind relative to gravity it is 10 to the 38th 10 38 times the strength times the strength of gravity or it's about a hundred times stronger than the electromagnetic force so once again the reason why you don't see the strong force which is the strongest of all of the forces or the weak interaction applying over huge scales is that they really only they only their strength dies off super super fast even when you start going to large radius nucleuses of atoms they strength starts to die off especially for the strong force the reason why you don't see the electromagnetic force operating over large distances even though in theory it can like gravity is that you don't see the type of charge concentrations the way you see mass concentrations in the universe because the charge concentrations tend to sort them out they start to equalize if I have if I have some if I have some positive a huge positive charge there and a huge negative charge there they will attract each other and then become essentially a big lump of neutral charge and once they're a big lump of neutral charge they won't they won't interact with anything else in gravity if you have one mass and another mass and they attract each other then you have another mass that's even better to attracting each other at other masses and so it'll keep attracting things to it so it kind of snowballs the process and that's why gravity can operates on these really really large large objects in our universe in the universe as a whole \\\hline
9  &          FFF &  In your body, there are a tremendous amount of negatively-charged electrons. Your computer also contains a huge number of negatively-charged electrons. We know that like charges repel, but you and your computer are not repelled apart. Which of the following explains why? &  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[05:32.6--08:33.14]} ...force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating... \\\hline
10 &          FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this... \\\hline
11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline
12 &          FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this... \\\hline
13 &          FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 \textbf{[00:00.03--03:02.79]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each... \\\hline
14 &          FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction... \\\hline
15 &          FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \textbf{[05:38.66--06:59.96]} ...itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic... \\\hline
16 &          BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point... \\\hline
17 &          BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out... \\\hline
18 &          BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen...\newline\textbf{[05:50.32--07:00.25]} ...helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few... \\\hline
19 &          BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   \textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the... \\\hline
20 &          BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[03:36.34--05:04.75]} ...you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not... \\\hline
21 &          BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out... \\\hline
22 &          BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the... \\\hline
23 &          BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the... \\\hline
24 &          BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[02:26.05--04:49.15]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the... \\\hline
25 &          BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[05:47.08--07:01.75]} ...eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the... \\\hline
26 &          BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:26.05--03:51.37]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron... \\\hline
27 &          BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out... \\\hline
28 &          BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out... \\\hline
29 &          BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\\hline
30 &          BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]} ...most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out... \\\hline

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings for each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} (BoS) to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Time courses of topic correlations for each question may be found in
Supplementary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}

\begin{figure}[tp]
    \includegraphics[width=\textwidth]{figs/topic-word-distributions}

    \caption{\textbf{Topic-word distributions.} Each topic is defined by a distribution 
    of weights over words in the topic model's vocabulary (i.e., the union of all unique 
    words from the two lectures' transcripts, excluding stop-words, after 
    preprocessing). Each plot above displays the weights for the 50 words 
    weighted most heavily by an individual topic extracted from the lectures' contents 
    (see~\topicModelMethods).}

    \label{fig:topic-word-distributions}
\end{figure}

\begin{figure}[tp]
    \includegraphics[width=\textwidth]{figs/topic-weights}

    \caption{\textbf{Topic weights. A. Average topic weights for each lecture and
    question set}. The bar plots display each topic's average weight across
    lecture timepoints (top row) and questions (bottom row); colors denote topics.
    The top-weighted words from the highest-weighted topic from each lecture are
    displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
    top-weighted words from the full set of topics may be found in Supplementary
    Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
    weights.} Pairwise correlations between the distributions of average topic
    weights for each lecture and question set. Each row and column corresponds
    to a bar plot in Panel A. Also see Figure~\topicVariability~in the main text.}

    \label{fig:topics}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/forces-qcorrs-peaks}

    \caption{\textbf{Topic correlation time series plots for individual
    \textit{Four Fundamental Forces} questions.} Each panel displays a
    time series plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
    shaded regions in each curve denote the full width at half maxima (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}
    \label{fig:forces-peaks}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/bos-qcorrs-peaks}

    \caption{\textbf{Topic correlation time series plots for individual
    \textit{Birth of Stars} questions.} Each panel displays a
    time series plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Birth of Stars}. The
    shaded regions in each curve denote the full width at half maxima (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}

    \label{fig:bos-peaks}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.57\textwidth]{figs/word-overlap-comparison}

    \caption{\textbf{Topic correlations versus word overlap.} \textbf{A.
    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
    question about \textit{Four Fundamental Forces} was compared to each
    timepoint of the lecture (dots). The blue dots denote the correlations
    between the topic vectors, and the orange dots denote Jaccard similarities
    (defined as the number of unique words in common between the question and
    corresponding window of the lecture, divided by the total number of unique
    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
    of Stars}}. Same format as Panel A. \textbf{C. Topic correlation time series
    plots.} This panel is in the same format as Figure 4A from the main text,
    but here the example question highlighted in purple in Panel A has been
    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
    the example question highlighted in green in Panel B has been emphasized
    for the \textit{Birth of Stars} traces on the right. \textbf{D. Jaccard
    similarity time series plots.} These panels are in the same format as Panel
    C, but they display the Jaccard similarity time series for the same
    questions. \textbf{E. Question and lecture text.} The text for the example
    purple (left) and green (right) questions is shown on top, and the text
    from the best-matching intervals of the lectures (computed using topic
    correlations; see Supp.~Tab.~\ref{tab:matches}) are shown on the bottom.}

    \label{fig:compare-wordcount}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/model-comparison}

    \caption{\textbf{Comparing LDA vs. BERT embeddings.} The rows display the
    equivalents of main text Figure 2C (top row), Figures 4A and 4B (middle two
    rows), and Figure 3B (bottom row) computed using LDA (left) and BERT
    (right).}

    \label{fig:compare-bert}
\end{figure}

\newpage

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz1}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 1 responses.} Each panel is in the same format as the knowledge map
    displayed in the left panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

    \label{fig:knowledge-maps-q1}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz2}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 2 responses.} Each panel is in the same format as the knowledge map
    displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

    \label{fig:knowledge-maps-q2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz3}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 3 responses.} Each panel is in the same format as the knowledge map
    displayed in the right panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

    \label{fig:knowledge-maps-q3}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz1-2}

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 1 and 2 responses.} Each panel is in the same format as the learning map
    displayed in the left panel of Figure~\knowledgeMaps B in the main text,
    but here the maps are shown separately for each participant.}

    \label{fig:learning-maps-q1_2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz2-3}

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 2 and 3 responses.} Each panel is in the same format as the learning map
    displayed in the right panel of Figure~\knowledgeMaps B in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:learning-maps-q2_3}
\end{figure}

\end{document}

### 2024-12-23 paper/main.tex
rewrote fig 6 results section

@@
 three quizzes. Then, separately for each quiz, we fit a generalized linear
-mixed model (GLMM) with a logistic link function to explain the likelihood of
+mixed model (GLMM) with a logistic link function to explain the probability of
 correctly answering a question as a function of estimated knowledge for its
@@
 covered by the same lecture. Third, we estimated knowledge for each question
-about one lecture using only questions (from the same participant and quiz)
+about one lecture using only the questions (from the same participant and quiz)
 about the \textit{other} lecture (``Across-lecture'';
@@
 \textit{generalizability} of our approach by asking whether our predictions 
-held across the content areas of the two lectures.
-
-In performing these analyses, our null hypothesis is that the knowledge
-estimates we compute based on the quiz questions' embedding coordinates do
-\textit{not} provide useful information about participants' abilities to answer
-those questions. What result might we expect to see if this is the case? To
-gain an intuition for this scenario, consider the expected outcome if we
-carried out these same analyses using a simple proportion-correct measure in
-lieu of our knowledge estimates. Suppose a participant correctly answered $n$
-out of $q$ questions on a given quiz. If we hold out a single
-\textit{correctly} answered question, the proportion of remaining questions
-answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a
-single \textit{incorrectly} answered question, the proportion of remaining
-questions answered correctly would be $\frac{n}{q - 1}$. In this way, the
-proportion of correctly answered remaining questions is always \textit{lower}
-when the held-out question was answered correctly than when it was answered
-incorrectly. Because our knowledge estimates are computed as a weighted version
-of this same proportion-correct score (where each held-in question's weight
-reflects its embedding-space distance from the held-out question; see
-Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
-distributed), then we should expect to see this same inverse relationship
-between estimated knowledge and performance, on average. On the other hand, if
-the spatial relationships among the quiz questions' embeddings \textit{are}
-predictive of participants' knowledge about the questions' content, then we
-would expect \textit{higher} estimated knowledge for held-out correctly (versus
-incorrectly) answered questions.
-
-Before presenting our results, it is worth considering three possible
-explanations of why a participant might answer a given question correctly or
-incorrectly. One possibility is that the participant simply \textit{guessed}
-the answer. A second is that they selected the incorrect answer by mistake,
-despite ``knowing'' the correct answer (or vice versa). In both of these
-scenarios, the participant's knowledge about the question's content should be
-uninformative about their observed response. A third possibility is that the
-participant's response reflects their \textit{actual} knowledge about the
-question's content. In this case, we \textit{might} expect to see a positive
-relationship between the participant's knowledge and their likelihood of
-answering the question correctly. However, in order to see this positive
-relationship, the participant's knowledge must be structured in a way that is
-reflected (at least partially) by the embedding space. In other words, if the
-participant's performance reflects their true knowledge, but our text embedding
-space does not sufficiently capture the structure of that knowledge, then the
-knowledge estimates we generate will not be predictive of the participant's
-performance. In the extreme, if the embedding space is completely unstructured
-with respect to the content of the quiz questions, then we would expect to see
-the negative relationship between estimated knowledge and performance that we
-described above.
+could extend across the content areas of the two lectures. When computing these 
+knowledge estimates, we used a rebalancing procedure to ensure that (for a given 
+participant and quiz) the knowledge estimates for correctly and incorrectly 
+answered questions were based on the same proportion of correctly answered 
+questions (see~\nameref{subsec:glmm}).
+
+%In performing these analyses, our null hypothesis is that the knowledge
+%estimates we compute based on the quiz questions' embedding coordinates do
+%\textit{not} provide useful information about participants' abilities to answer
+%those questions. In other words, our estimates of participants' knowledge
+%for questions they answered correctly should (on average) be 
+%
+%In other words, since our knowledge estimates are computed 
+%as a weighted proportion-correct score (where each held-in question's weight reflects
+%its embedding-space distance from the held-out question; see
+%Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
+%distributed), then we should expect that, on average, 
+%
+%% note that with correction, pcorrect of held in questions is now $\frac{n - 1}{q - 1}$ regardless of held-out question's label
+%
+%==================================
+%
+%In performing these analyses, our null hypothesis is that the knowledge
+%estimates we compute based on the quiz questions' embedding coordinates do
+%\textit{not} provide useful information about participants' abilities to answer
+%those questions. What result might we expect to see if this is the case? To
+%gain an intuition for this scenario, consider the expected outcome if we
+%carried out these same analyses using a simple proportion-correct measure in
+%lieu of our knowledge estimates. Suppose a participant correctly answered $n$
+%out of $q$ questions on a given quiz. If we hold out a single
+%\textit{correctly} answered question, the proportion of remaining questions
+%answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a
+%single \textit{incorrectly} answered question, the proportion of remaining
+%questions answered correctly would be $\frac{n}{q - 1}$. In this way, the
+%proportion of correctly answered remaining questions is always \textit{lower}
+%when the held-out question was answered correctly than when it was answered
+%incorrectly. Because our knowledge estimates are computed as a weighted version
+%of this same proportion-correct score (where each held-in question's weight
+%reflects its embedding-space distance from the held-out question; see
+%Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
+%distributed), then we should expect to see this same inverse relationship
+%between estimated knowledge and performance, on average. On the other hand, if
+%the spatial relationships among the quiz questions' embeddings \textit{are}
+%predictive of participants' knowledge about the questions' content, then we
+%would expect \textit{higher} estimated knowledge for held-out correctly (versus
+%incorrectly) answered questions.
+%
+%Before presenting our results, it is worth considering three possible
+%explanations of why a participant might answer a given question correctly or
+%incorrectly. One possibility is that the participant simply \textit{guessed}
+%the answer. A second is that they selected the incorrect answer by mistake,
+%despite ``knowing'' the correct answer (or vice versa). In both of these
+%scenarios, the participant's knowledge about the question's content should be
+%uninformative about their observed response. A third possibility is that the
+%participant's response reflects their \textit{actual} knowledge about the
+%question's content. In this case, we \textit{might} expect to see a positive
+%relationship between the participant's knowledge and their likelihood of
+%answering the question correctly. However, in order to see this positive
+%relationship, the participant's knowledge must be structured in a way that is
+%reflected (at least partially) by the embedding space. In other words, if the
+%participant's performance reflects their true knowledge, but our text embedding
+%space does not sufficiently capture the structure of that knowledge, then the
+%knowledge estimates we generate will not be predictive of the participant's
+%performance. In the extreme, if the embedding space is completely unstructured
+%with respect to the content of the quiz questions, then we would expect to see
+%the negative relationship between estimated knowledge and performance that we
+%described above.
+
+%%\textbf{NOTES FOR REWRITING RESULTS}
+%%\begin{itemize}
+%%    \item all questions
+%%    \begin{itemize}
+%%        \item quiz 1: odds ratio $(OR) = 8.126$, 95\%\ $\textnormal{CI} = [3.116,\ 20.123]$, likelihood-ratio test statistic $(\lambda_{LR}) = 17.002,\ p < 0.001$
+%%        \item quiz 2: $OR = 14.902,\ 95\%\ \textnormal{CI} = [4.976,\ 39.807],\ \lambda_{LR} = 25.408,\ p < 0.001$
+%%        \item quiz 3: $OR = 37.409,\ 95\%\ \textnormal{CI} = [10.425,\ 107.145],\ \lambda_{LR} = 40.948,\ p < 0.001$
+%%        \item we can reliably predict success on individual held-out questions regardless of level of knowledge; predictive power grows as participants' knowledge space becomes better defined/structured
+%%    \end{itemize}
+%%    \item within-lecture
+%%    \begin{itemize}
+%%        \item quiz 1, lecture 1: $OR = 15.934,\ 95\%\ \textnormal{CI} = [5.173,\ 38.005],\ \lambda_{LR} = 40.971,\ p < 0.001$
+%%        \item quiz 1, lecture 2: $OR = 9.775,\ 95\%\ \textnormal{CI} = [2.93,\ 25.08],\ \lambda_{LR} = 13.924,\ p < 0.001$
+%%        \item quiz 2, lecture 1: $OR = 35.126,\ 95\%\ \textnormal{CI} = [5.113,\ 123.868],\ \lambda_{LR} = 32.251,\ p < 0.001$
+%%        \item quiz 2, lecture 2: $OR = 4.717,\ 95\%\ \textnormal{CI} = [2.021,\ 9.844],\ \lambda_{LR} = 16.788,\ p < 0.001$
+%%        \item quiz 3, lecture 1: $OR = 2.485,\ 95\%\ \textnormal{CI} = [0.724,\ 8.366],\ \lambda_{LR} = 1.984,\ p = 0.170$
+%%        \item quiz 3, lecture 2: $OR = 16.902,\ 95\%\ \textnormal{CI} = [3.353,\ 53.265],\ \lambda_{LR} = 23.233,\ p < 0.001$
+%%        \item can successfully distinguish between knowledge for questions about different content within a lecture, but may be susceptible to ceiling effects (considering questions included in model, across-participants avg prop correct on quiz3, lecture-1 questions was highest of any set of questions we analyzed (mean: 0.795, std: 0.236)
+%%    \end{itemize}
+%%    \item across-lecture
+%%    \begin{itemize}
+%%        \item quiz 1, lecture 1: $OR = 1.896,\ 95\%\ \textnormal{CI} = [0.419,\ 9.088],\ \lambda_{LR} = 0.712,\ p = 0.404$
+%%        \item quiz 1, lecture 2: $OR = 1.522,\ 95\%\ \textnormal{CI} = [0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$
+%%        \item quiz 2, lecture 1: $OR = 3.49,\ 95\%\ \textnormal{CI} = [0.739,\ 12.849],\ \lambda_{LR} = 3.266,\ p = 0.083$
+%%        \item quiz 2, lecture 2: $OR = 2.199,\ 95\%\ \textnormal{CI} = [0.711,\ 5.623],\ \lambda_{LR} = 2.304,\ p = 0.141$
+%%        \item quiz 3, lecture 1: $OR = 11.294,\ 95\%\ \textnormal{CI} = [1.375,\ 47.744],\ \lambda_{LR} = 10.396,\ p < 0.001$
+%%        \item quiz 3, lecture 2: $OR = 7.302,\ 95\%\ \textnormal{CI} = [1.077,\ 44.879],\ \lambda_{LR} = 4.708,\ p = 0.038$
+%%        \item ability to generalize across content areas depends on participants having structured knowledge about both (A) the content used to estimate knowledge, and (B) the content for which knowledge is estimated (quiz 1: have neither; quiz 2: have one but not the other; quiz 3: have both)
+%%    \end{itemize}
+%%\end{itemize}
+
+%When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
+%question based on all other Quiz~1 questions, we observed an outcome consistent
+%with our null hypothesis: higher estimated knowledge at the embedding
+%coordinate of a held-out question was associated with a lower likelihood of
+%answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
+%test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
+%26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
+%\textit{not} provide useful information about participants' Quiz~1 performance
+%when we aggregated across all question content areas. We speculated that this
+%might either indicate that the knowledge estimates are uninformative in
+%general, or about Quiz~1 performance in particular. This would be expected, for
+%example, if participants were guessing about the answers to the Quiz~1
+%questions (prior to having watched either lecture). When we repeated this
+%analysis for Quizzes~2 and~3, we found that higher estimated knowledge
+%for a given question predicted a \textit{greater} likelihood of answering it correctly
+%(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
+%[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
+%95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
+%results suggest that our knowledge estimates reliably predict participants'
+%performance on individual held-out quiz questions, but only after participants
+%have received at least some training.
+
+%When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
+%question based on all other Quiz~1 questions, we found that higher estimated
+%knowledge for a given question predicted a greater likelihood of answering it 
+%correctly (odds ratio $(OR) = 8.126$, 95\%\ $\textnormal{CI} = [3.116,\ 
+%20.123]$, likelihood-ratio test statistic $(\lambda_{LR}) = 17.002,\ p < 
+%0.001$). This relationship held and appeared to strengthen when we repeated this 
+%analysis for Quiz~2 ($OR = 14.902,\ 95\%\ \textnormal{CI} = [4.976,\ 39.807],\ 
+%\lambda_{LR} = 25.408,\ p < 0.001$), and again for Quiz~3 ($OR = 37.409,\ 95\%\ 
+%\textnormal{CI} = [10.425,\ 107.145],\ \lambda_{LR} = 40.948,\ p < 0.001$).
+%Taken together, these results suggest that our knowledge estimates reliably 
+%predict participants' performance on individual questions when aggregated across
+%all quiz content, and that their predictive power increases as participants gain
+%additional knowledge about the content captured by the text embedding space.
 
 When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
-question based on all other Quiz~1 questions, we observed an outcome consistent
-with our null hypothesis: higher estimated knowledge at the embedding
-coordinate of a held-out question was associated with a lower likelihood of
-answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
-test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
-26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
-\textit{not} provide useful information about participants' Quiz~1 performance
-when we aggregated across all question content areas. We speculated that this
-might either indicate that the knowledge estimates are uninformative in
-general, or about Quiz~1 performance in particular. This would be expected, for
-example, if participants were guessing about the answers to the Quiz~1
-questions (prior to having watched either lecture). When we repeated this
-analysis for Quizzes~2 and~3, we found that higher estimated knowledge
-for a given question predicted a \textit{greater} likelihood of answering it correctly
-(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
-[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
-95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
-results suggest that our knowledge estimates reliably predict participants'
-performance on individual held-out quiz questions, but only after participants
-have received at least some training.
-
-We observed a similar pattern of results when used this approach to estimate
-participants' knowledge about held-out questions from one lecture using their
-performance on other questions from the \textit{same} lecture. Specifically,
-for Quiz~1 questions (i.e., prior to watching either), participants' estimated
-knowledge for the embedding coordinates of held-out \textit{Four Fundamental
-Forces}-related questions estimated using other \textit{Four Fundamental
-Forces}-related questions did not reliably predict whether those questions were
-answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI}
-= [2.091,\ 2.622],\ p = 0.138$). The same was true of knowledge estimates for
-held-out \textit{Birth of Stars}-related questions based on other \textit{Birth
-of Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\
-\textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$). As in our analysis that
-included all questions, we speculate that these ``null'' results might reflect
-some degree of random guessing on Quiz~1. When we repeated these within-lecture
-analyses using questions from Quiz~2 (which participants took immediately after
-viewing \textit{Four Fundamental Forces} but prior to viewing \textit{Birth of
-Stars}), we found that they now reliably predicted success on \textit{Four
-Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\
-95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p < 0.001$) but not on
-\textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\
-95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.054$). Here, we speculate that
-participants might have been guessing about the \textit{Birth of Stars} content
-(e.g., prior to having watched it), whereas they might have been drawing on
-some structured knowledge about the \textit{Four Fundamental Forces} content
-(e.g., from having just watched it). When we applied this approach to Quiz~3
-responses (given immediately after viewing \textit{Birth of Stars}), we found
-that within-lecture knowledge estimates for \textit{Birth of Stars}-related
-questions could now reliably predict success on those questions ($OR = 5.467,\
-\lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.005$).
-However, within-lecture knowledge estimates for \textit{Four Fundamental
-Forces} questions answered on Quiz~3 were no longer directly related to the
-likelihood of successfully answering them and instead exhibited the inverse
-relationship we would expect to arise from unstructured knowledge (with respect
-to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\
-\textnormal{CI} = [10.695, 23.096],\ p < 0.001$). Speculatively, we suggest
-that this may reflect participants forgetting some of the \textit{Four
-Fundamental Forces} content (e.g., perhaps in favor of prioritizing encoding
-the just-watched \textit{Birth of Stars} content in preparation for the third
-quiz). If this forgetting happens in a relatively ``random'' way (with respect
-to spatial distance within the embedding space), then it could explain why some
-held-out questions about \textit{Four Fundamental Forces} were answered
-incorrectly, even if questions at nearby coordinates (i.e., about similar
-content) were answered correctly. This might lead our approach to over-estimate
-knowledge for held-out questions about ``forgotten'' knowledge that
-participants answered incorrectly. Taken together, these within-lecture results
-suggest that our approach can distinguish between questions about different
-content covered by a single lecture when participants have sufficiently
-structured knowledge about its contents, though this specificity may decrease
-with time since the relevant material was learned.
-
-Finally, we used this approach to estimate participants' knowledge about
-held-out questions from one lecture using their performance on questions from
-the \textit{other} lecture. Here we again observed a similar pattern of
-results, though with some notable differences. On Quiz~1, we found that
-participants' abilities to correctly answer questions about \textit{Four
-Fundamental Forces} could be predicted from their responses to questions about
-\textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\
-\textnormal{CI} = [6.224, 7.524],\ p = 0.038$) and similarly, that their
-ability to correctly answer \textit{Birth of Stars}-related questions could be
-predicted from their responses to \textit{Four Fundamental Forces}-related
-questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\ \textnormal{CI} = [5.656,
-6.843],\ p = 0.042$). Given the results from our analyses that included all
-questions and within-lecture predictions, we were surprised to find that the
-knowledge estimates could reliably (if weakly) predict participants'
-performance across content from different lectures. It is possible that this
-result reflects a combination of random guessing prior to training (leading to
-a weak effect size), alongside some coarse-scale structured knowledge that
-participants had about the content prior to watching either lecture. When we
-repeated this analysis using questions from Quiz~2, we found participants'
-responses to \textit{Four Fundamental Forces}-related questions did
-\textit{not} reliably predict their success on \textit{Birth of Stars}-related
-questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027,
-3.600],\ p = 0.124$), nor did their responses to \textit{Birth of
-Stars}-related questions reliably predict their success on \textit{Four
-Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\
-95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.093$). These ``prediction
-failures'' appear to come from the fact that any signal derived from
-participants' knowledge about the content of the \textit{Birth of Stars}
-lecture (prior to watching it) is overwhelmed by the much more dramatic increase in
-their knowledge about the content of the \textit{Four Fundamental Forces}
-(which they watched just prior to taking Quiz~2). This is reflected in their
-Quiz~2 performance for questions about each lecture (mean proportion correct
-for \textit{Four Fundamental Forces}-related questions on Quiz~2: $0.77$; mean
-proportion correct for \textit{Birth of Stars}-related questions on Quiz~2:
-$0.36$). When we carried out these across-lecture knowledge predictions using
-questions from Quiz~3 (when participants had now viewed \textit{both}
-lectures), we could again reliably predict success on questions about both
-\textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\
-\textnormal{CI} = [9.126, 18.476],\ p = 0.003$) and \textit{Birth of Stars}
-($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\
-p = 0.016$) using responses to questions about the other lecture's content.
-Across all three versions of these analyses, our results suggest that (by and
-large) our knowledge estimates can reliably predict participants' abilities to
-answer individual quiz questions, distinguish between questions about similar
-content, and generalize across content areas, provided that participants' quiz
-responses reflect a minimum level of ``real'' knowledge about both content on
-which these predictions are based and that for which they are made.
+question based on all other Quiz~1 questions, we found that higher estimated
+knowledge for a given question predicted a greater likelihood of answering it 
+correctly (odds ratio $(OR) = 8.126$, 95\%\ $\textnormal{CI} = [3.116,\ 
+20.123]$, likelihood-ratio test statistic $(\lambda_{LR}) = 17.002,\ p < 
+0.001$). This relationship held when we repeated this analysis for Quiz~2 ($OR 
+= 14.902,\ 95\%\ \textnormal{CI} = [4.976,\ 39.807],\ \lambda_{LR} = 25.408,\ 
+p < 0.001$) and again for Quiz~3 ($OR = 37.409,\ 95\%\ \textnormal{CI} = 
+[10.425,\ 107.145],\ \lambda_{LR} = 40.948,\ p < 0.001$). Taken together, these 
+results suggest that our knowledge estimates can reliably predict participants' 
+performance on individual questions when aggregated across all quiz content.
+
+We observed a similar set of results when we restricted our estimates of
+participants' knowledge for questions about each lecture to consider only
+their performance on other questions about the \textit{same} lecture.
+Specifically, for Quiz~1, participants' knowledge of \textit{Four Fundamental 
+Forces}-related questions, estimated from their performance on other 
+\textit{Four Fundamental Forces}-related questions, was predictive of their 
+ability to answer those questions correctly ($OR = 15.934,\ 95\%\ 
+\textnormal{CI} = [5.173,\ 38.005],\ \lambda_{LR} = 40.971,\ p = 0.001$). The 
+same was true of participants' estimated knowledge for \textit{Birth of 
+Stars}-related questions based on their performance on other \textit{Birth of 
+Stars}-related questions ($OR = 9.775,\ 95\%\ \textnormal{CI} = [2.93,\ 
+25.08],\ \lambda_{LR} = 13.924,\ p = 0.001$). These within-lecture knowledge
+estimates also predicted success on questions about both lectures when we 
+computed them analogously for Quiz~2 (\textit{Four Fundamental Forces}: $OR = 
+35.126,\ 95\%\ \textnormal{CI} = [5.113,\ 123.868],\ \lambda_{LR} = 32.251,\ 
+p < 0.001$; \textit{Birth of Stars}: $OR = 4.717,\ 95\%\ \textnormal{CI} = 
+[2.021,\ 9.844],\ \lambda_{LR} = 16.788,\ p < 0.001$). For Quiz~3, we found that
+within-lecture knowledge estimates predicted participants' success on 
+\textit{Birth of Stars}-related questions ($OR = 16.902,\ 95\%\ \textnormal{CI} 
+= [3.353,\ 53.265],\ \lambda_{LR} = 23.233,\ p < 0.001$) but not on \textit{Four 
+Fundamental Forces}-related questions ($OR = 2.485,\ 95\%\ \textnormal{CI} = 
+[0.724,\ 8.366],\ \lambda_{LR} = 1.984,\ p = 0.170$). This may indicate that the 
+within-lecture knowledge estimates are susceptible to ceiling effects in 
+participants' quiz performance. On Quiz~3, after viewing both lectures, no 
+participant answered more than three \textit{Four Fundamental Forces}-related 
+questions incorrectly, and all but five participants (out of 50) answered two or 
+fewer questions incorrectly. (This was the only subset of questions about either 
+lecture, across all three quizzes, for which this was true.) Because of this, 
+when we held out one incorrectly answered \textit{Four Fundamental Forces} 
+question from a given participant's Quiz~3 responses and estimated their 
+knowledge at its embedding coordinate using the remaining \textit{Four 
+Fundamental Forces} questions they answered, for 90\% of participants, that 
+estimate leveraged information about at most a single other question they were 
+\textit{not} able to correctly answer. This broad homogeneity in participants' success on questions used to estimate their knowledge may have hurt our ability 
+to accurately characterize the specific (and by Quiz~3, relatively few) aspects 
+of the lecture content they did \textit{not} know about. Taken together, these 
+results suggest that our knowledge estimates can reliably distinguish between 
+questions about different content covered by a single lecture, provided there is 
+sufficient diversity in participants' quiz responses to extract meaningful 
+information about both what they know and what they do not know.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, when we estimated participants' knowledge for each question about one
+lecture using their performance on questions (from the same quiz) about the
+\textit{other} lecture, we observed a somewhat different pattern of results.
+Here we found that before viewing either lecture (i.e., on Quiz~1),
+participants' abilities to answer \textit{Four Fundamental Forces}-related
+questions could not be predicted from their responses to \textit{Birth of
+Stars}-related questions ($OR = 1.896,\ 95\%\ \textnormal{CI} = [0.419,\ 
+9.088],\ \lambda_{LR} = 0.712,\ p = 0.404$), nor could their abilities to 
+answer \textit{Birth of Stars}-related questions be predicted from their 
+responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\ 
+95\%\ \textnormal{CI} = [0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$).
+We similarly found that participants' success on questions about either lecture 
+could not be predicted given their responses to questions about the other 
+lecture after viewing \textit{Four Fundamental Forces} but before viewing \textit{Birth of Stars} (i.e., on Quiz~2; \textit{Four Fundamental Forces} 
+questions given \textit{Birth of Stars} questions: $OR = 3.49,\ 95\%\ 
+\textnormal{CI} = [0.739,\ 12.849],\ \lambda_{LR} = 3.266,\ p = 0.083$; 
+\textit{Birth of Stars} questions given \textit{Four Fundamental Forces} 
+questions: $OR = 2.199,\ 95\%\ \textnormal{CI} = [0.711,\ 5.623],\ 
+\lambda_{LR} = 2.304,\ p = 0.141$). Only after viewing \textit{both} lectures 
+(i.e., on Quiz~3) did these across-lecture knowledge estimates reliably predict 
+participants' success on individual quiz questions (\textit{Four Fundamental 
+Forces} questions given \textit{Birth of Stars} questions: $OR = 11.294,\ 
+95\%\ \textnormal{CI} = [1.375,\ 47.744],\ \lambda_{LR} = 10.396,\ p < 0.001$; 
+\textit{Birth of Stars} questions given \textit{Four Fundamental Forces} 
+questions: $OR = 7.302,\ 95\%\ \textnormal{CI} = [1.077,\ 44.879],\ 
+\lambda_{LR} = 4.708,\ p = 0.038$). Taken together, these results suggest that 
+our knowledge estimates can be used to predict participants' success across 
+content areas once they have received some training on both the content about 
+which their knowledge is estimated, and the content used to construct these
+estimates.
 
@@
 (Fig.~\ref{fig:knowledge-maps}A). Intuitively, the knowledge map constructed
-from a given quiz's responses provides a visualization of how ``much''
+from a given quiz's responses provides a visualization of ``how much''
 participants knew about any content expressible by the fitted text embedding

### 2025-01-04 paper/main.tex
make "proportion-correct" hyphenation consistent throughout

@@
 distance at which performance becomes statistically indistinguishable from a
-simple proportion correct score (see~\nameref{subsec:smoothness}). This
+simple proportion-correct score (see~\nameref{subsec:smoothness}). This
 suggests that, at least within the region of text embedding space covered by
@@
 sphere that the participant answered correctly, and averaged these per-radius
-proportion correct scores across reference questions that were answered
+proportion-correct scores across reference questions that were answered
 correctly, and those that were answered incorrectly. This resulted in two
@@
 reference question (i.e., sphere radius) at which each of these two sequences
-of per-radius proportion correct scores intersected the 95\% confidence
+of per-radius proportion-correct scores intersected the 95\% confidence
 interval for the overall proportion correct (i.e., analogous to the black error

### 2025-01-09 paper/main.tex
cleaned up fig 6 results section

@@
 participant and quiz) the knowledge estimates for correctly and incorrectly
-answered questions were based on the same proportion of correctly answered
+answered questions were computed from the same proportion of correctly answered
 questions (see~\nameref{subsec:glmm}).
-
-%In performing these analyses, our null hypothesis is that the knowledge
-%estimates we compute based on the quiz questions' embedding coordinates do
-%\textit{not} provide useful information about participants' abilities to answer
-%those questions. In other words, our estimates of participants' knowledge
-%for questions they answered correctly should (on average) be
-%
-%In other words, since our knowledge estimates are computed
-%as a weighted proportion-correct score (where each held-in question's weight reflects
-%its embedding-space distance from the held-out question; see
-%Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
-%distributed), then we should expect that, on average,
-%
-%% note that with correction, pcorrect of held in questions is now $\frac{n - 1}{q - 1}$ regardless of held-out question's label
-%
-%==================================
-%
-%In performing these analyses, our null hypothesis is that the knowledge
-%estimates we compute based on the quiz questions' embedding coordinates do
-%\textit{not} provide useful information about participants' abilities to answer
-%those questions. What result might we expect to see if this is the case? To
-%gain an intuition for this scenario, consider the expected outcome if we
-%carried out these same analyses using a simple proportion-correct measure in
-%lieu of our knowledge estimates. Suppose a participant correctly answered $n$
-%out of $q$ questions on a given quiz. If we hold out a single
-%\textit{correctly} answered question, the proportion of remaining questions
-%answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a
-%single \textit{incorrectly} answered question, the proportion of remaining
-%questions answered correctly would be $\frac{n}{q - 1}$. In this way, the
-%proportion of correctly answered remaining questions is always \textit{lower}
-%when the held-out question was answered correctly than when it was answered
-%incorrectly. Because our knowledge estimates are computed as a weighted version
-%of this same proportion-correct score (where each held-in question's weight
-%reflects its embedding-space distance from the held-out question; see
-%Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
-%distributed), then we should expect to see this same inverse relationship
-%between estimated knowledge and performance, on average. On the other hand, if
-%the spatial relationships among the quiz questions' embeddings \textit{are}
-%predictive of participants' knowledge about the questions' content, then we
-%would expect \textit{higher} estimated knowledge for held-out correctly (versus
-%incorrectly) answered questions.
-%
-%Before presenting our results, it is worth considering three possible
-%explanations of why a participant might answer a given question correctly or
-%incorrectly. One possibility is that the participant simply \textit{guessed}
-%the answer. A second is that they selected the incorrect answer by mistake,
-%despite ``knowing'' the correct answer (or vice versa). In both of these
-%scenarios, the participant's knowledge about the question's content should be
-%uninformative about their observed response. A third possibility is that the
-%participant's response reflects their \textit{actual} knowledge about the
-%question's content. In this case, we \textit{might} expect to see a positive
-%relationship between the participant's knowledge and their likelihood of
-%answering the question correctly. However, in order to see this positive
-%relationship, the participant's knowledge must be structured in a way that is
-%reflected (at least partially) by the embedding space. In other words, if the
-%participant's performance reflects their true knowledge, but our text embedding
-%space does not sufficiently capture the structure of that knowledge, then the
-%knowledge estimates we generate will not be predictive of the participant's
-%performance. In the extreme, if the embedding space is completely unstructured
-%with respect to the content of the quiz questions, then we would expect to see
-%the negative relationship between estimated knowledge and performance that we
-%described above.
-
-%%\textbf{NOTES FOR REWRITING RESULTS}
-%%\begin{itemize}
-%%    \item all questions
-%%    \begin{itemize}
-%%        \item quiz 1: odds ratio $(OR) = 8.126$, 95\%\ $\textnormal{CI} = [3.116,\ 20.123]$, likelihood-ratio test statistic $(\lambda_{LR}) = 17.002,\ p < 0.001$
-%%        \item quiz 2: $OR = 14.902,\ 95\%\ \textnormal{CI} = [4.976,\ 39.807],\ \lambda_{LR} = 25.408,\ p < 0.001$
-%%        \item quiz 3: $OR = 37.409,\ 95\%\ \textnormal{CI} = [10.425,\ 107.145],\ \lambda_{LR} = 40.948,\ p < 0.001$
-%%        \item we can reliably predict success on individual held-out questions regardless of level of knowledge; predictive power grows as participants' knowledge space becomes better defined/structured
-%%    \end{itemize}
-%%    \item within-lecture
-%%    \begin{itemize}
-%%        \item quiz 1, lecture 1: $OR = 15.934,\ 95\%\ \textnormal{CI} = [5.173,\ 38.005],\ \lambda_{LR} = 40.971,\ p < 0.001$
-%%        \item quiz 1, lecture 2: $OR = 9.775,\ 95\%\ \textnormal{CI} = [2.93,\ 25.08],\ \lambda_{LR} = 13.924,\ p < 0.001$
-%%        \item quiz 2, lecture 1: $OR = 35.126,\ 95\%\ \textnormal{CI} = [5.113,\ 123.868],\ \lambda_{LR} = 32.251,\ p < 0.001$
-%%        \item quiz 2, lecture 2: $OR = 4.717,\ 95\%\ \textnormal{CI} = [2.021,\ 9.844],\ \lambda_{LR} = 16.788,\ p < 0.001$
-%%        \item quiz 3, lecture 1: $OR = 2.485,\ 95\%\ \textnormal{CI} = [0.724,\ 8.366],\ \lambda_{LR} = 1.984,\ p = 0.170$
-%%        \item quiz 3, lecture 2: $OR = 16.902,\ 95\%\ \textnormal{CI} = [3.353,\ 53.265],\ \lambda_{LR} = 23.233,\ p < 0.001$
-%%        \item can successfully distinguish between knowledge for questions about different content within a lecture, but may be susceptible to ceiling effects (considering questions included in model, across-participants avg prop correct on quiz3, lecture-1 questions was highest of any set of questions we analyzed (mean: 0.795, std: 0.236)
-%%    \end{itemize}
-%%    \item across-lecture
-%%    \begin{itemize}
-%%        \item quiz 1, lecture 1: $OR = 1.896,\ 95\%\ \textnormal{CI} = [0.419,\ 9.088],\ \lambda_{LR} = 0.712,\ p = 0.404$
-%%        \item quiz 1, lecture 2: $OR = 1.522,\ 95\%\ \textnormal{CI} = [0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$
-%%        \item quiz 2, lecture 1: $OR = 3.49,\ 95\%\ \textnormal{CI} = [0.739,\ 12.849],\ \lambda_{LR} = 3.266,\ p = 0.083$
-%%        \item quiz 2, lecture 2: $OR = 2.199,\ 95\%\ \textnormal{CI} = [0.711,\ 5.623],\ \lambda_{LR} = 2.304,\ p = 0.141$
-%%        \item quiz 3, lecture 1: $OR = 11.294,\ 95\%\ \textnormal{CI} = [1.375,\ 47.744],\ \lambda_{LR} = 10.396,\ p < 0.001$
-%%        \item quiz 3, lecture 2: $OR = 7.302,\ 95\%\ \textnormal{CI} = [1.077,\ 44.879],\ \lambda_{LR} = 4.708,\ p = 0.038$
-%%        \item ability to generalize across content areas depends on participants having structured knowledge about both (A) the content used to estimate knowledge, and (B) the content for which knowledge is estimated (quiz 1: have neither; quiz 2: have one but not the other; quiz 3: have both)
-%%    \end{itemize}
-%%\end{itemize}
-
-%When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
-%question based on all other Quiz~1 questions, we observed an outcome consistent
-%with our null hypothesis: higher estimated knowledge at the embedding
-%coordinate of a held-out question was associated with a lower likelihood of
-%answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
-%test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
-%26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
-%\textit{not} provide useful information about participants' Quiz~1 performance
-%when we aggregated across all question content areas. We speculated that this
-%might either indicate that the knowledge estimates are uninformative in
-%general, or about Quiz~1 performance in particular. This would be expected, for
-%example, if participants were guessing about the answers to the Quiz~1
-%questions (prior to having watched either lecture). When we repeated this
-%analysis for Quizzes~2 and~3, we found that higher estimated knowledge
-%for a given question predicted a \textit{greater} likelihood of answering it correctly
-%(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
-%[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
-%95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
-%results suggest that our knowledge estimates reliably predict participants'
-%performance on individual held-out quiz questions, but only after participants
-%have received at least some training.
-
-%When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
-%question based on all other Quiz~1 questions, we found that higher estimated
-%knowledge for a given question predicted a greater likelihood of answering it
-%correctly (odds ratio $(OR) = 8.126$, 95\%\ $\textnormal{CI} = [3.116,\
-%20.123]$, likelihood-ratio test statistic $(\lambda_{LR}) = 17.002,\ p <
-%0.001$). This relationship held and appeared to strengthen when we repeated this
-%analysis for Quiz~2 ($OR = 14.902,\ 95\%\ \textnormal{CI} = [4.976,\ 39.807],\
-%\lambda_{LR} = 25.408,\ p < 0.001$), and again for Quiz~3 ($OR = 37.409,\ 95\%\
-%\textnormal{CI} = [10.425,\ 107.145],\ \lambda_{LR} = 40.948,\ p < 0.001$).
-%Taken together, these results suggest that our knowledge estimates reliably
-%predict participants' performance on individual questions when aggregated across
-%all quiz content, and that their predictive power increases as participants gain
-%additional knowledge about the content captured by the text embedding space.
 
@@
 estimate leveraged information about at most a single other question they were
-\textit{not} able to correctly answer. This broad homogeneity in participants' success on questions used to estimate their knowledge may have hurt our ability
+\textit{not} able to correctly answer. This broad homogeneity in participants'
+success on questions used to estimate their knowledge may have hurt our ability
 to accurately characterize the specific (and by Quiz~3, relatively few) aspects
@@
 information about both what they know and what they do not know.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 content areas once they have received some training on both the content about
-which their knowledge is estimated, and the content used to construct these
+which their knowledge is estimated and the content used to construct these
 estimates.

### 2025-01-09 paper/main.tex
add description of rebalancing procedure to GLMM methods section

@@
 question (i.e., excluding questions about general physics knowledge), we
-computed analogous knowledge estimates based on all other questions the
-participant answered on the same quiz about (1) the same lecture as the target
-question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2)
-the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions},
+computed analogous knowledge estimates based on two different subsets of
+questions the participant answered on the same quiz: (1) all \textit{other}
+questions about the same lecture as the target question (``Within-lecture'';
+Fig.~\ref{fig:predictions}, middle rows), and (2) all questions about the other
+of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions},
 bottom rows).
+
+In performing these analyses, our null hypothesis is that the knowledge
+estimates we compute based on the quiz questions' embedding coordinates do
+\textit{not} provide useful information about participants' abilities to answer
+those questions---in other words, that there is no meaningful difference (on
+average) between the knowledge estimates we compute for questions participants
+answered correctly and those they answered incorrectly. Specifically, since we
+estimate knowledge for a given embedding coordinate as a weighted
+proportion-correct score (where each question's weight reflects its
+embedding-space distance from the target coordinate; see Eqn.~\ref{eqn:prop}),
+if these weights are uninformative (e.g., randomly distributed), then our
+estimates of participants' knowledge should be equivalent (on average) to the
+\textit{unweighted} proportion of correctly answered questions used to compute
+them. In general, for a given participant and quiz, this expected value (i.e.,
+that participant's proportion-correct score on that quiz) is the same for any
+coordinate in the embedding space (e.g., any lecture timepoint, quiz question,
+etc.). However, in the ``All questions'' and ``Within-lecture'' versions of the
+analyses shown in Figure~\ref{fig:predictions}, we estimate each participant's
+knowledge for each target question using all \textit{other} questions (or all
+\textit{other} questions about the same lecture) they answered on the same quiz.
+This introduces a systematic dependency between a participant's success on a
+target question and their proportion-correct score on the questions available to
+estimate their knowledge for it. For example, suppose a participant correctly
+answered $n$ out of $q$ questions on a given quiz. If we hold out a single
+\textit{correctly} answered question as the target, the proportion of remaining
+questions answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold
+out a single \textit{incorrectly} answered question, the proportion of remaining
+questions answered correctly would be $\frac{n}{q - 1}$. Thus, the proportion of
+correctly answered remaining questions (and therefore the null-hypothesized
+value of a knowledge estimate computed from them) is always \textit{lower} for
+target questions a participant answered correctly than for those they answered
+incorrectly.
+
+To correct for this baseline inverse relationship between a participant's
+success on a target question and their estimated knowledge for it, we used a
+rebalancing procedure that ensured our knowledge estimates for questions each
+participant answered correctly and incorrectly were computed from the
+\textit{same} proportion of correctly answered questions. For each target
+question on a given participant's quiz, we identified all remaining questions
+with the opposite ``correctness'' label (i.e., if the target question was
+answered correctly, we identified all remaining incorrectly answered questions,
+and vice versa). We then held out each of these opposite-label questions, in
+turn, along with the target question, and estimated the participant's knowledge
+for the target question using all \textit{other} remaining questions. Since each
+of these subsets of remaining questions was constructed by holding out one
+correctly answered question and one incorrectly answered question from the
+participant's quiz, if the participant correctly answered $n$ out of $q$
+questions total, then their proportion-correct score on each subset of questions
+used to estimate their knowledge for the target question is $\frac{n-1}{q-2}$,
+regardless of whether they answered the target question correctly or
+incorrectly. Finally, averaging over these per-subset knowledge estimates
+yielded a rebalanced estimate of the participant's knowledge for the target
+question that leveraged information from all remaining questions' embedding
+coordinates, but whose expected value under our null hypothesis was the same as
+that of each individual subset ($\frac{n-1}{q-2}$). By equalizing the
+null-hypothesized values of knowledge estimates for correctly and incorrectly
+answered questions, this procedure ensures that any meaningful relationships we
+observe between participants' estimated knowledge for individual quiz questions
+and their ability to answer them are attributable to the predictive power of the
+embedding-space distances used to weight questions' contributions to the
+knowledge estimates, rather than an artifact of our estimation procedure. Note
+that if a participant answered all or no questions on a given quiz correctly,
+their responses contained no opposite-label questions with which to perform this
+rebalancing, and we therefore excluded their data from our analyses for that
+quiz. We used this rebalancing procedure when constructing knowledge estimates
+for the ``All questions'' and ``Within-lecture'' versions of the analyses shown
+in Figure~\ref{fig:predictions}, but not for the ``Across-lecture'' analyses as,
+in this case, the target questions and the questions used to estimate
+participants' knowledge for them were drawn from different subsets of quiz
+questions (those about one lecture, and those about the other), and were
+therefore independent.
 

### 2025-01-09 paper/main.tex
minor typo fixes

@@
 whether estimates of participants' knowledge at the embedding coordinates of
-individual quiz questions could be used to reliably predict their ability to
+individual quiz questions could be used to reliably predict their abilities to
 correctly answer those questions. In essence, we treated each question a given
@@
 prior to embedding them in the 2D space. When we inverted the embedded vectors
-(e.g., to estimate topic vectors or word clouds, as in
+(e.g., to estimate topic vectors for word clouds, as in
 Fig.~\ref{fig:knowledge-maps}C), we passed the inverted (log-transformed)

### 2025-01-10 paper/main.tex
revisions to GLMM methods section

@@
 This introduces a systematic dependency between a participant's success on a
-target question and their proportion-correct score on the questions available to
-estimate their knowledge for it. For example, suppose a participant correctly
-answered $n$ out of $q$ questions on a given quiz. If we hold out a single
-\textit{correctly} answered question as the target, the proportion of remaining
-questions answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold
-out a single \textit{incorrectly} answered question, the proportion of remaining
-questions answered correctly would be $\frac{n}{q - 1}$. Thus, the proportion of
-correctly answered remaining questions (and therefore the null-hypothesized
-value of a knowledge estimate computed from them) is always \textit{lower} for
-target questions a participant answered correctly than for those they answered
-incorrectly.
+target question and their proportion-correct score on the remaining questions
+available to estimate their knowledge for it. For example, suppose a participant
+correctly answered $n$ out of $q$ questions on a given quiz. If we hold out a
+single \textit{correctly} answered question as the target, the proportion of
+remaining questions answered correctly would be $\frac{n - 1}{q - 1}$. Whereas
+if we hold out a single \textit{incorrectly} answered question, the proportion
+of remaining questions answered correctly would be $\frac{n}{q - 1}$. Thus, the
+proportion of correctly answered remaining questions (and therefore the
+null-hypothesized value of a knowledge estimate computed from them) is always
+\textit{lower} for target questions a participant answered correctly than for
+those they answered incorrectly.
 
@@
 observe between participants' estimated knowledge for individual quiz questions
-and their ability to answer them are attributable to the predictive power of the
-embedding-space distances used to weight questions' contributions to the
-knowledge estimates, rather than an artifact of our estimation procedure. Note
-that if a participant answered all or no questions on a given quiz correctly,
-their responses contained no opposite-label questions with which to perform this
-rebalancing, and we therefore excluded their data from our analyses for that
-quiz. We used this rebalancing procedure when constructing knowledge estimates
-for the ``All questions'' and ``Within-lecture'' versions of the analyses shown
-in Figure~\ref{fig:predictions}, but not for the ``Across-lecture'' analyses as,
-in this case, the target questions and the questions used to estimate
-participants' knowledge for them were drawn from different subsets of quiz
-questions (those about one lecture, and those about the other), and were
-therefore independent.
+and their abilities to correctly answer them are attributable to the predictive
+power of the embedding-space distances used to weight questions' contributions
+to the knowledge estimates, rather than an artifact of our estimation procedure.
+Note that if a participant answered all or no questions on a given quiz
+correctly, their responses contained no opposite-label questions with which to
+perform this rebalancing, and we therefore excluded their data from our analyses
+for that quiz. We used this rebalancing procedure when constructing knowledge
+estimates for the ``All questions'' and ``Within-lecture'' versions of the
+analyses shown in Figure~\ref{fig:predictions}, but not for the
+``Across-lecture'' analyses as, in this case, the target questions and the
+questions used to estimate participants' knowledge for them were drawn from
+different subsets of quiz questions (those about one lecture, and those about
+the other), and were therefore independent.
 
@@
 (GLMM) with a logistic link function to the set of knowledge estimates for all
-questions that participants answered on the given quiz. We implemented these
-models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and
-fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
-Specifically, we initially fit each model with the maximal random effects
-structure afforded by our design, which we identified as:
+questions (or all questions about a particular lecture) that participants
+answered on the given quiz. We implemented these models in \texttt{R} using the
+\texttt{lme4} package~\citep{BateEtal15a} and fit them following guidance
+from~\citet{BateEtal15b} and \citet{MatuEtal17}. Specifically, we initially fit
+each model with the maximal random effects structure afforded by our design,
+which we identified as:
 \[
@@
 Note that with our coding scheme, identifiers for each \texttt{question} are
-implicitly nested within levels of \texttt{lecture} and do not require explicit
-nesting in our model formula. We then iteratively removed random effects from
-the maximal model until it successfully converged with a full rank (i.e., non-singular)
-random effects variance-covariance matrix.
+implicitly nested within levels of \texttt{lecture} and so do not require
+explicit nesting in our model formula. We then iteratively removed random
+effects from the maximal model until it successfully converged with a full-rank
+random effects variance-covariance matrix. We obtained the odds ratios reported
+in Figure~\ref{fig:predictions} by exponentiating the estimated coefficient for
+``\texttt{knowledge}'' from each fitted model. Conceptually, these odds ratios
+represent how many times greater the odds are that a given participant will
+answer a given question correctly if their estimated knowledge for its embedding
+coordinate is 1, compared to if it is 0. We estimated 95\% confidence intervals
+for each odds ratio by generating 10,000 random subsamples (of full size, with
+replacement) from the data used to fit each model, and refitting the models to
+each subsample to obtain bootstrap distributions of 10,000 odds ratios.
 
 To assess the predictive value of our knowledge estimates, we compared each
-GLMM's ability to discriminate between correctly and incorrectly answered
-questions to that of an analogous model that did \textit{not} consider estimated
-knowledge. Specifically, we used the same sets of observations with which we
-fit each ``full'' model to fit a second ``null'' model, with the formula:
-\[
-    \mathtt{accuracy \sim (1\ \vert\ participant) + (1\ \vert\ question)}
-\]
-where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above.
-As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' is as defined above.
-We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT).
-Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrap procedure~\citep{DaviHink97,HaleHojs14}.
-For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
-We then re-fit both the null and full models to this simulated sample and compared them via an LRT.
-This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
-We computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r+1}{n+1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than our observed value and $n$ is the number of simulations we ran (1,000).
+GLMM's ability to explain participants' success on individual quiz questions to
+that of an analogous model which assumed (as we assume under our null hypothesis) that knowledge estimates for correctly and incorrectly answered
+questions did \textit{not} systematically differ, on average. Specifically, we
+used the same sets of observations with which we fit each ``full'' model to fit
+a second ``null'' model that had the same random effects structure, but in which
+the coefficient for the fixed effect of ''\texttt{knowledge}'' was fixed at 0
+(i.e., we removed this term from the null model). We then compared each full
+model to its reduced (null) equivalent using a likelihood-ratio test (LRT).
+Because the standard asymptotic $\chi^2_d$ approximation of the null
+distribution for the LRT statistic ($\lambda_{LR}$) can be anti-conservative for
+finite sample sizes~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed
+$p$-values for these tests using a parametric bootstrap
+procedure~\citep{DaviHink97,HaleHojs14}. For each of 10,000 bootstraps, we used
+the fitted null model to simulate a sample of observations of equal size to our
+original sample. We then re-fit both the null and full models to this simulated
+sample and compared them via an LRT. This yielded a distribution of
+$\lambda_{LR}$ statistics we may expect to observe given data that conforms to
+our null hypothesis. We computed a corrected $p$-value for our observed
+$\lambda_{LR}$ as $\frac{r+1}{n+1}$, where $r$ is the number of simulated model
+comparisons that yielded a $\lambda_{LR}$ greater than our observed value and
+$n$ is the number of simulations we ran (10,000).
 

### 2025-01-10 paper/main.tex
minor updates to fig 6 results and methods

@@
 correlations between any lecture timepoint and question, taken over all
-timepoints in the given lecture, and all five questions \textit{about} that lecture appearing on the given quiz.
-We also define $f(s, \Omega)$ as the
+timepoints in the given lecture, and all five questions \textit{about} that
+lecture appearing on the given quiz. We also define $f(s, \Omega)$ as the
 $s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
-Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
-the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
+Here $t$ indexes the set of lecture topic vectors $L$, and $i$ and $j$ index
+the topic vectors of questions $Q$ used to estimate the knowledge trace. Note
 that ``correct'' denotes the set of indices of the questions the participant
@@
 Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
-vectors (e.g., the topic vector from one timepoint in a lecture, $x$, and the
-topic vector for one question, $y$), normalized by the minimum and maximum
-correlations (across all timepoints $t$ and questions $Q$) to range between 0
+vectors (e.g., the topic vector $x$ for one timepoint in a lecture and the
+topic vector $y$ for one question), normalized by the minimum and maximum
+correlations (across all timepoints $t$ and questions $j$) to range between 0
 and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average

### 2025-01-11 paper/main.tex
add mention of fig 6 results to abstract, intro, discussion

@@
 these embeddings, along with participants' quiz responses, to track how the
-learners' knowledge changed after watching each video. Our findings show how a
-small set of quiz questions may be used to obtain rich and meaningful
-high-resolution insights into what each learner knows, and how their knowledge
-changes over time as they learn.
+learners' knowledge changed after watching each video and predict their success
+on individual quiz questions. Our findings show how a small set of quiz
+questions may be used to obtain rich and meaningful high-resolution insights
+into what each learner knows, and how their knowledge changes over time as they
+learn.
 
@@
 online courses to inform, fit, and test models of real-world conceptual
-learning. We also provide a demonstration of how our models can be used to
+learning. We show that these models recover meaningful relationships between
+concepts presented during course lectures and tested by assessments, and that
+these relationships can be leveraged to predict students' success on individual
+quiz questions. We also provide a demonstration of how our models can be used to
 construct ``maps'' of what students know, and how their knowledge changes with
@@
 (Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
-estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
-Finally, we use our framework to construct visual maps that provide snapshot
-estimates of how much participants know about any concept within the scope of
-our text embedding model, and how much their knowledge of those concepts
-changes with training (Fig.~\ref{fig:knowledge-maps}).
+estimates can generalize to held-out questions and predict participants'
+abilities to answer them correctly (Fig.~\ref{fig:predictions}). Finally, we use
+our framework to construct visual maps that provide snapshot estimates of how
+much participants know about any concept within the scope of our text embedding
+model, and how much their knowledge of those concepts changes with training
+(Fig.~\ref{fig:knowledge-maps}).
 

### 2025-01-11 paper/main.tex
shrink vspace in author affiliations to fit keywords on first page

@@
 
-\author{Paxton C. Fitzpatrick\textsuperscript{1},
-Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
+\author{Paxton C. Fitzpatrick\textsuperscript{1}, Andrew C.
+Heusser\textsuperscript{1, 2}, and Jeremy R. Manning\textsuperscript{1, *}\\
+\vspace{-0.5em}\small{\textsuperscript{1}Department of Psychological and Brain
+Sciences}\\
+\small{Dartmouth College, Hanover, NH 03755, USA}\\
+\vspace{-0.5em}\small{\textsuperscript{2}Akili Interactive Labs}\\
+\small{Boston, MA 02110, USA}\\
+\vspace{-0.5em}\small{\textsuperscript{*}Corresponding author:
 Jeremy.R.Manning@Dartmouth.edu}}

### 2025-01-11 paper/main.tex
fix some references to supp figs

@@
 matches'' between individual questions and individual moments of each lecture
-(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The time series plot of
-individual questions' correlations are different from each other when computed
-using LDA (e.g., the traces can be clearly visually separated), whereas the
-correlations computed from BERT embeddings of different questions all look very
-similar. This tells us that LDA is capturing some differences in content
+(Fig.~\ref{fig:question-correlations}, Supp.~Fig.~\ldaVsBERT). The time series
+plot of individual questions' correlations are different from each other when
+computed using LDA (e.g., the traces can be clearly visually separated), whereas
+the correlations computed from BERT embeddings of different questions all look
+very similar. This tells us that LDA is capturing some differences in content
 between the questions, whereas BERT is not. The time series plots of individual
@@
 intersection of words from $A$ and $B$ divided by the number of unique words in
-the union of words from $A$ and $B$. In a supplementary analysis (Supp.
-Fig.~\jaccard), we compared the LDA-based question-lecture matches we reported
-in Figure~\ref{fig:question-correlations} with the Jaccard similarities between
-each question and each sliding window of text from the corresponding lecture.
-As shown in Supplementary Figure~\jaccard, this simple word-matching approach
-does not appear to capture the same level of specificity as the LDA-based
-approach. Whereas the LDA-based approach often yields a clear peak in the
-time series of correlations between each question and the corresponding lecture,
-the Jaccard similarity-based approach does not. Furthermore, these LDA-based
-matches appear to capture conceptual overlaps between the questions and
-lectures (Supp.~Tab.~\matchTab), whereas simple word matching does not. For
+the union of words from $A$ and $B$. In a supplementary analysis
+(Supp.~Fig.~\jaccard), we compared the LDA-based question-lecture matches we
+reported in Figure~\ref{fig:question-correlations} with the Jaccard similarities
+between each question and each sliding window of text from the corresponding
+lecture. As shown in Supplementary Figure~\jaccard, this simple word-matching
+approach does not appear to capture the same level of specificity as the
+LDA-based approach. Whereas the LDA-based approach often yields a clear peak in
+the time series of correlations between each question and the corresponding
+lecture, the Jaccard similarity-based approach does not. Furthermore, these
+LDA-based matches appear to capture conceptual overlaps between the questions
+and lectures (Supp.~Tab.~\matchTab), whereas simple word matching does not. For
 example, one of the example questions examined in Supplementary

### 2025-01-12 paper/main.tex
some style and phrasing clean up

@@
 random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82,
-Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the objective of
+Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However, the objective of
 real-world training, or learning from life experiences more generally, is often
@@
 Equation~\ref{eqn:prop} to estimate their knowledge at the given question's
-embedding space coordinate based on other questions that participant answered
+embedding-space coordinate based on other questions that participant answered
 on the same quiz. We repeated this for all participants, and for each of the
@@
 correctly answering a question as a function of estimated knowledge for its
-embedding coordinate, while accounting for random variation among participants
-and questions (see \nameref{subsec:glmm}). To assess the predictive value of
-the knowledge estimates, we compared each GLMM to an analogous (i.e., nested)
-``null'' model that did not consider estimated knowledge using parametric
-bootstrap likelihood-ratio tests.
+embedding coordinate, while accounting for varied effects of individual 
+participants and questions (see \nameref{subsec:glmm}). To assess the predictive 
+value of the knowledge estimates, we compared each GLMM to an analogous (i.e., 
+nested) ``null'' model that assumed these estimates carried no predictive information using parametric bootstrap likelihood-ratio tests.
 
@@
     knowledge.} We used generalized linear mixed models (GLMMs) to model the
-    likelihood of correctly answering a quiz question as a function of
+    probability of correctly answering a quiz question as a function of
     estimated knowledge for its embedding coordinate (see
@@
 \textit{generalizability} of our approach by asking whether our predictions
-could extend across the content areas of the two lectures. When computing these
-knowledge estimates, we used a rebalancing procedure to ensure that (for a given
-participant and quiz) the knowledge estimates for correctly and incorrectly
-answered questions were computed from the same proportion of correctly answered
-questions (see~\nameref{subsec:glmm}).
+could extend across the content areas of the two lectures. When estimating
+participants' knowledge, we used a rebalancing procedure to ensure that (for a 
+given participant and quiz) their knowledge estimates for correctly and 
+incorrectly answered questions were computed from the same underlying proportion 
+of correctly answered questions (see~\nameref{subsec:glmm}).
 
@@
 results suggest that our knowledge estimates can reliably predict participants'
-performance on individual questions when aggregated across all quiz content.
+performance on individual questions when they incorporate information from all 
+(other) quiz content.
 
@@
 lecture, across all three quizzes, for which this was true.) Because of this,
-when we held out one incorrectly answered \textit{Four Fundamental Forces}
-question from a given participant's Quiz~3 responses and estimated their
-knowledge at its embedding coordinate using the remaining \textit{Four
-Fundamental Forces} questions they answered, for 90\% of participants, that
-estimate leveraged information about at most a single other question they were
-\textit{not} able to correctly answer. This broad homogeneity in participants'
-success on questions used to estimate their knowledge may have hurt our ability
-to accurately characterize the specific (and by Quiz~3, relatively few) aspects
-of the lecture content they did \textit{not} know about. Taken together, these
-results suggest that our knowledge estimates can reliably distinguish between
-questions about different content covered by a single lecture, provided there is
-sufficient diversity in participants' quiz responses to extract meaningful
-information about both what they know and what they do not know.
+when we held out one incorrectly answered 
+\textit{Four Fundamental Forces}-related question from a given participant's 
+Quiz~3 responses and estimated their knowledge at its embedding coordinate using 
+the remaining \textit{Four Fundamental Forces}-related questions they answered, 
+for 90\% of participants, that estimate leveraged information about at most a 
+single other question they were \textit{not} able to correctly answer. This
+broad homogeneity in participants' success on questions used to estimate their 
+knowledge may have hurt our ability to accurately characterize the specific (and 
+by Quiz~3, relatively few) aspects of the lecture content they did \textit{not} 
+know about. Taken together, these results suggest that our knowledge estimates 
+can reliably distinguish between questions about different content covered by a 
+single lecture, provided there is sufficient diversity in participants' quiz 
+responses to extract meaningful information about both what they know and what 
+they do not know.
 
@@
 distance? Conversely, suppose the participant instead answered that same
-question \textit{in}correctly. Again, as we move farther away from $x$ in the
+question \textit{incorrectly}. Again, as we move farther away from $x$ in the
 embedding space, how does the likelihood that the participant does \textit{not}
@@
 All of the statistical tests performed in our study were two-sided. The 95\%
-confidence intervals we reported for each correlation were estimated by
-generating 10,000 bootstrap distributions of correlation coefficients by
+confidence intervals we reported for each correlation were estimated from 
+bootstrap distributions of 10,000 correlation coefficients obtained by
 sampling (with replacement) from the observed data.
@@
 (i.e., the union of all unique words, across all documents, excluding ``stop
-words.''). Conceptually, each topic is intended to give larger weights to words
+words''). Conceptually, each topic is intended to give larger weights to words
 that are semantically related (as inferred from their tendency to co-occur in
@@
 correlations between any lecture timepoint and question, taken over all
-timepoints in the given lecture, and all five questions \textit{about} that
+timepoints in the given lecture and all questions \textit{about} that
 lecture appearing on the given quiz. We also define $f(s, \Omega)$ as the
@@
 the topic vectors of questions $Q$ used to estimate the knowledge trace. Note
-that ``correct'' denotes the set of indices of the questions the participant
-answered correctly on the given quiz.
+that ``$\mathrm{correct}$'' denotes the set of indices of the questions the 
+participant answered correctly on the given quiz.
 
@@
 vectors (e.g., the topic vector $x$ for one timepoint in a lecture and the
-topic vector $y$ for one question), normalized by the minimum and maximum
-correlations (across all timepoints $t$ and questions $j$) to range between 0
-and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
-proportion of correctly answered questions about the content presented at
-timepoint $t$, where the weights are given by the normalized correlations
+topic vector $y$ for one question on a quiz), normalized by the minimum and 
+maximum correlations (across all timepoints $t$ and questions $j$) to range 
+between 0 and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted 
+average proportion of correctly answered questions about the content presented 
+at timepoint $t$, where the weights are given by the normalized correlations
 between timepoint $t$'s topic vector and the topic vectors for each question.

### 2025-01-12 paper/main.tex
another couple typo fixes

@@
 location $y$, then guessing the outcome at $y$ based on $x$ should be no more
-successful than guessing based on a measure that does not consider embedding
-space distance.
+successful than guessing based on a measure that does not consider 
+embedding-space distance.
 
@@
 constructed a series of concentric 15-dimensional ``spheres'' centered on the
-reference question's embedding space coordinate, where each successive sphere's
+reference question's embedding-space coordinate, where each successive sphere's
 radius increased by 0.01 (correlation distance) between 0 and 2, inclusive

### 2025-01-12 paper/main.tex
minor updates to paragraph introducing fig 8 results

@@
 
-Knowledge estimates need not be limited to the content of the lectures. As
-illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
-estimating knowledge from a small number of quiz questions may be extended to
-\textit{any} content, given its text embedding coordinate. To visualize how
-knowledge ``spreads'' through text embedding space to content beyond the
-lectures participants watched, we first fit a new topic model to the lectures'
-sliding windows with $k = 100$~topics. Conceptually, increasing the
-number of topics used by the model functions to increase the ``resolution'' of
-the embedding space, providing a greater ability to estimate knowledge for
-content that is highly similar to (but not precisely the same as) that
-contained in the two lectures. We note that we used these 2D maps solely for
-visualization; all relevant comparisons, distance computations, and statistical
-tests we report above were carried out in the original 15-dimensional space,
-using the 15-topic model. Aside from increasing the number of topics from 15 to
-100, all other procedures and model parameters were carried over from the
-preceding analyses. As in our other analyses, we resampled each lecture's topic
-trajectory to 1~Hz and projected each question into a shared text embedding
-space.
+Knowledge estimates need not be limited to the contents of these particular
+lectures and quizzes. As illustrated in Figure~\ref{fig:knowledge-maps}, our 
+general approach to estimating knowledge from a small number of quiz questions 
+may be extended to \textit{any} content, given its text embedding coordinate. To 
+visualize how knowledge ``spreads'' through text embedding space to content 
+beyond the lectures participants watched and the questions they answered, we 
+first fit a new topic model to the lectures' sliding windows with $k = 
+100$~topics. Conceptually, increasing the number of topics used by the model 
+functions to increase the ``resolution'' of the embedding space, providing a 
+greater ability to estimate knowledge for content that is highly similar to (but 
+not precisely the same as) that contained in the two lectures used to train the 
+model. We note that we used these 2D maps solely for visualization; all relevant 
+comparisons, distance computations, and statistical tests we report above were 
+carried out in the original 15-dimensional space, using the 15-topic model. 
+Aside from increasing the number of topics from 15 to 100, all other procedures 
+and model parameters were carried over from the preceding analyses. As in our 
+other analyses, we resampled each lecture's topic trajectory to 1~Hz and 
+projected each question into a shared text embedding space.
 

### 2025-01-14 paper/main.tex

@@
 single other question they were \textit{not} able to correctly answer. This
-broad homogeneity in participants' success on questions used to estimate their 
+homogeneity in participants' success on questions used to estimate their
 knowledge may have hurt our ability to accurately characterize the specific (and
@@
 95\%\ \textnormal{CI} = [0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$).
-We similarly found that participants' success on questions about either lecture
-could not be predicted given their responses to questions about the other
-lecture after viewing \textit{Four Fundamental Forces} but before viewing \textit{Birth of Stars} (i.e., on Quiz~2; \textit{Four Fundamental Forces}
+Similarly, we found that participants' performance on questions about either
+lecture could not be predicted given their responses to questions about the
+other lecture after viewing \textit{Four Fundamental Forces} but before viewing
+\textit{Birth of Stars} (i.e., on Quiz~2; \textit{Four Fundamental Forces}
 questions given \textit{Birth of Stars} questions: $OR = 3.49,\ 95\%\
@@
 
-We view our work as making several contributions to the study of how people
-acquire conceptual knowledge. First, from a methodological standpoint, our
-modeling framework provides a systematic means of mapping out and
-characterizing knowledge in maps that have infinite (arbitrarily many) numbers
-of coordinates, and of ``filling out'' those maps using relatively small
-numbers of multiple choice quiz questions. Our experimental finding that we can
-use these maps to predict responses to held-out questions has several
-psychological implications as well. For example, concepts that are assigned to
-nearby coordinates by the text embedding model also appear to be ``known to a
-similar extent'' (as reflected by participants' responses to held-out
-questions; Fig.~\ref{fig:predictions}). This suggests that participants also
+Our work makes several contributions to the study of how people acquire
+conceptual knowledge. First, from a methodological standpoint, our modeling
+framework provides a systematic means of mapping out and characterizing
+knowledge in maps that have infinite (arbitrarily many) numbers of coordinates,
+and of ``filling out'' those maps using relatively small numbers of multiple
+choice quiz questions. Our experimental finding that we can use these maps to
+predict responses to held-out questions has several psychological implications
+as well. For example, concepts that are assigned to nearby coordinates by the
+text embedding model also appear to be ``known to a similar extent'' (as
+reflected by participants' responses to held-out questions;
+Fig.~\ref{fig:predictions}). This suggests that participants also
 \textit{conceptualize} similarly the content reflected by nearby embedding
@@
 GLMM's ability to explain participants' success on individual quiz questions to
-that of an analogous model which assumed (as we assume under our null hypothesis) that knowledge estimates for correctly and incorrectly answered
+that of an analogous model which assumed (as we assume under our null
+hypothesis) that knowledge estimates for correctly and incorrectly answered
 questions did \textit{not} systematically differ, on average. Specifically, we
@@
 \end{equation}
-Intuitively, Equation~\ref{eqn:rbf-knowledge} computes the weighted proportion of
-correctly answered questions, where the weights are given by how nearby (in the 2D space)
-each question is to the $x$.  We also defined \textit{learning maps} as the coordinate-by-coordinate
-differences between any pair of knowledge maps.  Intuitively, learning maps reflect the \textit{change}
-in knowledge across two maps.
+Equation~\ref{eqn:rbf-knowledge} computes the weighted proportion of correctly
+answered questions, where the weights are given by how nearby (in the 2D space)
+each question is to the $x$. We also defined \textit{learning maps} as the
+coordinate-by-coordinate differences between any pair of knowledge maps.
+Intuitively, learning maps reflect the \textit{change} in knowledge
+across two maps.
 

### 2025-01-14 paper/main.tex
slight re-framing of Fig 6 across-lecture results

@@
 
-Finally, when we estimated participants' knowledge for each question about one
+Finally, we estimated participants' knowledge for each question about one
 lecture using their performance on questions (from the same quiz) about the
-\textit{other} lecture, we observed a somewhat different pattern of results.
-Here we found that before viewing either lecture (i.e., on Quiz~1),
-participants' abilities to answer \textit{Four Fundamental Forces}-related
-questions could not be predicted from their responses to \textit{Birth of
-Stars}-related questions ($OR = 1.896,\ 95\%\ \textnormal{CI} = [0.419,\
-9.088],\ \lambda_{LR} = 0.712,\ p = 0.404$), nor could their abilities to
-answer \textit{Birth of Stars}-related questions be predicted from their
-responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\
-95\%\ \textnormal{CI} = [0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$).
-Similarly, we found that participants' performance on questions about either
-lecture could not be predicted given their responses to questions about the
-other lecture after viewing \textit{Four Fundamental Forces} but before viewing
-\textit{Birth of Stars} (i.e., on Quiz~2; \textit{Four Fundamental Forces}
-questions given \textit{Birth of Stars} questions: $OR = 3.49,\ 95\%\
-\textnormal{CI} = [0.739,\ 12.849],\ \lambda_{LR} = 3.266,\ p = 0.083$;
-\textit{Birth of Stars} questions given \textit{Four Fundamental Forces}
-questions: $OR = 2.199,\ 95\%\ \textnormal{CI} = [0.711,\ 5.623],\
-\lambda_{LR} = 2.304,\ p = 0.141$). Only after viewing \textit{both} lectures
-(i.e., on Quiz~3) did these across-lecture knowledge estimates reliably predict
-participants' success on individual quiz questions (\textit{Four Fundamental
-Forces} questions given \textit{Birth of Stars} questions: $OR = 11.294,\
-95\%\ \textnormal{CI} = [1.375,\ 47.744],\ \lambda_{LR} = 10.396,\ p < 0.001$;
-\textit{Birth of Stars} questions given \textit{Four Fundamental Forces}
-questions: $OR = 7.302,\ 95\%\ \textnormal{CI} = [1.077,\ 44.879],\
-\lambda_{LR} = 4.708,\ p = 0.038$). Taken together, these results suggest that
-our knowledge estimates can be used to predict participants' success across
-content areas once they have received some training on both the content about
-which their knowledge is estimated and the content used to construct these
-estimates.
+\textit{other} lecture. This is an especially stringent test of our approach.
+Our primary assumption in building our knowledge estimates is that knowledge
+about a given concept is similar to knowledge about other concepts that are
+nearby in the embedding space. However, our analyses in Figure~\ref{fig:topics}
+and Supplementary Figure~\topicWeights~show that the embeddings of content from
+the two lectures are largely distinct. Therefore any predictive power of the
+knowledge estimates must overcome large distances in the embedding space. To
+put this in concrete terms, this test requires predicting participants'
+performance on individual highly specific questions about the formation of
+stars, using each participants' responses to just five multiple choice
+questions about the fundamental forces of the universe (and vice versa).
+
+We found that, before viewing either lecture (i.e., on Quiz~1), participants'
+abilities to answer \textit{Four Fundamental Forces}-related questions could
+not be predicted from their responses to \textit{Birth of Stars}-related
+questions ($OR = 1.896,\ 95\%\ \textnormal{CI} = [0.419,\ 9.088],\ \lambda_{LR}
+= 0.712,\ p = 0.404$), nor could their abilities to answer \textit{Birth of
+Stars}-related questions be predicted from their responses to \textit{Four
+Fundamental Forces}-related questions ($OR = 1.522,\ 95\%\ \textnormal{CI} =
+[0.332,\ 6.835],\ \lambda_{LR} = 0.286,\ p = 0.611$). Similarly, we found that
+participants' performance on questions about either lecture could not be
+predicted given their responses to questions about the other lecture after
+viewing \textit{Four Fundamental Forces} but before viewing \textit{Birth of
+Stars} (i.e., on Quiz~2; \textit{Four Fundamental Forces} questions given
+\textit{Birth of Stars} questions: $OR = 3.49,\ 95\%\ \textnormal{CI} =
+[0.739,\ 12.849],\ \lambda_{LR} = 3.266,\ p = 0.083$; \textit{Birth of Stars}
+questions given \textit{Four Fundamental Forces} questions: $OR = 2.199,\ 95\%\
+\textnormal{CI} = [0.711,\ 5.623],\ \lambda_{LR} = 2.304,\ p = 0.141$). Only
+after viewing \textit{both} lectures (i.e., on Quiz~3) did these across-lecture
+knowledge estimates reliably predict participants' success on individual quiz
+questions (\textit{Four Fundamental Forces} questions given \textit{Birth of
+Stars} questions: $OR = 11.294,\ 95\%\ \textnormal{CI} = [1.375,\ 47.744],\
+\lambda_{LR} = 10.396,\ p < 0.001$; \textit{Birth of Stars} questions given
+\textit{Four Fundamental Forces} questions: $OR = 7.302,\ 95\%\ \textnormal{CI}
+= [1.077,\ 44.879],\ \lambda_{LR} = 4.708,\ p = 0.038$). Taken together, our
+results suggest that our ability to form estimates solely across different
+content areas is more limited than our ability to form estimates that
+incorporate responses to questions across both content areas (as in
+Fig.~\ref{fig:predictions}, ``All questions'') or within a single content area (as
+in Fig.~\ref{fig:predictions}, ``Within-lecture'').  However, if participants have recently
+received some training on both content areas, the knowledge estimates appear to be informative
+even across content areas.
+
+We speculate that these ``Across-lecture'' results might relate to some of our
+earlier work on the nature of semantic representations~\citep{MannKaha12}. In
+that work, we asked whether semantic similarities could be captured through
+behavioral measures, even if participants' ``true'' internal representations
+differed from the embeddings used to \textit{characterize} participants'
+behaviors. We found that mismatches between someone's internal representation
+of a set of concepts and the representation used to characterize their
+behaviors can lead to underestimates of how semantically driven their behaviors
+are. Along similar lines, we suspect that in our current study, participants'
+conceptual representations may initially differ from the representations
+learned by our topic model. (Although the topic models are still
+\textit{related} to participants' initial internal representations; otherwise
+we would have found that knowledge estimates derived from Quiz 1 and 2
+responses would have no predictive power in the other tests we conducted.)
+After watching both lectures, however, participants' internal representations
+may become more aligned with the embeddings used to estimate their knowledge
+(since those embeddings were trained on the lecture transcripts). This could
+help explain why the knowledge estimates derived from Quizzes 1 and 2 (before
+both lectures had been watched) do not reliably predict performance across
+content areas, whereas estiamtes derived from Quiz 3 \textit{do} reliably
+predict performance across content areas.
 

### 2025-01-14 paper/main.tex
cleaned up phrasing of fig 6 within-lecture results

--- 2025-01-14 paper/main.tex
@@
 questions incorrectly, and all but five participants (out of 50) answered two or
-fewer questions incorrectly. (This was the only subset of questions about either
-lecture, across all three quizzes, for which this was true.) Because of this,
-when we held out one incorrectly answered
-\textit{Four Fundamental Forces}-related question from a given participant's
-Quiz~3 responses and estimated their knowledge at its embedding coordinate using
-the remaining \textit{Four Fundamental Forces}-related questions they answered,
-for 90\% of participants, that estimate leveraged information about at most a
-single other question they were \textit{not} able to correctly answer. This
-homogeneity in participants' success on questions used to estimate their
-knowledge may have hurt our ability to accurately characterize the specific (and
-by Quiz~3, relatively few) aspects of the lecture content they did \textit{not}
-know about. Taken together, these results suggest that our knowledge estimates
-can reliably distinguish between questions about different content covered by a
-single lecture, provided there is sufficient diversity in participants' quiz
-responses to extract meaningful information about both what they know and what
-they do not know.
+fewer incorrectly. (This was the only subset of questions about either lecture, 
+across all three quizzes, for which this was true.) Because of this, for 90\% of 
+participants, our within-lecture estimates of their knowledge for \textit{Four 
+Fundamental Forces}-related questions that they answered incorrectly leveraged 
+information from at most a single other question they were \textit{not} able to 
+correctly answer. This likely hampered our ability to accurately characterize 
+the specific (and by the time they took Quiz~3, relatively few) aspects of the 
+lecture content these participants did \textit{not} know about, and successfully 
+distinguish them from the far more numerous aspects of the lecture content they 
+now \textit{did} know about. Taken together, these results suggest that our 
+knowledge estimates can reliably distinguish between questions about different
+content covered by a single lecture, provided there is sufficient diversity in 
+participants' quiz responses to extract meaningful information about both what 
+they know and what they do not know.
 

### 2025-01-14 paper/main.tex
minor cleanup to fig 6 across-lecture results

@@
 nearby in the embedding space. However, our analyses in Figure~\ref{fig:topics}
-and Supplementary Figure~\topicWeights~show that the embeddings of content from
-the two lectures are largely distinct. Therefore any predictive power of the
-knowledge estimates must overcome large distances in the embedding space. To
-put this in concrete terms, this test requires predicting participants'
-performance on individual highly specific questions about the formation of
-stars, using each participants' responses to just five multiple choice
-questions about the fundamental forces of the universe (and vice versa).
+and Supplementary Figure~\topicWeights\ show that the embeddings of content from
+the two lectures (and of their associated quiz questions) are largely distinct 
+from each other. Therefore, any predictive power of these across-lecture 
+knowledge estimates must overcome large distances in the embedding space. To put 
+this in concrete terms, this test requires predicting participants' performance 
+on individual, highly specific questions about the formation of stars from their 
+responses to just five multiple-choice questions about the fundamental forces of 
+the universe (and vice versa).
 
@@
 \textit{Four Fundamental Forces} questions: $OR = 7.302,\ 95\%\ \textnormal{CI}
-= [1.077,\ 44.879],\ \lambda_{LR} = 4.708,\ p = 0.038$). Taken together, our
+= [1.077,\ 44.879],\ \lambda_{LR} = 4.708,\ p = 0.038$). Taken together, these
 results suggest that our ability to form estimates solely across different
 content areas is more limited than our ability to form estimates that
-incorporate responses to questions across both content areas (as in
-Fig.~\ref{fig:predictions}, ``All questions'') or within a single content area (as
-in Fig.~\ref{fig:predictions}, ``Within-lecture'').  However, if participants have recently
-received some training on both content areas, the knowledge estimates appear to be informative
-even across content areas.
+incorporate responses to questions from both content areas (as in 
+Fig.~\ref{fig:predictions}, ``All questions'') or within a single content area 
+(as in Fig.~\ref{fig:predictions}, ``Within-lecture''). However, if participants 
+have recently received some training on both content areas, the knowledge 
+estimates appear to be informative even across content areas.
 
@@
 behavioral measures, even if participants' ``true'' internal representations 
-differed from the embeddings used to \textit{characterize} participants'
-behaviors. We found that mismatches between someone's internal representation
-of a set of concepts and the representation used to characterize their
-behaviors can lead to underestimates of how semantically driven their behaviors
-are. Along similar lines, we suspect that in our current study, participants'
-conceptual representations may initially differ from the representations
-learned by our topic model. (Although the topic models are still
-\textit{related} to participants' initial internal representations; otherwise
-we would have found that knowledge estimates derived from Quiz 1 and 2
-responses would have no predictive power in the other tests we conducted.)
-After watching both lectures, however, participants' internal representations
-may become more aligned with the embeddings used to estimate their knowledge
-(since those embeddings were trained on the lecture transcripts). This could
-help explain why the knowledge estimates derived from Quizzes 1 and 2 (before
-both lectures had been watched) do not reliably predict performance across
-content areas, whereas estiamtes derived from Quiz 3 \textit{do} reliably
-predict performance across content areas.
+differed from the embeddings used to \textit{characterize} their behaviors. We 
+found that mismatches between an individual's internal representation of a set 
+of concepts and the representation used to characterize their behaviors can lead 
+to underestimates of how semantically driven those behaviors are. Along similar 
+lines, we suspect that in our current study, participants' conceptual 
+representations may initially differ from the representations learned by our 
+topic model. (Although the topic model's representations are still 
+\textit{related} to participants' initial internal representations; otherwise we 
+would have found that knowledge estimates derived from Quizzes~1 and 2 had no 
+predictive power in the other tests we conducted.) After watching both lectures, 
+however, participants' internal representations may become more aligned with the 
+embeddings used to estimate their knowledge (since those embeddings were trained 
+on the lectures' transcripts). This could help explain why the knowledge 
+estimates derived from Quizzes~1 and 2 (before both lectures had been watched) 
+do not reliably predict performance across content areas, whereas estimates 
+derived from Quiz~3 do.
 

### 2025-02-21 paper/main.tex
multiple choice -> multiple-choice

@@
 knowledge in maps that have infinite (arbitrarily many) numbers of coordinates,
-and of ``filling out'' those maps using relatively small numbers of multiple
-choice quiz questions. Our experimental finding that we can use these maps to
-predict responses to held-out questions has several psychological implications
-as well. For example, concepts that are assigned to nearby coordinates by the
-text embedding model also appear to be ``known to a similar extent'' (as
-reflected by participants' responses to held-out questions;
+and of ``filling out'' those maps using relatively small numbers of 
+multiple-choice quiz questions. Our experimental finding that we can use these 
+maps to predict responses to held-out questions has several psychological 
+implications as well. For example, concepts that are assigned to nearby 
+coordinates by the text embedding model also appear to be ``known to a similar 
+extent'' (as reflected by participants' responses to held-out questions;
 Fig.~\ref{fig:predictions}). This suggests that participants also

### 2025-02-22 paper/supplement.tex
update table formatting for readability

@@
 \documentclass[10pt]{article}
-\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{placeins}
-\usepackage{booktabs}
 \usepackage{longtable}
+\usepackage[table]{xcolor}
+\usepackage{ragged2e}
 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
-\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
+% some customizations for better-looking tables:
+% color for gray rows
+\definecolor{tablerowgray}{RGB}{245, 245, 245}
+% column type for multiline (paragraph) text, same as p{} but left-aligned 
+% instead of justified to prevent ugly spacing
+\newcolumntype{P}[1]{>{\RaggedRight\arraybackslash}p{#1}}
+% adds a horizontal rule the same width as booktabs's \midrule but without the 
+% gaps above & below
+\newcommand{\thickhline}{\noalign{\hrule height.6pt}}
 
@@
 
-\author{Paxton C. Fitzpatrick\textsuperscript{1},
-Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
+\author{Paxton C. Fitzpatrick\textsuperscript{1}, Andrew C. 
+Heusser\textsuperscript{1, 2}, and Jeremy R. Manning\textsuperscript{1, *}\\
+\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\
+\small{Dartmouth College, Hanover, NH 03755, USA}\\
+\small{\textsuperscript{2}Akili Interactive Labs}\\
+\small{Boston, MA 02110, USA}\\
+\small{\textsuperscript{*}Corresponding author:
 Jeremy.R.Manning@Dartmouth.edu}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Supplementary tables
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Supplementary tables}
+
 \begin{tiny}
-\renewcommand*{\arraystretch}{1.4}
-\begin{longtable}{|r|p{0.375in}|p{1.275in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|}
-\hline
-    \textbf{ID} & \textbf{Question set} &                                                                                                                                                                                                                                                                         \textbf{Question} &                                                                                                                                     \textbf{Correct response} &                                                                                                     \textbf{Alternative 1} &                                                                                                                          \textbf{Alternative 2} &                                                                                                                                 \textbf{Alternative 3} \\\hline
-    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
-&                                           Neither you nor your computer has enough mass to cause a noticeable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline
-    2     &     FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
-&                          A neutron in a radioactive Cesium atom is converted into a proton, leading to the release of a few particles &  Light from the sun collides with a satellite orbiting Earth and exerts a small push on the satellite &  Two protons bound together in a Helium nucleus resist separation despite a repulsive electromagnetic force acting on them &                                                   A distant galaxy exerts a small but detectable gravitational pull on the  Earth \\\hline
-    3     &     FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity?
-&                                                                                                    10,\-000,\-000,\-000,\-000,\-000,\-000,\-000,\-000 &                                                                                                    10 &                                                                                                                  1,000,000 &                                                                                  The Weak Interaction is less strong than gravity \\\hline
-    4     &     FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction?
-&                                                                         The weak interaction only acts over extremely small distances &                The weak interaction between you and your computer is counteracted by the other forces &                                                                                   You and your computer have no net charge &                                            Neither you nor your computer has enough mass to induce a significant Weak Interaction \\\hline
-    5     &     FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
-&                                            Gravity is only ever attractive while the electromagnetic force can both attract and repel &                                           Gravity is a much more powerful force than electromagnetism &           Gravity can only act over large distances while the electromagnetic force can act over large and small distances &                   The electromagnetic force can only act over small distances while gravity can act over small or large distances \\\hline
-    6     &     FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                            View them in different frames of reference &                              Switch which charges we call positive and which charges we call negative &                                        Consider both the effects over small distances and the effects over large distances &                                                           Consider both the attractive and repulsive properties of the two forces \\\hline
-    7     &     FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
-&                                                                                        The Strong Force and the Electromagnetic Force &                                                                      Gravity and the Weak Interaction &                                                                                      Gravity and the Electromagnetic Force &                                                                                         The Strong Force and the Weak Interaction \\\hline
-    8     &     FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge?
-&  Positive and negative charges cancel out and become a neutral charge when they combine while masses only grow larger as they combine &                                                    Masses tend to repel while charges tend to attract &                                                                         Masses tend to attract while charges tend to repel &       The gravitational interaction acting between masses is stronger than the electromagnetic interaction acting between charges \\\hline
-    9     &     FFF &  In your body, there are a tremendous amount of negatively-charged electrons.
-Your computer also contains a huge number of negatively-charged electrons.
-We know that like charges repel, but you and your computer are not repelled apart.
-Which of the following explains why?
-&                                    The electrons' negative charges are balanced by the positive charges of an equal number of protons &                                         An attractive gravitational force balances out this repulsion &                                                              The Electromagnetic force only acts over very small distances &                                                                     The Electromagnetic force only acts over very large distances \\\hline
-    10    &     FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force?
-&                                                                                               Both act only over very small distances &                                                      Both are stronger than the Electromagnetic force &                                                                                               Both are weaker than Gravity &                                                                     Both are responsible for attractions between distant galaxies \\\hline
-    11    &     FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
-&                                                                                                                          Strong Force &                                                                                               Gravity &                                                                                                           Weak Interaction &                                                                                            Electromagnetic Force is the strongest \\\hline
-    12    &     FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity?
-&                                                                                                                                 10\textasciicircum 38 &                                                                                                   100 &                                                                                                                      10\textasciicircum 18 &                                                                                           The Strong Force is weaker than gravity \\\hline
-    13    &     FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects?
-&                                                                            The objects would have to be extremely close to each other &                                                          The objects would have to have the same mass &                                                            The objects would have to be extremely far away from each other &                                                                                   The objects would have to have different masses \\\hline
-    14    &     FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth?
-&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
-    15    &     FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to?
-&                                      The repulsion of objects with similar charge and the attraction of objects with different charge &          The repulsion of objects with similar mass and the attraction of objects with different mass &                 The repulsion of objects with similar temperature and the attraction of objects with different temperature &                                The repulsion of objects with similar density and the attraction of objects with different density \\\hline
-    16    &     BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms?
-&                                                                                 The atoms move to the center of the mass of the atoms &                                          The atoms move away from the center of the mass of the atoms &                                                                  The atoms spin around the center of the mass of the atoms &                                                                                         Gravity has no effect on a cloud of atoms \\\hline
-    17    &     BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
-&                                                                                                                 Temperature increases &                                                                                 Temperature decreases &                                                                                                             Mass increases &                                                                                                                    Mass decreases \\\hline
-    18    &     BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
-&                                                                                                                     10 Million Kelvin &                                                                                              0 Kelvin &                                                                                                              10,000 Kelvin &                                                                                                                 10 Billion Kelvin \\\hline
-    19    &     BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force?
-&                                                                                                    High temperature and high pressure &                                                                     Low temperature and high pressure &                                                                                          High temperature and low pressure &                                                                                                  Low temperature and low pressure \\\hline
-    20    &     BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity?
-&                                                           Energy released from the fusion of hydrogen atoms provides outward pressure &                                    The fusion of hydrogen atoms decreases the temperature of the star &                                                                               The gravitational pull of other stars nearby &                                                                                                              The Weak Interaction \\\hline
-    21    &     BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars?
-&                                                                                                               Fusion occurs very fast &                                                                               Fusion occurs very slow &                                                                                         Fusion occurs in the reverse order &                                                                                                      Fusion does not occur at all \\\hline
-    22    &     BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
-&                                                                                                                             Deuterium &                                                                                                Oxygen &                                                                                                                     Helium &                                                                                                                         Beryllium \\\hline
-    23    &     BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
-&                                                                                                                      The Strong Force &                                                                             The Electromagnetic Force &                                                                                                                    Gravity &                                                                                                              The Weak Interaction \\\hline
-    24    &     BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus?
-&                                                                                           The mass of the combined nucleus is smaller &                                                            The mass of the combined nucleus is larger &                                                                               The mass of the combined nucleus is the same &                                                                                It is not possible for two nuclei to fuse together \\\hline
-    25    &     BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun?
-&                                                                     Hydrogen atoms in the Sun are fusing together and becoming Helium &                                                                        The Sun is a supermassive star &                                     The Sun does not experience the force of Gravity but does experience the Coulomb Force &                                                                                 The Sun is comprised of 10 million Hydrogen atoms \\\hline
-    26    &     BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
-&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
-    27    &     BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases?
-&                                                                                                                 Temperature increases &                                                                                      Volume increases &                                                                                                             Mass increases &                                                                                                                 None of the above \\\hline
-    28    &     BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion?
-&                                                                                                                                Helium &                                                                                                Oxygen &                                                                                                                     Cesium &                                                                                                                            Carbon \\\hline
-    29    &     BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun?
-&                                                                                                                    Main sequence star &                                                                                     Supermassive star &                                                                                                  Alternative sequence star &                                                                                                                 None of the above \\\hline
-    30    &     BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
-&                                                                                                                              Ignition &                                                                                            Combustion &                                                                                                              Decomposition &                                                                                                                      Displacement \\\hline
-    31    &      GPK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
-&                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\\hline
-    32    &      GPK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
-&                                                                                                                 Its number of protons &                                                                                Its number of neutrons &                                                                                                    Its number of electrons &                                                                                                                          Its mass \\\hline
-    33    &      GPK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron.
-What changes as a result of this conversion?
-&                                                                                                                    The atom's element &                                                                The atom's mass (in atomic mass units) &                                                                                                        The atom's velocity &                                                                                                                The atom's density \\\hline
-    34    &      GPK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest?
-&                                                                                                  Star, solar system, galaxy, universe &                                                             Galaxy, solar system, Milky Way, universe &                                                                                         Planet, galaxy, star, solar system &                                                                                             Earth, solar system, universe, galaxy \\\hline
-    35    &      GPK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom?
-&                                                                                                                  Protons and neutrons &                                                                                          Only protons &                                                                                                             Only electrons &                                                                                                            Neutrons and electrons \\\hline
-    36    &      GPK &                                                                                                                                                                                                                                       Which of the following has the least mass?
-&                                                                                                                           An electron &                                                                                              A proton &                                                                                                                  A neutron &                                                                                                                   A hydrogen atom \\\hline
-    37    &      GPK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy?
-&                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\\hline
-    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter ``m'' represent?
-&                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\\hline
-    39    &      GPK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
-&                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\\hline
-
-    \caption{\textbf{Question pool.} Each participant completed three quizzes consisting 
+  \singlespacing
+  \rowcolors{1}{tablerowgray}{}
+  \renewcommand*{\arraystretch}{1.75}
+  \setlength{\RaggedRightRightskip}{0pt plus 1em}
+%  \captionsetup{singlelinecheck=false}
+  \begin{longtable}{r P{0.3in} P{1.203in} P{0.8in} P{0.8in} P{0.8in} P{0.8in}}
+    \hiderowcolors
+    \caption[Question pool]{\textbf{Question pool.} Each participant completed three quizzes consisting
     of 13 multiple-choice questions randomly selected from the question pool. Each
@@
     one quiz (for each participant).}
+    \label{tab:questions}\\
 
-    \label{tab:questions}
+    \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Correct response} & \textbf{Alternative 1} & \textbf{Alternative 2} & \textbf{Alternative 3} \\
+    \thickhline
+    \showrowcolors
+    \endfirsthead
+
+    \hiderowcolors
+    \caption[]{(continued)}\\
+    \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Correct response} & \textbf{Alternative 1} & \textbf{Alternative 2} & \textbf{Alternative 3} \\
+    \thickhline
+    \showrowcolors
+    \endhead
+
+    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
+&                                           Neither you nor your computer has enough mass to cause a noticeable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\
+    2     &     FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
+&                          A neutron in a radioactive Cesium atom is converted into a proton, leading to the release of a few particles &  Light from the sun collides with a satellite orbiting Earth and exerts a small push on the satellite &  Two protons bound together in a Helium nucleus resist separation despite a repulsive electromagnetic force acting on them &                                                   A distant galaxy exerts a small but detectable gravitational pull on the  Earth \\
+    3     &     FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity?
+&                                                                                                    10,\-000,\-000,\-000,\-000,\-000,\-000,\-000,\-000 &                                                                                                    10 &                                                                                                                  1,000,000 &                                                                                  The Weak Interaction is less strong than gravity \\
+    4     &     FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction?
+&                                                                         The weak interaction only acts over extremely small distances &                The weak interaction between you and your computer is counteracted by the other forces &                                                                                   You and your computer have no net charge &                                            Neither you nor your computer has enough mass to induce a significant Weak Interaction \\
+    5     &     FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
+&                                            Gravity is only ever attractive while the electromagnetic force can both attract and repel &                                           Gravity is a much more powerful force than electromagnetism &           Gravity can only act over large distances while the electromagnetic force can act over large and small distances &                   The electromagnetic force can only act over small distances while gravity can act over small or large distances \\
+    6     &     FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                            View them in different frames of reference &                              Switch which charges we call positive and which charges we call negative &                                        Consider both the effects over small distances and the effects over large distances &                                                           Consider both the attractive and repulsive properties of the two forces \\
+    7     &     FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
+&                                                                                        The Strong Force and the Electromagnetic Force &                                                                      Gravity and the Weak Interaction &                                                                                      Gravity and the Electromagnetic Force &                                                                                         The Strong Force and the Weak Interaction \\
+    8     &     FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge?
+&  Positive and negative charges cancel out and become a neutral charge when they combine while masses only grow larger as they combine &                                                    Masses tend to repel while charges tend to attract &                                                                         Masses tend to attract while charges tend to repel &       The gravitational interaction acting between masses is stronger than the electromagnetic interaction acting between charges \\
+    9     &     FFF &  In your body, there are a tremendous amount of negatively-charged electrons.
+Your computer also contains a huge number of negatively-charged electrons.
+We know that like charges repel, but you and your computer are not repelled apart.
+Which of the following explains why?
+&                                    The electrons' negative charges are balanced by the positive charges of an equal number of protons &                                         An attractive gravitational force balances out this repulsion &                                                              The Electromagnetic force only acts over very small distances &                                                                     The Electromagnetic force only acts over very large distances \\
+    10    &     FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force?
+&                                                                                               Both act only over very small distances &                                                      Both are stronger than the Electromagnetic force &                                                                                               Both are weaker than Gravity &                                                                     Both are responsible for attractions between distant galaxies \\
+    11    &     FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
+&                                                                                                                          Strong Force &                                                                                               Gravity &                                                                                                           Weak Interaction &                                                                                            Electromagnetic Force is the strongest \\
+    12    &     FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity?
+&                                                                                                                                 10\textasciicircum 38 &                                                                                                   100 &                                                                                                                      10\textasciicircum 18 &                                                                                           The Strong Force is weaker than gravity \\
+    13    &     FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects?
+&                                                                            The objects would have to be extremely close to each other &                                                          The objects would have to have the same mass &                                                            The objects would have to be extremely far away from each other &                                                                                   The objects would have to have different masses \\
+    14    &     FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth?
+&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\
+    15    &     FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to?
+&                                      The repulsion of objects with similar charge and the attraction of objects with different charge &          The repulsion of objects with similar mass and the attraction of objects with different mass &                 The repulsion of objects with similar temperature and the attraction of objects with different temperature &                                The repulsion of objects with similar density and the attraction of objects with different density \\
+    16    &     BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms?
+&                                                                                 The atoms move to the center of the mass of the atoms &                                          The atoms move away from the center of the mass of the atoms &                                                                  The atoms spin around the center of the mass of the atoms &                                                                                         Gravity has no effect on a cloud of atoms \\
+    17    &     BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
+&                                                                                                                 Temperature increases &                                                                                 Temperature decreases &                                                                                                             Mass increases &                                                                                                                    Mass decreases \\
+    18    &     BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
+&                                                                                                                     10 Million Kelvin &                                                                                              0 Kelvin &                                                                                                              10,000 Kelvin &                                                                                                                 10 Billion Kelvin \\
+    19    &     BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force?
+&                                                                                                    High temperature and high pressure &                                                                     Low temperature and high pressure &                                                                                          High temperature and low pressure &                                                                                                  Low temperature and low pressure \\
+    20    &     BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity?
+&                                                           Energy released from the fusion of hydrogen atoms provides outward pressure &                                    The fusion of hydrogen atoms decreases the temperature of the star &                                                                               The gravitational pull of other stars nearby &                                                                                                              The Weak Interaction \\
+    21    &     BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars?
+&                                                                                                               Fusion occurs very fast &                                                                               Fusion occurs very slow &                                                                                         Fusion occurs in the reverse order &                                                                                                      Fusion does not occur at all \\
+    22    &     BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
+&                                                                                                                             Deuterium &                                                                                                Oxygen &                                                                                                                     Helium &                                                                                                                         Beryllium \\
+    23    &     BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
+&                                                                                                                      The Strong Force &                                                                             The Electromagnetic Force &                                                                                                                    Gravity &                                                                                                              The Weak Interaction \\
+    24    &     BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus?
+&                                                                                           The mass of the combined nucleus is smaller &                                                            The mass of the combined nucleus is larger &                                                                               The mass of the combined nucleus is the same &                                                                                It is not possible for two nuclei to fuse together \\
+    25    &     BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun?
+&                                                                     Hydrogen atoms in the Sun are fusing together and becoming Helium &                                                                        The Sun is a supermassive star &                                     The Sun does not experience the force of Gravity but does experience the Coulomb Force &                                                                                 The Sun is comprised of 10 million Hydrogen atoms \\
+    26    &     BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
+&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\
+    27    &     BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases?
+&                                                                                                                 Temperature increases &                                                                                      Volume increases &                                                                                                             Mass increases &                                                                                                                 None of the above \\
+    28    &     BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion?
+&                                                                                                                                Helium &                                                                                                Oxygen &                                                                                                                     Cesium &                                                                                                                            Carbon \\
+    29    &     BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun?
+&                                                                                                                    Main sequence star &                                                                                     Supermassive star &                                                                                                  Alternative sequence star &                                                                                                                 None of the above \\
+    30    &     BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
+&                                                                                                                              Ignition &                                                                                            Combustion &                                                                                                              Decomposition &                                                                                                                      Displacement \\
+    31    &      GPK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
+&                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\
+    32    &      GPK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
+&                                                                                                                 Its number of protons &                                                                                Its number of neutrons &                                                                                                    Its number of electrons &                                                                                                                          Its mass \\
+    33    &      GPK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron.
+What changes as a result of this conversion?
+&                                                                                                                    The atom's element &                                                                The atom's mass (in atomic mass units) &                                                                                                        The atom's velocity &                                                                                                                The atom's density \\
+    34    &      GPK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest?
+&                                                                                                  Star, solar system, galaxy, universe &                                                             Galaxy, solar system, Milky Way, universe &                                                                                         Planet, galaxy, star, solar system &                                                                                             Earth, solar system, universe, galaxy \\
+    35    &      GPK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom?
+&                                                                                                                  Protons and neutrons &                                                                                          Only protons &                                                                                                             Only electrons &                                                                                                            Neutrons and electrons \\
+    36    &      GPK &                                                                                                                                                                                                                                       Which of the following has the least mass?
+&                                                                                                                           An electron &                                                                                              A proton &                                                                                                                  A neutron &                                                                                                                   A hydrogen atom \\
+    37    &      GPK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy?
+&                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\
+    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter ``m'' represent?
+&                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\
+    39    &      GPK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
+&                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\
   \end{longtable}
@@
 
-\begin{table}[tp]
-    \centering
-    \begin{tiny}
-    \begin{tabular}{|r|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-    \textbf{Topic} & \textbf{1} & \textbf{2} &      \textbf{3} &  \textbf{4} & \textbf{5} & \textbf{6} &    \textbf{7} &  \textbf{8} & \textbf{9} &     \textbf{10} \\\hline
-             1 &       star &     helium &            main &        mass &     atomic &   sequence &           get &      energy &       fuse &        hydrogen \\\hline
-             2 &     charge &      force &            mass &     gravity &     strong &    attract &         large &    strength &   distance & electromagnetic \\\hline
-             3 &       huge &      force & electromagnetic &       macro &        way &      scale & concentration &       apply &       kind &          charge \\\hline
-             4 &       atom &      dense &              go &    hydrogen &       slow &        get &          huge &    condense &       mass &           would \\\hline
-             5 &     fusion &        get &       threshold &        core &      occur &       mass &     something &       start &    several &         jupiter \\\hline
-             6 &     enough &   ignition &          proton &       force &        get &      close &       nucleus &     coulomb &     fusion &           would \\\hline
-             7 &     energy &   pressure &        ignition &        mass &     little &       keep &       provide &      fusion &        get &        hydrogen \\\hline
-             8 &     proton &       weak &         neutron & interaction &        one &         go &       nucleon &      cesium &      extra &             get \\\hline
-            10 &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &         say &   distance &         combine \\\hline
-            11 &        one &   hydrogen &          helium &          go &     proton &    neutron &          keep &      atomic &     detail &            fuse \\\hline
-            12 &    gravity &      force &            weak & interaction &      apply &   strength &      distance &         ten &   relative &            next \\\hline
-            13 &      force &         go &   electrostatic &        call &     charge &     magnet &          side &     coulomb &       know &       different \\\hline
-            14 &      force &       atom &         nucleus &    electron &       much &   hydrogen &           get &      around &    coulomb &          charge \\\hline
-            15 &      force &      scale &         gravity &       start &       weak &      orbit &          keep & fundamental &     around &        surprise \\\hline
-    \end{tabular}    
-    \end{tiny}
+\begin{table}
+  \centering\tiny
+  \rowcolors{1}{}{tablerowgray}
+  \renewcommand*{\arraystretch}{1.75}
+  \setlength{\tabcolsep}{5.6pt}
 
-    \caption{\textbf{Topics.} We fit a topic model with $k = 15$ topics
+  \caption[Topics]{\textbf{Topics.} We fit a topic model with $k = 15$ topics
   to sliding windows parsed from the two course video transcripts
@@
   in Supplementary Figure~\ref{fig:topic-word-distributions}.}
+  \label{tab:topics}
 
-    \label{tab:topics}
+%  \begin{tabular}{>{\kern-\tabcolsep}r<{\hspace{0.1in}}*{10}{l}<{\kern-\tabcolsep}}
+  \begin{tabular}{>{\kern-\tabcolsep}r<{\hspace{0.1in}}*{10}{l}}
+    & \multicolumn{10}{c}{\textbf{Word rank}}\\
+    \cline{2-11}
+    \textbf{Topic}    & \textbf{1} & \textbf{2} &      \textbf{3} &  \textbf{4} & \textbf{5} & \textbf{6} &    \textbf{7} &  \textbf{8} & \textbf{9} &     \textbf{10} \\
+    \thickhline
+     1\hspace{0.08in} &       star &     helium &            main &        mass &     atomic &   sequence &           get &      energy &       fuse &        hydrogen \\
+     2\hspace{0.08in} &     charge &      force &            mass &     gravity &     strong &    attract &         large &    strength &   distance & electromagnetic \\
+     3\hspace{0.08in} &       huge &      force & electromagnetic &       macro &        way &      scale & concentration &       apply &       kind &          charge \\
+     4\hspace{0.08in} &       atom &      dense &              go &    hydrogen &       slow &        get &          huge &    condense &       mass &           would \\
+     5\hspace{0.08in} &     fusion &        get &       threshold &        core &      occur &       mass &     something &       start &    several &         jupiter \\
+     6\hspace{0.08in} &     enough &   ignition &          proton &       force &        get &      close &       nucleus &     coulomb &     fusion &           would \\
+     7\hspace{0.08in} &     energy &   pressure &        ignition &        mass &     little &       keep &       provide &      fusion &        get &        hydrogen \\
+     8\hspace{0.08in} &     proton &       weak &         neutron & interaction &        one &         go &       nucleon &      cesium &      extra &             get \\
+    10\hspace{0.08in} &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &         say &   distance &         combine \\
+    11\hspace{0.08in} &        one &   hydrogen &          helium &          go &     proton &    neutron &          keep &      atomic &     detail &            fuse \\
+    12\hspace{0.08in} &    gravity &      force &            weak & interaction &      apply &   strength &      distance &         ten &   relative &            next \\
+    13\hspace{0.08in} &      force &         go &   electrostatic &        call &     charge &     magnet &          side &     coulomb &       know &       different \\
+    14\hspace{0.08in} &      force &       atom &         nucleus &    electron &       much &   hydrogen &           get &      around &    coulomb &          charge \\
+    15\hspace{0.08in} &      force &      scale &         gravity &       start &       weak &      orbit &          keep & fundamental &     around &        surprise \\
+  \end{tabular}
 \end{table}
 
-\newpage
+\clearpage
 
 \begin{tiny}
-    \renewcommand*{\arraystretch}{1.4}
-    \begin{longtable}{|r|p{0.375in}|p{1.275in}|p{3.5in}|}
-        \hline
-        \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Matched lecture transcript text} \\\hline
+  \centering\singlespacing
+  \rowcolors{1}{tablerowgray}{}
+  \renewcommand*{\arraystretch}{1.75}
+  \setlength{\tabcolsep}{5pt}
+  \begin{longtable}{r p{0.3in} p{1.212in} p{3.8in}}
+    \hiderowcolors
+    \caption{\textbf{Lecture-specific questions and lecture excerpts.} We used 
+    the text embeddings for each question about \textit{Four Fundamental Forces} 
+    (FFF) and \textit{Birth of Stars} (BoS) to identify corresponding matching 
+    intervals of the lectures. The text of the questions and the best-matching 
+    time intervals of the lecture transcripts are displayed (lecture times are 
+    noted in square brackets). Time courses of topic correlations for each 
+    question may be found in Supplementary Figures~\ref{fig:forces-peaks} 
+    and~\ref{fig:bos-peaks}. Note that no matching lecture interval was found 
+    for Question 29.}
+    \label{tab:matches}\\
+
+    \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Matched lecture transcript text} \\
+    \thickhline
+    \showrowcolors
+    \endfirsthead
+
+    \hiderowcolors
+    \caption[]{(continued)}\\
+    \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Matched lecture transcript text} \\
+    \thickhline
+    \showrowcolors
+    \endhead
+
     1  &          FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction~\ldots \\
     2  &          FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[01:22.439--03:05.1]} ...this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[01:22.439--03:05.1]}~\ldots this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate~\ldots \\
     3  &          FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]}~\ldots anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this~\ldots \\
     4  &          FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[00:00.03--02:42.9]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[00:00.03--02:42.9]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an~\ldots \\
     5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
-\\\hline
-6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]}~\ldots times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar~\ldots \\
+    6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]}~\ldots times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar~\ldots\smallskip\newline\textbf{[06:37.31--07:28.1]}~\ldots that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in~\ldots \\
     7  &          FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[07:10.13--08:35.24]} ...reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction~\ldots\smallskip\newline\textbf{[07:10.13--08:35.24]}~\ldots reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances~\ldots \\
     8  &          FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[08:24.11--10:26.27]} ...just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances so if you get two of these protons close enough together and the strong force only applies over very very very small distances subatomic I should even say sub nucleic distances then the strong interaction comes into play so then you have the strong interaction actually keeping these charges together and once again just to keep it in in in mind relative to gravity it is 10 to the 38th 10 38 times the strength times the strength of gravity or it's about a hundred times stronger than the electromagnetic force so once again the reason why you don't see the strong force which is the strongest of all of the forces or the weak interaction applying over huge scales is that they really only they only their strength dies off super super fast even when you start going to large radius nucleuses of atoms they strength starts to die off especially for the strong force the reason why you don't see the electromagnetic force operating over large distances even though in theory it can like gravity is that you don't see the type of charge concentrations the way you see mass concentrations in the universe because the charge concentrations tend to sort them out they start to equalize if I have if I have some if I have some positive a huge positive charge there and a huge negative charge there they will attract each other and then become essentially a big lump of neutral charge and once they're a big lump of neutral charge they won't they won't interact with anything else in gravity if you have one mass and another mass and they attract each other then you have another mass that's even better to attracting each other at other masses and so it'll keep attracting things to it so it kind of snowballs the process and that's why gravity can operates on these really really large large objects in our universe in the universe as a whole \\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[08:24.11--10:26.27]}~\ldots just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances so if you get two of these protons close enough together and the strong force only applies over very very very small distances subatomic I should even say sub nucleic distances then the strong interaction comes into play so then you have the strong interaction actually keeping these charges together and once again just to keep it in in in mind relative to gravity it is 10 to the 38th 10 38 times the strength times the strength of gravity or it's about a hundred times stronger than the electromagnetic force so once again the reason why you don't see the strong force which is the strongest of all of the forces or the weak interaction applying over huge scales is that they really only they only their strength dies off super super fast even when you start going to large radius nucleuses of atoms they strength starts to die off especially for the strong force the reason why you don't see the electromagnetic force operating over large distances even though in theory it can like gravity is that you don't see the type of charge concentrations the way you see mass concentrations in the universe because the charge concentrations tend to sort them out they start to equalize if I have if I have some if I have some positive a huge positive charge there and a huge negative charge there they will attract each other and then become essentially a big lump of neutral charge and once they're a big lump of neutral charge they won't they won't interact with anything else in gravity if you have one mass and another mass and they attract each other then you have another mass that's even better to attracting each other at other masses and so it'll keep attracting things to it so it kind of snowballs the process and that's why gravity can operates on these really really large large objects in our universe in the universe as a whole \\
     9  &          FFF &  In your body, there are a tremendous amount of negatively-charged electrons.
@@
 Which of the following explains why?
-&  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[05:32.6--08:33.14]} ...force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating...
-\\\hline
+&  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction~\ldots\smallskip\newline\textbf{[05:32.6--08:33.14]}~\ldots force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating~\ldots \\
     10 &          FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]}~\ldots anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this~\ldots \\
     11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]}~\ldots times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar~\ldots \\
     12 &          FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]}~\ldots anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this~\ldots \\
     13 &          FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 \textbf{[00:00.03--03:02.79]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 \textbf{[00:00.03--03:02.79]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each~\ldots \\
     14 &          FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction~\ldots \\
     15 &          FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \textbf{[05:38.66--06:59.96]} ...itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \textbf{[05:38.66--06:59.96]}~\ldots itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic~\ldots \\
     16 &          BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point~\ldots \\
     17 &          BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point~\ldots\smallskip\newline\textbf{[06:50.68--07:52.81]}~\ldots there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out~\ldots \\
     18 &          BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen...\newline\textbf{[05:50.32--07:00.25]} ...helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen~\ldots\smallskip\newline\textbf{[05:50.32--07:00.25]}~\ldots helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few~\ldots \\
     19 &          BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   \textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   \textbf{[02:24.67--03:53.08]}~\ldots learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the~\ldots \\
     20 &          BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[03:36.34--05:04.75]} ...you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[03:36.34--05:04.75]}~\ldots you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not~\ldots \\
     21 &          BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]}~\ldots actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out~\ldots \\
     22 &          BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point~\ldots\smallskip\newline\textbf{[02:24.67--03:53.08]}~\ldots learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the~\ldots \\
     23 &          BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point~\ldots\smallskip\newline\textbf{[02:24.67--03:53.08]}~\ldots learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the~\ldots \\
     24 &          BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[02:26.05--04:49.15]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[02:26.05--04:49.15]}~\ldots they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the~\ldots \\
     25 &          BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[05:47.08--07:01.75]} ...eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[05:47.08--07:01.75]}~\ldots eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the~\ldots \\
     26 &          BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:26.05--03:51.37]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]}~\ldots and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point~\ldots\smallskip\newline\textbf{[02:26.05--03:51.37]}~\ldots they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron~\ldots \\
     27 &          BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]}~\ldots actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out~\ldots \\
     28 &          BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
-\\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]}~\ldots actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out~\ldots \\
     29 &          BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\\hline
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
     30 &          BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]} ...most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
-\\\hline
-
-\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
-text embeddings for each question about \textit{Four Fundamental Forces} (FFF)
-and \textit{Birth of Stars} (BoS) to identify corresponding matching intervals of the
-lectures. The text of the questions and the best-matching time intervals of the
-lecture transcripts are displayed (lecture times are noted in square brackets).
-Time courses of topic correlations for each question may be found in
-Supplementary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
-no matching lecture interval was found for Question 29.} 
-\label{tab:matches}
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]}~\ldots most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium~\ldots\smallskip\newline\textbf{[06:50.68--07:52.81]}~\ldots there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out~\ldots \\
   \end{longtable}
@@
 
-\begin{figure}[tp]
+\clearpage
+
+\section*{Supplementary figures}
+
+\begin{figure}[b!]
     \includegraphics[width=\textwidth]{figs/topic-word-distributions}
@@
 
+\FloatBarrier
+
+\section*{Supplementary discussion}
+
 \end{document}

### 2025-02-24 paper/main.tex
shortened and cleaned up discussion on LDA vs BERT + LDA vs Jaccard sim

@@
 \usepackage{amsmath}
-\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{lineno}
-
 \usepackage{xcolor}
@@
 
-% supplemental tables
+% supplementary tables
 \newcommand{\questions}{1}
@@
 \newcommand{\matchTab}{3}
-
-% supplemental figures
+% supplementary figures
 \newcommand{\topicWordWeights}{1}
@@
 \newcommand{\individualLearningMapsB}{11}
-
-\newcommand{\U}{{\fontfamily{serif}\selectfont\ensuremath{\mathrm{U}}}}
+% supplementary discussion
+\newcommand{\suppResults}{\textit{Supplementary results}}
 
@@
 \newcommand{\comment}[1]{}
+
 % italicize section names in \nameref and place in \mbox to prevent bug when
@@
 \textit{conceptualize} similarly the content reflected by nearby embedding
-coordinates. How participants' knowledge falls off with spatial distance is
+coordinates. How participants' knowledge ``falls off'' with spatial distance is
 captured by the knowledge maps we infer from their quiz responses
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In our study, we characterize the ``coordinates'' of participants' knowledge
@@
 ][]{BleiEtal03}. More sophisticated text embedding models, such as
-transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23}
-can learn complex grammatical and semantic relationships between words,
-higher-order syntactic structures, stylistic features, and more. We considered
-using transformer-based models in our study, but we found that the text
-embeddings derived from these models were surprisingly uninformative with
-respect to differentiating or otherwise characterizing the conceptual content
-of the lectures and questions we used. We suspect that this reflects a broader
-challenge in constructing models that are high-resolution within a given domain
-(e.g., the domain of physics lectures and questions) \textit{and} sufficiently
-broad so as to enable them to cover a wide range of domains. For example, we
-found that the embeddings derived even from much larger and more modern models
-like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17}, LLaMa~\citep{TouvEtal23},
-and others that are trained on enormous text corpora, end up yielding poor
-resolution within the content space spanned by individual course videos
-(Supp.~Fig.~\ldaVsBERT). Whereas the LDA embeddings of the lectures and
-questions are ``near'' each other (i.e., the convex hull enclosing the two
-lectures' trajectories is highly overlapping with the convex hull enclosing the
-questions' embeddings), the BERT embeddings of the lectures and questions are
-instead largely distinct (top row of Supp.~Fig.~\ldaVsBERT). The LDA embeddings
-of the questions for each lecture and the corresponding lecture's trajectory
-are also similar. For example, as shown in Fig.~\ref{fig:sliding-windows}C, the
-LDA embeddings for \textit{Four Fundamental Forces} questions (blue dots)
-appear closer to the \textit{Four Fundamental Forces} lecture trajectory (blue
-line), whereas the LDA embeddings for \textit{Birth of Stars} questions (green
-dots) appear closer to the \textit{Birth of Stars} lecture trajectory (green
-line). The BERT embeddings of the lectures and questions do not show this
-property (Supp.~Fig.~\ldaVsBERT). We also examined per-question ``content
-matches'' between individual questions and individual moments of each lecture
-(Fig.~\ref{fig:question-correlations}, Supp.~Fig.~\ldaVsBERT). The time series
-plot of individual questions' correlations are different from each other when
-computed using LDA (e.g., the traces can be clearly visually separated), whereas
-the correlations computed from BERT embeddings of different questions all look
-very similar. This tells us that LDA is capturing some differences in content
-between the questions, whereas BERT is not. The time series plots of individual
-questions' correlations have clear ``peaks'' when computed using LDA, but not
-when computed using BERT. This tells us that LDA is capturing a ``match''
-between the content of each question and a relatively well-defined time window
-of the corresponding lectures. The BERT embeddings appear to blur together the
-content of the questions versus specific moments of each lecture. Finally, we
-also compared the pairwise correlations between embeddings of questions within
-versus across content areas (i.e., content covered by the individual lectures,
-lecture-specific questions, and by the ``general physics knowledge''
-questions). The LDA embeddings show a strong contrast between same-content
-embeddings versus across-content embeddings. In other words, the embeddings of
-questions about the \textit{Four Fundamental Forces} material are highly
-correlated with the embeddings of the \textit{Four Fundamental Forces} lecture,
-but not with the embeddings of \textit{Birth of Stars}, questions about
-\textit{Birth of Stars}, or general physics knowledge questions. We see a
-similar pattern with the LDA embeddings of the \textit{Birth of Stars}
-questions (Fig.~\ref{fig:topics}, Supp.~Fig.~\topicWeights). In contrast, the
-BERT embeddings are all highly correlated with each other (Supp.
-Fig.~\ldaVsBERT). Taken together, these comparisons illustrate how LDA (trained
-on the specific content in question) provides both coverage of the requisite
-material and specificity at the level of the content covered by individual
-questions. BERT, on the other hand, essentially assigns both lectures and all
-of the questions (which are all broadly about ``physics'') into a tiny region
-of its embedding space, thereby blurring out meaningful distinctions between
-different specific concepts covered by the lectures and questions. We note that
-these are not criticisms of BERT (or other large language models trained on
-large and diverse corpora). Rather, our point is that simple fine-tuned models
-trained on a relatively small but specialized corpus can outperform much more
-complicated models trained on much larger corpora, when we are specifically
-interested in capturing subtle conceptual differences at the level of a single
-course lecture or question. Of course if our goal had been to find a model that
-generalized to many different content areas, we would expect our approach to
-perform comparatively poorly relative to BERT or other much larger models. We
-suggest that bridging the tradeoff between high resolution within each content
-area versus the ability to generalize to many different content areas will be
-an important challenge for future work in this domain.
+transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23},
+can leverage additional textual information such as complex grammatical and 
+semantic relationships between words, higher-order syntactic structures, 
+stylistic features, and more. We considered using transformer-based models in 
+our study, but we found that the text embeddings derived from these models were 
+surprisingly uninformative with respect to differentiating or otherwise 
+characterizing the conceptual content of the lectures and questions we used 
+(see \suppResults). We suspect that this reflects a broader challenge in 
+constructing models that are both high-resolution within a given domain (e.g., 
+the domain of physics lectures and questions) \textit{and} sufficiently broad 
+as to enable them to cover a wide range of domains. Essentially, these 
+``larger'' language models learn these more complex features of language through 
+pre-training on enormous and diverse text corpora. But as a result, their 
+embedding spaces also ``span'' an enormous and diverse range of conceptual 
+content, sacrificing a degree of specificity in their capacities to distinguish 
+subtle conceptual differences within a more narrow range of content. 
+In comparing our LDA model (trained specifically on the lectures used in our 
+study) to a larger transformer-based model (BERT), we found that LDA provides 
+both coverage of the requisite material and specificity at the level of 
+individual questions, while BERT essentially relegates the contents of both 
+lectures and all quiz questions (which are all broadly about ``physics'') to a 
+tiny region of its embedding space, thereby blurring out meaningful distinctions 
+between different specific concepts covered by the lectures and questions 
+(Supp.~Fig.~\ldaVsBERT). We note that these are not criticisms of BERT, nor of 
+other large language models trained on large and diverse corpora. Rather, our 
+point is that simpler models trained on relatively small but specialized 
+corpora can outperform much more complex models trained on much larger corpora 
+when we are specifically interested in capturing subtle conceptual differences 
+at the level of a single course lecture or question. On the other hand, if our 
+goal had been to choose a model that generalized to many different content 
+domains, we would expect our LDA model to perform comparatively poorly to BERT 
+or other much larger models. We suggest that bridging this tradeoff will be
+an important challenge for future work.
+
+At the opposite end of the spectrum from large language models, one could also
+imagine using an even \textit{simpler} ``model'' than LDA that relates the 
+contents of course lectures and quiz questions through explicit word-overlap 
+metrics (rather than similarities in the latent topics they exhibit). In a 
+supplementary analysis (Supp.~Fig.~\jaccard), we compared the LDA-based 
+question-lecture matches shown in Figure~\ref{fig:question-correlations} with
+analogous matches based on the Jaccard similarity between each question's text 
+and each sliding window from the corresponding lecture's transcript. Similarly 
+to the embeddings derived from BERT, we found that this approach also blurred 
+meaningful distinctions between concepts presented in different parts of each 
+lecture and tested by different quiz questions. In this case, this lack of 
+specificity reflects that meaningful distinctions between concepts do not tend
+to emerge at the level of individual words.
+
+In this way, we view our approach as occupying a sort of ``sweet spot'' between
+much larger language models and simpler word-matching-based approaches, in that 
+it enables us to capture the relevant conceptual content of course materials at 
+the appropriate semantic scale. Our approach enables us to accurately and 
+consistently identify each question's content in a way that matches it with 
+specific content from the lectures and distinguishes it from other questions 
+about similar content. In turn, this enables us to construct accurate 
+predictions about participants' knowledge of the conceptual content tested by 
+individual quiz questions (Fig.~\ref{fig:predictions}).
 
@@
 what learners know and what they do not know.
-
-At the opposite end of the spectrum from large language models, one could also
-imagine \textit{simplifying} some aspects of our LDA-based approach by
-computing simple word overlap metrics. For example, the Jaccard similarity
-between text $A$ and $B$ is computed as the number of unique words in the
-intersection of words from $A$ and $B$ divided by the number of unique words in
-the union of words from $A$ and $B$. In a supplementary analysis
-(Supp.~Fig.~\jaccard), we compared the LDA-based question-lecture matches we
-reported in Figure~\ref{fig:question-correlations} with the Jaccard similarities
-between each question and each sliding window of text from the corresponding
-lecture. As shown in Supplementary Figure~\jaccard, this simple word-matching
-approach does not appear to capture the same level of specificity as the
-LDA-based approach. Whereas the LDA-based approach often yields a clear peak in
-the time series of correlations between each question and the corresponding
-lecture, the Jaccard similarity-based approach does not. Furthermore, these
-LDA-based matches appear to capture conceptual overlaps between the questions
-and lectures (Supp.~Tab.~\matchTab), whereas simple word matching does not. For
-example, one of the example questions examined in Supplementary
-Figure~\jaccard~asks ``Which of the following occurs as a cloud of atoms gets
-more dense?'' The LDA-based matches identify lecture timepoints where the
-relevant \textit{topics} are discussed (e.g., when words like ``cloud,''
-``atom,'' ``dense,'' etc., are mentioned \textit{together}). The Jaccard
-similarity-based matches, on the other hand, are strong when \textit{any} of
-these words are mentioned, even if they do not occur together.
-
-We view our approach as occupying a sort of ``sweet spot,'' between much larger
-language models and simple word matching-based approaches, that enables us to
-capture the relevant conceptual content of course materials at an appropriate
-semantic scale. Our approach enables us to accurately and consistently identify
-each question's content in a way that also matches up with what is presented in
-the lectures. In turn, this enables us to construct accurate predictions about
-participants' knowledge of the conceptual content tested by held-out questions
-(Fig.~\ref{fig:predictions}).
 

### 2025-02-25 paper/main.tex
reframed some ideas in discussion to clarify 'sweet spot' idea

@@
 \newcommand{\individualLearningMapsB}{11}
-% supplementary discussion
+% supplementary results
 \newcommand{\suppResults}{\textit{Supplementary results}}
@@
 multiple-choice quiz questions. Our experimental finding that we can use these 
-maps to predict responses to held-out questions has several psychological 
+maps to predict success on held-out questions has several psychological 
 implications as well. For example, concepts that are assigned to nearby 
@@
 meaningful distinctions between concepts presented in different parts of each 
-lecture and tested by different quiz questions. In this case, this lack of 
-specificity reflects that meaningful distinctions between concepts do not tend
-to emerge at the level of individual words.
-
-In this way, we view our approach as occupying a sort of ``sweet spot'' between
-much larger language models and simpler word-matching-based approaches, in that 
-it enables us to capture the relevant conceptual content of course materials at 
-the appropriate semantic scale. Our approach enables us to accurately and 
-consistently identify each question's content in a way that matches it with 
-specific content from the lectures and distinguishes it from other questions 
-about similar content. In turn, this enables us to construct accurate 
-predictions about participants' knowledge of the conceptual content tested by 
-individual quiz questions (Fig.~\ref{fig:predictions}).
+lecture and tested by different quiz questions. But rather than characterizing
+their contents at too \textit{broad} a semantic scale, the lack of specificity 
+in this approach arises from considering too \textit{narrow} a semantic scale: 
+the sorts of concepts typically conveyed in course lectures and tested by quiz 
+questions are not defined (and meaningful similarities and distinctions between 
+them do not tend to emerge) at the level of individual words.
+
+In other words, while the embedding spaces of more complex large language models 
+afford low resolution at the scale of individual course lectures and questions 
+because they ``zoom out'' too far, simpler word-matching measures yield low 
+resolution because they ``zoom \textit{in}'' too far. In this way, we view our 
+approach as occupying a sort of ``sweet spot'' between simpler and more complex 
+alternatives, in that it enables us to characterize the contents of course 
+materials at the appropriate semantic scale where relevant concepts ``come into 
+focus.'' Our approach enables us to accurately and consistently identify each 
+question's content in a way that matches it with specific content from the 
+lectures and distinguishes it from other questions about similar content. In 
+turn, this enables us to construct accurate predictions about participants' 
+knowledge of the conceptual content tested by individual quiz questions 
+(Fig.~\ref{fig:predictions}).
 
@@
 explicitly modeling the content of individual lectures or questions is to
-leverage the models' abilities to generate text. For example, generative text
+leverage these models' abilities to generate text. For example, generative text
 models like ChatGPT~\citep{ChatGPT} and LLaMa~\citep{TouvEtal23} are already

### 2025-02-27 paper/supplement.tex
finished supplementary results for BERT fig

@@
 \usepackage{geometry}
-\usepackage{natbib}
+\usepackage[sort&compress, numbers]{natbib}
 \usepackage{pxfonts}
@@
 \usepackage{ragged2e}
+
+\setcitestyle{notesep={; }}
 
@@
 
+% references to main text
+\newcommand{\slidingWindows}{2}
 \newcommand{\topicVariability}{3}
+\newcommand{\questionCorrs}{4}
 \newcommand{\knowledgeMaps}{7}
@@
     (local maxima) within each shaded region.}
+
     \label{fig:forces-peaks}
@@
 \end{figure}
-
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=0.57\textwidth]{figs/word-overlap-comparison}
-
-    \caption{\textbf{Topic correlations versus word overlap.} \textbf{A.
-    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
-    question about \textit{Four Fundamental Forces} was compared to each
-    timepoint of the lecture (dots). The blue dots denote the correlations
-    between the topic vectors, and the orange dots denote Jaccard similarities
-    (defined as the number of unique words in common between the question and
-    corresponding window of the lecture, divided by the total number of unique
-    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
-    of Stars}}. Same format as Panel A. \textbf{C. Topic correlation time series
-    plots.} This panel is in the same format as Figure 4A from the main text,
-    but here the example question highlighted in purple in Panel A has been
-    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
-    the example question highlighted in green in Panel B has been emphasized
-    for the \textit{Birth of Stars} traces on the right. \textbf{D. Jaccard
-    similarity time series plots.} These panels are in the same format as Panel
-    C, but they display the Jaccard similarity time series for the same
-    questions. \textbf{E. Question and lecture text.} The text for the example
-    purple (left) and green (right) questions is shown on top, and the text
-    from the best-matching intervals of the lectures (computed using topic
-    correlations; see Supp.~Tab.~\ref{tab:matches}) are shown on the bottom.}
-
-    \label{fig:compare-wordcount}
-\end{figure}
-
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=0.7\textwidth]{figs/model-comparison}
-
-    \caption{\textbf{Comparing LDA vs. BERT embeddings.} The rows display the
-    equivalents of main text Figure 2C (top row), Figures 4A and 4B (middle two
-    rows), and Figure 3B (bottom row) computed using LDA (left) and BERT
-    (right).}
-
-    \label{fig:compare-bert}
-\end{figure}
-
-\newpage
 
@@
 
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs/model-comparison}
+
+    \caption{\textbf{Comparing LDA vs. BERT embeddings.} The rows display the
+    equivalents of main text Figure \slidingWindows C (top row), Figures 
+    \questionCorrs A and \questionCorrs B (middle two rows), and Figure 
+    \topicVariability B (bottom row) computed using LDA (left) and BERT 
+    (right).}
+
+    \label{fig:compare-bert}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.57\textwidth]{figs/word-overlap-comparison}
+
+    \caption{\textbf{Topic correlations versus word overlap.} \textbf{A.
+    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
+    question about \textit{Four Fundamental Forces} was compared to each
+    timepoint of the lecture (dots). The blue dots denote the correlations
+    between the topic vectors, and the orange dots denote Jaccard similarities
+    (defined as the number of unique words in common between the question and
+    corresponding window of the lecture, divided by the total number of unique
+    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
+    of Stars}}. Same format as Panel A. \textbf{C. Topic correlation time series
+    plots.} This panel is in the same format as Figure 4A from the main text,
+    but here the example question highlighted in purple in Panel A has been
+    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
+    the example question highlighted in green in Panel B has been emphasized
+    for the \textit{Birth of Stars} traces on the right. \textbf{D. Jaccard
+    similarity time series plots.} These panels are in the same format as Panel
+    C, but they display the Jaccard similarity time series for the same
+    questions. \textbf{E. Question and lecture text.} The text for the example
+    purple (left) and green (right) questions is shown on top, and the text
+    from the best-matching intervals of the lectures (computed using topic
+    correlations; see Supp.~Tab.~\ref{tab:matches}) are shown on the bottom.}
+
+    \label{fig:compare-wordcount}
+\end{figure}
+
 \FloatBarrier
 
-\section*{Supplementary discussion}
+\section*{Supplementary results}
 
+\doublespacing
+
+%In our study, we construct the coordinate space through which we relate the 
+%conceptual contents of course lectures and quiz questions using a relatively 
+%simple text embedding model ~\citep[LDA; ][]{BleiEtal03} trained on overlapping 
+%sliding windows of text from the lectures' transcripts (see \topicModelMethods). 
+%While we considered using more modern and complex models trained on much 
+%larger and more diverse text corpora [e.g., BERT,~\citealp{DevlEtal18}; 
+%GPT,~\citealp{ViswEtal17}; LLaMa,~\citealp{TouvEtal23}], we found that the 
+%embeddings yielded by the LDA model exhibited a number of desirable 
+%properties that embeddings derived from larger pre-trained models did not. To
+%illustrate some of these properties, in Supplementary 
+%Figure~\ref{fig:compare-bert} we display a subset of visualizations from the 
+%main text based on our LDA embeddings (left column) alongside analogous 
+%visualizations based instead on BERT embeddings (right column). Qualitatively
+%comparing these two sets of visualizations suggests that \_\_\_\_\_
+
+In our study, we relate the conceptual contents of course lectures and quiz 
+questions by their coordinates in a high-dimensional feature space, which we 
+construct using a relatively simple text embedding model (Latent Dirichlet 
+Allocation;~\citealp{BleiEtal03}) trained on overlapping sliding windows of 
+text from the lectures' transcripts (see \topicModelMethods). In comparing our 
+approach to various alternative methods of characterizing the lectures' and 
+questions' contents, we found that LDA embeddings exhibited a number of 
+desirable properties that both simpler and more complex alternatives did not. 
+For example, we found that analogous embeddings derived from more modern and 
+complex models trained on much larger and more diverse text corpora (e.g., 
+BERT,~\citealp{DevlEtal18}; GPT,~\citealp{ViswEtal17}; 
+LLaMa,~\citealp{TouvEtal23}) tended to afford poor resolution within the content 
+space spanned by individual course lectures and quiz questions. To illustrate this contrast, in 
+Supplementary Figure~\ref{fig:compare-bert} we display a subset of 
+visualizations from the main text based on our LDA embeddings (left column) 
+alongside analogous visualizations based instead on BERT embeddings (right 
+column).
+
+The top row of Supplementary Figure~\ref{fig:compare-bert} displays PCA 
+projections of the two lectures' trajectories and 39 quiz questions' 
+coordinates within the embedding space of each model (analogous to 
+Figure~{\slidingWindows}C in the main text). Qualitatively comparing these two
+sets of projections reveals a number of notable differences. For example, 
+whereas the LDA embeddings of the lectures and questions are ``near'' each 
+other (i.e., the convex hull enclosing the two lectures' trajectories is highly 
+overlapping with the convex hull enclosing the questions' embeddings), the BERT 
+embeddings of the lectures and questions are instead largely distinct. The LDA 
+embeddings of the questions about each lecture and the corresponding lecture's 
+trajectory are also similar: \textit{Four Fundamental Forces}-related questions 
+(blue dots) generally appear closer to the \textit{Four Fundamental Forces} 
+lecture trajectory (blue line), while \textit{Birth of Stars}-related questions 
+(green dots) generally appear closer to the \textit{Birth of Stars} lecture trajectory 
+(green line). The BERT embeddings of the lectures and questions do not display 
+this property.
+
+The second row of Supplementary Figure~\ref{fig:compare-bert} offers a more 
+quantitative version of the comparisons above. 
+Here, for the embeddings derived from each model, we show the pairwise correlations between the variance in each feature dimension's weight, across timepoints from each lecture and quiz questions about each content area
+(analogous to main text Fig.~\topicVariability B).
+The LDA embeddings show a strong contrast between same-content embeddings and across-content embeddings.
+In other words, the the amount of ``information'' about different features (i.e., topics) reflected in each lecture's content is highly similar to the amount of information reflected in the contents of its corresponding quiz questions, and dissimilar from that of other subsets of quiz questions.
+The BERT embeddings, by contrast, do not exhibit these clear distinctions between content areas, and instead represent \textit{all} course materials used in our study highly similarly overall.
+This indicates that, relative to enormous breadth of conceptual content BERT embeddings can represent, representations of concepts that are specifically related to \textit{Four Fundamental Forces}, specifically related to \textit{Birth of Stars}, and related to physics more generally are so similar as to be almost indistinguishable.
+Additionally, the relative similarities (i.e., correlations) between lectures and question sets indicate that both lectures are represented more similarly to each other than to any subset of quiz questions, and each subset of quiz questions is represented more similarly to other quiz questions than to either lecture.
+This mirrors the separation between the lectures and questions visible in their PCA projections above, and suggests that BERT's representations of the subtle, specific semantic features that link the lecture and questions within each content area, and distinguish between different content areas, are sufficiently weak that they are overpowered by representations of \textit{syntactic} features that tend to distinguish questions from lectures more broadly (e.g., beginning with words like ``What'', ``Which'', or ``Why'', ending with a question mark, etc.).
+Taken together, first two rows of Supplementary Figure~\ref{fig:compare-bert} suggest that a simple LDA model trained on the specific lectures used in our study can ``match'' quiz questions to their corresponding lectures by similarities in their embedding weights, while BERT (trained on a much broader text corpus) cannot.
+
+We also examined both models' abilities to match the quiz questions to specific temporal intervals within the lectures.
+The third and fourth rows of Supplementary Figure~\ref{fig:compare-bert} display the time series of correlations between the embedding weights for each quiz question and each timepoint of its corresponding lecture (third row: \textit{Four Fundamental Forces}; fourth row: \textit{Birth of Stars}; analogous to main text Fig.~\questionCorrs).
+When computed using LDA embeddings, the questions' correlation time series generally appear fairly different from each other (i.e., individual questions' traces can be easily visually separated), whereas their correlation time series computed using BERT embeddings are all highly similar.
+This indicates that the LDA embeddings are capturing some differences in content between the questions about a given lecture that the BERT embeddings are not.
+The time series plots of individual questions' correlations also exhibit clear ``peaks'' when computed using LDA embeddings, but not when computed using BERT embeddings.
+This indicates that the LDA embeddings are capturing specific ``matches'' between individual quiz questions and relatively well defined time periods of lecture content, whereas the BERT embeddings appear to blue these specific correspondences.
+Taken together, these comparisons suggest that our LDA model trained specifically on the two lectures' contents is sensitive to subtle differences between the concepts probed by individual quiz questions, and can identify the relevant periods in the lectures where those concepts where presented (Fig.~\questionCorrs, Supp.~Figs.~\ref{fig:forces-peaks},~\ref{fig:bos-peaks}, Supp.~Tab.~\ref{tab:matches}).
+Meanwhile, BERT, whose embedding weights must be able to represent a far broader range of concepts, consequently blurs these subtle distinctions between concepts conveyed within the span of a single course lecture, thereby affording a ``lower resolution'' depiction of its contents.
+
+\clearpage
+\bibliographystyle{apa}
+\renewcommand{\refname}{Supplementary references}
+\bibliography{CDL-bibliography/cdl}
 \end{document}

### 2025-02-28 paper/supplement.tex
finished edits to supplement

@@
 The time series plots of individual questions' correlations also exhibit clear ``peaks'' when computed using LDA embeddings, but not when computed using BERT embeddings.
-This indicates that the LDA embeddings are capturing specific ``matches'' between individual quiz questions and relatively well defined time periods of lecture content, whereas the BERT embeddings appear to blue these specific correspondences.
+This indicates that the LDA embeddings are capturing specific ``matches'' between individual quiz questions and relatively well defined time periods of lecture content, whereas the BERT embeddings appear to blur these specific correspondences.
 Taken together, these comparisons suggest that our LDA model trained specifically on the two lectures' contents is sensitive to subtle differences between the concepts probed by individual quiz questions, and can identify the relevant periods in the lectures where those concepts where presented (Fig.~\questionCorrs, Supp.~Figs.~\ref{fig:forces-peaks},~\ref{fig:bos-peaks}, Supp.~Tab.~\ref{tab:matches}).
 Meanwhile, BERT, whose embedding weights must be able to represent a far broader range of concepts, consequently blurs these subtle distinctions between concepts conveyed within the span of a single course lecture, thereby affording a ``lower resolution'' depiction of its contents.
+
+We also compared the within-lecture question matches identified by our LDA-based approach to analogous matches obtained via a simpler approach that did \textit{not} entail using a text embedding model.
+Instead of projecting the text of the lectures and quiz questions into a common space and relating them by the similarities (i.e., correlations) between their coordinates (i.e., topic vectors), in this approach we related them by a measure of similarity computed directly from their texts.
+Specifically, we first parsed the two lectures' transcripts into overlapping sliding windows and performed the same preprocessing as we did for our LDA-based approach (see~\topicModelMethods).
+We then computed the Jaccard similarity between the text of each lecture-related quiz question and each sliding window from its corresponding lecture's transcript.
+Here, the Jaccard similarity between a question $Q$ and a lecture window $W$ is defined as the number of unique words that appear in the texts of both $Q$ and $W$ (i.e., $Q \cap W$) divided by the number of unique words that appear in either $Q$ or $W$ (i.e., $Q \cup W$).
+
+As shown in Supplementary Figure~\ref{fig:compare-wordcount}, this simple word-matching approach does not appear to capture the same level of specificity as our LDA-based approach.
+Panels A and B display each question's distribution of topic vector correlations with all lecture timepoints (blue dots) alongside its distribution of Jaccard similarities to all sliding windows (orange dots).
+In these panels, both similarity measures have been normalized (independently, and separately for each question) to range between 0 and 1, such that a similarity of 1 reflects each question's ``best matching'' sample of lecture content, and a similarity of 0 reflects the least similar lecture content.
+In most cases, the distributions of topic vector correlations are dominated by extreme values (i.e., values close to 0 or 1) with comparatively few intermediate values.
+In other words, this approach yields strong and specific matches: each question's similarity is near its maximum value for a particular set of timepoints, and tends to be close to its minimum value for most other timepoints.
+The distributions of Jaccard similarities show the opposite pattern, consisting primarily of intermediate values with very few extreme values.
+In other words, this approach tends to weakly match each question to a large proportion of the lecture content.
+
+These patterns are reflected in the similarity time series plots shown in panels C and D (analogous to main text Fig.~\questionCorrs).
+The questions' time series of topic vector correlations exhibit visually distinct ``peaks'' during specific sections of the lectures, outside of which their correlations tend to be relatively low.
+In other words, the set of timepoints whose topic vectors are maximally correlated with the topic vector for a given question tend to be not only specific, but also temporally contiguous.
+This indicates that topic vector correlation matches questions with sustained, cohesive periods of lecture content where the relevant underlying \textit{concepts} are discussed, rather than with a sporadic assortment of timepoints where the question and lecture content share more superficial similarities.
+The time series of Jaccard similarities, by contrast, are less cleanly structured and do appear to reflect such superficial content matches in the more scattered, brief, and weak ``peaks'' they exhibit.
+As an example, panel E displays text of the two quiz questions highlighted in green and purple in panels A through D, along with the text from the best-matching intervals from the lectures (identified based on topic vector correlation).
+Both questions include words that---given the subject matter of the two lectures---appear frequently throughout their transcripts (e.g., ``\textit{force}'', ``\textit{atom}'', ``\textit{nucleus}'', ``\textit{cloud}'', ``\textit{dense}'', etc.).
+While the presence or absence of any one (or more) of these words will lead to differences in the degree of ``match'' based on Jaccard similarity (resulting in the ``jagged'' time series shown in panel D), LDA is able to capture some notion of the \textit{context} in which different usages of the same words occur.
+As a result, the model is able to successfully assign similar topic vectors to quiz questions and lecture timepoints specifically when their shared combinations of words denote the same deeper meaning.
 

### 2025-02-28 paper/supplement.tex
cleaned up source file formatting

@@
 
-    \caption{\textbf{Comparing LDA vs. BERT embeddings.} The rows display the
+    \caption{\textbf{Comparing LDA vs.~BERT embeddings.} The rows display the
     equivalents of main text Figure \slidingWindows C (top row), Figures 
@@
 
-%In our study, we construct the coordinate space through which we relate the 
-%conceptual contents of course lectures and quiz questions using a relatively 
-%simple text embedding model ~\citep[LDA; ][]{BleiEtal03} trained on overlapping 
-%sliding windows of text from the lectures' transcripts (see \topicModelMethods). 
-%While we considered using more modern and complex models trained on much 
-%larger and more diverse text corpora [e.g., BERT,~\citealp{DevlEtal18}; 
-%GPT,~\citealp{ViswEtal17}; LLaMa,~\citealp{TouvEtal23}], we found that the 
-%embeddings yielded by the LDA model exhibited a number of desirable 
-%properties that embeddings derived from larger pre-trained models did not. To
-%illustrate some of these properties, in Supplementary 
-%Figure~\ref{fig:compare-bert} we display a subset of visualizations from the 
-%main text based on our LDA embeddings (left column) alongside analogous 
-%visualizations based instead on BERT embeddings (right column). Qualitatively
-%comparing these two sets of visualizations suggests that \_\_\_\_\_
-
 In our study, we relate the conceptual contents of course lectures and quiz 
@@
 LLaMa,~\citealp{TouvEtal23}) tended to afford poor resolution within the content 
-space spanned by individual course lectures and quiz questions. To illustrate this contrast, in 
-Supplementary Figure~\ref{fig:compare-bert} we display a subset of 
-visualizations from the main text based on our LDA embeddings (left column) 
-alongside analogous visualizations based instead on BERT embeddings (right 
-column).
+space spanned by individual course lectures and quiz questions. To illustrate 
+this contrast, in Supplementary Figure~\ref{fig:compare-bert} we display a 
+subset of visualizations from the main text based on our LDA embeddings (left 
+column) alongside analogous visualizations based instead on BERT embeddings 
+(right column).
 
@@
 lecture trajectory (blue line), while \textit{Birth of Stars}-related questions 
-(green dots) generally appear closer to the \textit{Birth of Stars} lecture trajectory 
-(green line). The BERT embeddings of the lectures and questions do not display 
-this property.
+(green dots) generally appear closer to the \textit{Birth of Stars} lecture 
+trajectory (green line). The BERT embeddings of the lectures and questions do 
+not display this property.
 
 The second row of Supplementary Figure~\ref{fig:compare-bert} offers a more 
-quantitative version of the comparisons above. 
-Here, for the embeddings derived from each model, we show the pairwise correlations between the variance in each feature dimension's weight, across timepoints from each lecture and quiz questions about each content area
-(analogous to main text Fig.~\topicVariability B).
-The LDA embeddings show a strong contrast between same-content embeddings and across-content embeddings.
-In other words, the the amount of ``information'' about different features (i.e., topics) reflected in each lecture's content is highly similar to the amount of information reflected in the contents of its corresponding quiz questions, and dissimilar from that of other subsets of quiz questions.
-The BERT embeddings, by contrast, do not exhibit these clear distinctions between content areas, and instead represent \textit{all} course materials used in our study highly similarly overall.
-This indicates that, relative to enormous breadth of conceptual content BERT embeddings can represent, representations of concepts that are specifically related to \textit{Four Fundamental Forces}, specifically related to \textit{Birth of Stars}, and related to physics more generally are so similar as to be almost indistinguishable.
-Additionally, the relative similarities (i.e., correlations) between lectures and question sets indicate that both lectures are represented more similarly to each other than to any subset of quiz questions, and each subset of quiz questions is represented more similarly to other quiz questions than to either lecture.
-This mirrors the separation between the lectures and questions visible in their PCA projections above, and suggests that BERT's representations of the subtle, specific semantic features that link the lecture and questions within each content area, and distinguish between different content areas, are sufficiently weak that they are overpowered by representations of \textit{syntactic} features that tend to distinguish questions from lectures more broadly (e.g., beginning with words like ``What'', ``Which'', or ``Why'', ending with a question mark, etc.).
-Taken together, first two rows of Supplementary Figure~\ref{fig:compare-bert} suggest that a simple LDA model trained on the specific lectures used in our study can ``match'' quiz questions to their corresponding lectures by similarities in their embedding weights, while BERT (trained on a much broader text corpus) cannot.
+quantitative version of the comparisons above. Here, for the embeddings derived 
+from each model, we show the pairwise correlations between the variance in each 
+feature dimension's weight, across timepoints from each lecture and quiz 
+questions about each content area (analogous to main text 
+Fig.~\topicVariability B). The LDA embeddings show a strong contrast between 
+same-content embeddings and across-content embeddings. In other words, the the 
+amount of ``information'' about different features (i.e., topics) reflected in 
+each lecture's content is highly similar to the amount of information reflected 
+in the contents of its corresponding quiz questions, and dissimilar from that of 
+other subsets of quiz questions. The BERT embeddings, by contrast, do not 
+exhibit these clear distinctions between content areas, and instead represent 
+\textit{all} course materials used in our study highly similarly overall. This 
+indicates that, relative to enormous breadth of conceptual content BERT 
+embeddings can represent, representations of concepts that are specifically 
+related to \textit{Four Fundamental Forces}, specifically related to 
+\textit{Birth of Stars}, and related to physics more generally are so similar as 
+to be almost indistinguishable. Additionally, the relative similarities (i.e., 
+correlations) between lectures and question sets indicate that both lectures are 
+represented more similarly to each other than to any subset of quiz questions, 
+and each subset of quiz questions is represented more similarly to other quiz 
+questions than to either lecture. This mirrors the separation between the 
+lectures and questions visible in their PCA projections above, and suggests that 
+BERT's representations of the subtle, specific semantic features that link the 
+lecture and questions within each content area, and distinguish between 
+different content areas, are sufficiently weak that they are overpowered by 
+representations of \textit{syntactic} features that tend to distinguish 
+questions from lectures more broadly (e.g., beginning with words like ``What'', 
+``Which'', or ``Why'', ending with a question mark, etc.). Taken together, first 
+two rows of Supplementary Figure~\ref{fig:compare-bert} suggest that a simple 
+LDA model trained on the specific lectures used in our study can ``match'' quiz 
+questions to their corresponding lectures by similarities in their embedding 
+weights, while BERT (trained on a much broader text corpus) cannot.
 
-We also examined both models' abilities to match the quiz questions to specific temporal intervals within the lectures.
-The third and fourth rows of Supplementary Figure~\ref{fig:compare-bert} display the time series of correlations between the embedding weights for each quiz question and each timepoint of its corresponding lecture (third row: \textit{Four Fundamental Forces}; fourth row: \textit{Birth of Stars}; analogous to main text Fig.~\questionCorrs).
-When computed using LDA embeddings, the questions' correlation time series generally appear fairly different from each other (i.e., individual questions' traces can be easily visually separated), whereas their correlation time series computed using BERT embeddings are all highly similar.
-This indicates that the LDA embeddings are capturing some differences in content between the questions about a given lecture that the BERT embeddings are not.
-The time series plots of individual questions' correlations also exhibit clear ``peaks'' when computed using LDA embeddings, but not when computed using BERT embeddings.
-This indicates that the LDA embeddings are capturing specific ``matches'' between individual quiz questions and relatively well defined time periods of lecture content, whereas the BERT embeddings appear to blur these specific correspondences.
-Taken together, these comparisons suggest that our LDA model trained specifically on the two lectures' contents is sensitive to subtle differences between the concepts probed by individual quiz questions, and can identify the relevant periods in the lectures where those concepts where presented (Fig.~\questionCorrs, Supp.~Figs.~\ref{fig:forces-peaks},~\ref{fig:bos-peaks}, Supp.~Tab.~\ref{tab:matches}).
-Meanwhile, BERT, whose embedding weights must be able to represent a far broader range of concepts, consequently blurs these subtle distinctions between concepts conveyed within the span of a single course lecture, thereby affording a ``lower resolution'' depiction of its contents.
+We also examined both models' abilities to match the quiz questions to specific 
+temporal intervals within the lectures. The third and fourth rows of 
+Supplementary Figure~\ref{fig:compare-bert} display the time series of 
+correlations between the embedding weights for each quiz question and each 
+timepoint of its corresponding lecture (third row: \textit{Four Fundamental 
+Forces}; fourth row: \textit{Birth of Stars}; analogous to main text 
+Fig.~\questionCorrs). When computed using LDA embeddings, the questions' 
+correlation time series generally appear fairly different from each other (i.e., 
+individual questions' traces can be easily visually separated), whereas their 
+correlation time series computed using BERT embeddings are all highly similar. 
+This indicates that the LDA embeddings are capturing some differences in content 
+between the questions about a given lecture that the BERT embeddings are not. 
+The time series plots of individual questions' correlations also exhibit clear 
+``peaks'' when computed using LDA embeddings, but not when computed using BERT 
+embeddings. This indicates that the LDA embeddings are capturing specific 
+``matches'' between individual quiz questions and relatively well defined time 
+periods of lecture content, whereas the BERT embeddings appear to blur these 
+specific correspondences. Taken together, these comparisons suggest that our LDA 
+model trained specifically on the two lectures' contents is sensitive to subtle 
+differences between the concepts probed by individual quiz questions, and can 
+identify the relevant periods in the lectures where those concepts where 
+presented (Fig.~\questionCorrs, 
+Supp.~Figs.~\ref{fig:forces-peaks},~\ref{fig:bos-peaks}, 
+Supp.~Tab.~\ref{tab:matches}). Meanwhile, BERT, whose embedding weights must be 
+able to represent a far broader range of concepts, consequently blurs these 
+subtle distinctions between concepts conveyed within the span of a single course 
+lecture, thereby affording a ``lower resolution'' depiction of its contents.
 
-We also compared the within-lecture question matches identified by our LDA-based approach to analogous matches obtained via a simpler approach that did \textit{not} entail using a text embedding model.
-Instead of projecting the text of the lectures and quiz questions into a common space and relating them by the similarities (i.e., correlations) between their coordinates (i.e., topic vectors), in this approach we related them by a measure of similarity computed directly from their texts.
-Specifically, we first parsed the two lectures' transcripts into overlapping sliding windows and performed the same preprocessing as we did for our LDA-based approach (see~\topicModelMethods).
-We then computed the Jaccard similarity between the text of each lecture-related quiz question and each sliding window from its corresponding lecture's transcript.
-Here, the Jaccard similarity between a question $Q$ and a lecture window $W$ is defined as the number of unique words that appear in the texts of both $Q$ and $W$ (i.e., $Q \cap W$) divided by the number of unique words that appear in either $Q$ or $W$ (i.e., $Q \cup W$).
+We also compared the within-lecture question matches identified by our LDA-based 
+approach to analogous matches obtained via a simpler approach that did 
+\textit{not} entail using a text embedding model. Instead of projecting the text 
+of the lectures and quiz questions into a common space and relating them by the 
+similarities (i.e., correlations) between their coordinates (i.e., topic 
+vectors), in this approach we related them by a measure of similarity computed 
+directly from their texts. Specifically, we first parsed the two lectures' 
+transcripts into overlapping sliding windows and performed the same 
+preprocessing as we did for our LDA-based approach (see~\topicModelMethods). We 
+then computed the Jaccard similarity between the text of each lecture-related 
+quiz question and each sliding window from its corresponding lecture's 
+transcript. Here, the Jaccard similarity between a question $Q$ and a lecture 
+window $W$ is defined as the number of unique words that appear in the texts of 
+both $Q$ and $W$ (i.e., $Q \cap W$) divided by the number of unique words that 
+appear in either $Q$ or $W$ (i.e., $Q \cup W$).
 
-As shown in Supplementary Figure~\ref{fig:compare-wordcount}, this simple word-matching approach does not appear to capture the same level of specificity as our LDA-based approach.
-Panels A and B display each question's distribution of topic vector correlations with all lecture timepoints (blue dots) alongside its distribution of Jaccard similarities to all sliding windows (orange dots).
-In these panels, both similarity measures have been normalized (independently, and separately for each question) to range between 0 and 1, such that a similarity of 1 reflects each question's ``best matching'' sample of lecture content, and a similarity of 0 reflects the least similar lecture content.
-In most cases, the distributions of topic vector correlations are dominated by extreme values (i.e., values close to 0 or 1) with comparatively few intermediate values.
-In other words, this approach yields strong and specific matches: each question's similarity is near its maximum value for a particular set of timepoints, and tends to be close to its minimum value for most other timepoints.
-The distributions of Jaccard similarities show the opposite pattern, consisting primarily of intermediate values with very few extreme values.
-In other words, this approach tends to weakly match each question to a large proportion of the lecture content.
+As shown in Supplementary Figure~\ref{fig:compare-wordcount}, this simple 
+word-matching approach does not appear to capture the same level of specificity 
+as our LDA-based approach. Panels A and B display each question's distribution 
+of topic vector correlations with all lecture timepoints (blue dots) alongside 
+its distribution of Jaccard similarities to all sliding windows (orange dots). 
+In these panels, both similarity measures have been normalized (independently, 
+and separately for each question) to range between 0 and 1, such that a 
+similarity of 1 reflects each question's ``best matching'' sample of lecture 
+content, and a similarity of 0 reflects the least similar lecture content. In 
+most cases, the distributions of topic vector correlations are dominated by 
+extreme values (i.e., values close to 0 or 1) with comparatively few 
+intermediate values. In other words, this approach yields strong and specific 
+matches: each question's similarity is near its maximum value for a particular 
+set of timepoints, and tends to be close to its minimum value for most other 
+timepoints. The distributions of Jaccard similarities show the opposite pattern, 
+consisting primarily of intermediate values with very few extreme values. In 
+other words, this approach tends to weakly match each question to a large 
+proportion of the lecture content.
 
-These patterns are reflected in the similarity time series plots shown in panels C and D (analogous to main text Fig.~\questionCorrs).
-The questions' time series of topic vector correlations exhibit visually distinct ``peaks'' during specific sections of the lectures, outside of which their correlations tend to be relatively low.
-In other words, the set of timepoints whose topic vectors are maximally correlated with the topic vector for a given question tend to be not only specific, but also temporally contiguous.
-This indicates that topic vector correlation matches questions with sustained, cohesive periods of lecture content where the relevant underlying \textit{concepts} are discussed, rather than with a sporadic assortment of timepoints where the question and lecture content share more superficial similarities.
-The time series of Jaccard similarities, by contrast, are less cleanly structured and do appear to reflect such superficial content matches in the more scattered, brief, and weak ``peaks'' they exhibit.
-As an example, panel E displays text of the two quiz questions highlighted in green and purple in panels A through D, along with the text from the best-matching intervals from the lectures (identified based on topic vector correlation).
-Both questions include words that---given the subject matter of the two lectures---appear frequently throughout their transcripts (e.g., ``\textit{force}'', ``\textit{atom}'', ``\textit{nucleus}'', ``\textit{cloud}'', ``\textit{dense}'', etc.).
-While the presence or absence of any one (or more) of these words will lead to differences in the degree of ``match'' based on Jaccard similarity (resulting in the ``jagged'' time series shown in panel D), LDA is able to capture some notion of the \textit{context} in which different usages of the same words occur.
-As a result, the model is able to successfully assign similar topic vectors to quiz questions and lecture timepoints specifically when their shared combinations of words denote the same deeper meaning.
+These patterns are reflected in the similarity time series plots shown in panels 
+C and D (analogous to main text Fig.~\questionCorrs). The questions' time series 
+of topic vector correlations exhibit visually distinct ``peaks'' during specific 
+sections of the lectures, outside of which their correlations tend to be 
+relatively low. In other words, the set of timepoints whose topic vectors are 
+maximally correlated with the topic vector for a given question tend to be not 
+only specific, but also temporally contiguous. This indicates that topic vector 
+correlation matches questions with sustained, cohesive periods of lecture 
+content where the relevant underlying \textit{concepts} are discussed, rather 
+than with a sporadic assortment of timepoints where the question and lecture 
+content share more superficial similarities. The time series of Jaccard 
+similarities, by contrast, are less cleanly structured and do appear to reflect 
+such superficial content matches in the more scattered, brief, and weak 
+``peaks'' they exhibit. As an example, panel E displays text of the two quiz 
+questions highlighted in green and purple in panels A through D, along with the 
+text from the best-matching intervals from the lectures (identified based on
+topic vector correlation). Both questions include words that---given the subject 
+matter of the two lectures---appear frequently throughout their transcripts 
+(e.g., ``\textit{force}'', ``\textit{atom}'', ``\textit{nucleus}'', 
+``\textit{cloud}'', ``\textit{dense}'', etc.). While the presence or absence of 
+any one (or more) of these words will lead to differences in the degree of 
+``match'' based on Jaccard similarity (resulting in the ``jagged'' time series
+shown in panel D), LDA is able to capture some notion of the \textit{context} in 
+which different usages of the same words occur. As a result, the model is able 
+to successfully assign similar topic vectors to quiz questions and lecture 
+timepoints specifically when their shared combinations of words denote the same 
+deeper meaning.
 

### 2025-02-28 paper/supplement.tex
fixed supp fig 10 caption to match new order

@@
     \caption{\textbf{Comparing LDA vs.~BERT embeddings.} The rows display the
-    equivalents of main text Figure \slidingWindows C (top row), Figures 
-    \questionCorrs A and \questionCorrs B (middle two rows), and Figure 
-    \topicVariability B (bottom row) computed using LDA (left) and BERT 
+    equivalents of main text Figure \slidingWindows C (top row), Figure 
+    \topicVariability B (second row), and Figures \questionCorrs A and 
+    \questionCorrs B (bottom two rows) computed using LDA (left) and BERT 
     (right).}

### 2025-03-01 paper/main.tex
update references to supp figs to match new order
minor rephrasings to clarify intent of BERT/LDA comparisons

@@
 \newcommand{\bosCorrs}{4}
-\newcommand{\jaccard}{5}
-\newcommand{\ldaVsBERT}{6}
-\newcommand{\individualKnowledgeMapsA}{7}
-\newcommand{\individualKnowledgeMapsB}{8}
-\newcommand{\individualKnowledgeMapsC}{9}
-\newcommand{\individualLearningMapsA}{10}
-\newcommand{\individualLearningMapsB}{11}
+\newcommand{\individualKnowledgeMapsA}{5}
+\newcommand{\individualKnowledgeMapsB}{6}
+\newcommand{\individualKnowledgeMapsC}{7}
+\newcommand{\individualLearningMapsA}{8}
+\newcommand{\individualLearningMapsB}{9}
+\newcommand{\jaccard}{10}
+\newcommand{\ldaVsBERT}{11}
 % supplementary results
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In our study, we characterize the ``coordinates'' of participants' knowledge
@@
 ``larger'' language models learn these more complex features of language through 
-pre-training on enormous and diverse text corpora. But as a result, their 
+training on enormous and diverse text corpora. But as a result, their 
 embedding spaces also ``span'' an enormous and diverse range of conceptual 
@@
 In comparing our LDA model (trained specifically on the lectures used in our 
-study) to a larger transformer-based model (BERT), we found that LDA provides 
+study) to a larger transformer-based model (BERT), we found that our LDA model provides 
 both coverage of the requisite material and specificity at the level of 
@@
 when we are specifically interested in capturing subtle conceptual differences 
-at the level of a single course lecture or question. On the other hand, if our 
-goal had been to choose a model that generalized to many different content 
-domains, we would expect our LDA model to perform comparatively poorly to BERT 
-or other much larger models. We suggest that bridging this tradeoff will be
-an important challenge for future work.
+at the level of a single course lecture or quiz question. On the other hand, if 
+our goal had been to choose a model that generalized to many different content 
+areas, we would expect our LDA model to perform comparatively poorly to BERT or 
+other much larger general-purpose models. We suggest that bridging this tradeoff 
+between high resolution within a single content area and the ability to 
+generalize to many diverse content areas will be an important challenge for 
+future work.
 

### 2025-03-02 paper/supplement.tex

@@
 approach to various alternative methods of characterizing the lectures' and 
-questions' contents, we found that LDA embeddings exhibited a number of 
-desirable properties that both simpler and more complex alternatives did not. 
-For example, we found that analogous embeddings derived from more modern and 
-complex models trained on much larger and more diverse text corpora (e.g., 
-BERT,~\citealp{DevlEtal18}; GPT,~\citealp{ViswEtal17}; 
-LLaMa,~\citealp{TouvEtal23}) tended to afford poor resolution within the content 
-space spanned by individual course lectures and quiz questions. To illustrate 
-this contrast, in Supplementary Figure~\ref{fig:compare-bert} we display a 
-subset of visualizations from the main text based on our LDA embeddings (left 
-column) alongside analogous visualizations based instead on BERT embeddings 
-(right column).
+questions' contents, we found that embeddings derived from our corpus-specific 
+LDA model exhibited a number of desirable properties that both simpler and more 
+complex alternatives did not. For example, we found that analogous embeddings 
+derived from more modern and complex models trained on much larger and more 
+diverse text corpora (e.g., BERT,~\citealp{DevlEtal18}; 
+GPT,~\citealp{ViswEtal17}; LLaMa,~\citealp{TouvEtal23}) tended to afford poor 
+resolution within the content space spanned by individual course lectures and 
+quiz questions. To illustrate this contrast, in Supplementary 
+Figure~\ref{fig:compare-bert} we display a subset of visualizations from the 
+main text based on our LDA embeddings (left column) alongside analogous 
+visualizations based instead on BERT embeddings (right column).
 

### 2025-05-23 paper/main.tex
final edits and cleanup through main text page 33

@@
 \NewCommandCopy{\oldnameref}{\nameref}
-\renewcommand{\nameref}[1]{\mbox{\textit{\oldnameref{#1}}}}
+\renewcommand{\nameref}[1]{\textit{\oldnameref{#1}}}
 
@@
 detail, versus a single annotation saying that the student answered 85\% of
-their quiz questions correctly, or that they received a `B'. Here, we show that
+their quiz questions correctly, or that they received a `B'. Here we show that
 the same quiz data required to compute proportion-correct scores or letter
@@
 patterns in how those elements appear across different scales (e.g.,
-sentences, paragraphs, chapters, etc.), the temporal and grammatical
-properties of the elements, and other high-level characteristics of
+sentences, paragraphs, chapters, etc.), their temporal and grammatical
+properties, and other high-level characteristics of
 how they are used~\citep{Mann23b, Mann21a}.
@@
 at capturing an analogue of ``understanding'' is able to assign nearby
-feature vectors to two conceptually related documents, \textit{even
+feature vectors to two conceptually related documents \textit{even
   when the specific words contained in those documents have limited
@@
     5 questions about Lecture~2, and 3 questions about general physics
-    knowledge. The specific questions reflected on each quiz, and the orders of
+    knowledge. The specific questions appearing on each quiz, and the orders of
     each quiz's questions, were randomized across participants.}
@@
 their respective content areas. Second, we wanted the two lectures to have some
-related content, so that we could test our approach's ability to distinguish
+related content so that we could test our approach's ability to distinguish
 similar conceptual content. To this end, we chose two videos from the same Khan
@@
 model can be used to transform arbitrary (potentially new) documents into sets
-of ``topic proportions,'' describing the weighted blend of learned topics
+of ``topic proportions'' describing the weighted blend of learned topics
 reflected in their texts. We parsed automatically generated transcripts of the
@@
 lecture and questions \textit{about} each lecture. Importantly, such a
-correspondence could not solely arise from superficial text matching between
+correspondence could not arise solely from superficial text matching between
 lecture transcripts and questions, since the lectures and questions often used
@@
 (Supp.~Fig.~\topicWeights). Specifically, the average topic weights from Lecture~1 are
-strongly correlated with the average topic weights from Lecture~1 questions
+strongly correlated with the average topic weights from questions about Lecture~1
 ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval (CI)~$= [0.633,~0.962]$),
 and the average topic weights from Lecture~2 are strongly correlated with the
-average topic weights from Lecture~2 questions ($r(13) = 0.728,~p = 0.002$,
+average topic weights from questions about Lecture~2 ($r(13) = 0.728,~p = 0.002$,
 95\% CI~$= [0.456,~0.920]$). At the same time, the average topic weights from
@@
     \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic
-    weight variability}. The bar plots display the variance of each topic's
+    weight variability}. The bar plots display the variance in each topic's
     weight across lecture timepoints (top row) and questions (bottom row);
@@
 property of the lecture \textit{overall} (conceptual or otherwise), but unless
-the topic's weights changed in meaningful ways over time, the topic would be a
+the topic's weights change in meaningful ways over time, it would be a
 poor indicator of any \textit{specific} conceptual content in the lecture. We
-therefore also compared the variances in topic weights (across time or
+therefore also compared the variances in topic weights (over time and across
 questions) between the lectures and questions. The variability in topic
-expression (over time and across questions) was similar for the Lecture~1 video
-and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the
+expression was similar for the Lecture~1 video
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$), and for the
 Lecture~2 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$=
@@
 
-While an individual lecture may be organized around a single broad theme at a
-coarse scale, at a finer scale, each moment of a lecture typically covers a
+An individual lecture may be organized around a single broad theme at a
+coarse scale, but at a finer scale, each moment of a lecture typically covers a
 narrower range of content. Given the correspondence we found between the
@@
 vectors were maximally correlated with a well-defined (and relatively narrow)
-range of timepoints from their corresponding lectures, and the correlations
-fell off sharply outside of that range (Supp.~Figs.~\forcesCorrs,~\bosCorrs).
+range of timepoints from their corresponding lectures, outside of which the
+correlations fell off sharply (Supp.~Figs.~\forcesCorrs,~\bosCorrs).
 We also qualitatively examined the best-matching intervals for each question by
-comparing the question's text to the transcribed text from the most-correlated parts of the
+comparing the questions' text to the transcribed text from the most-correlated parts of the
 lectures (Supp.~Tab.~\matchTab). Despite that the questions were excluded from
@@
 student ``knows'' about the content of a given lecture entail administering some form of assessment (e.g., a quiz) and computing the
-proportion of correctly answered questions. But if two students receive
-identical scores on such an exam, might our modeling framework help us to gain more
+proportion of questions the student answered correctly. But if two students receive
+identical scores on such an assessment, might our modeling framework help us to gain more
 nuanced insights into the \textit{specific} content that each student has
@@
 We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
-responses to a small set of multiple-choice questions to estimate how much the
+responses to a small set of multiple-choice questions to estimate how much that
 participant ``knows'' about the concept reflected by any arbitrary coordinate
@@
 we obtain a high-resolution snapshot (at the time each quiz was taken) of what
-the participants knew about any moment's content, from either of the two
+participants knew about any moment's content, from either of the two
 lectures they watched (comprising a total of 1,100 samples across the two
@@
     knowledge estimates are for the content of the \textit{Birth of Stars}
-    lecture. All panels: error ribbons and error bars denote 95\% confidence
+    lecture. \textbf{All panels.} Error ribbons and error bars denote 95\% confidence
     intervals, estimated across participants.}
@@
 Consistent with this prediction, we found no reliable differences in estimated
-knowledge about the \textit{Birth of Stars} lecture content on Quizzes~1 versus
-2 ($t(49) = 1.013,~p = 0.316$), but the estimated knowledge was substantially
+knowledge about the \textit{Birth of Stars} lecture content on Quiz~1 versus
+2 ($t(49) = 1.013,~p = 0.316$), but estimated knowledge was substantially
 higher on Quiz~3 versus 2 ($t(49) = 10.561,~p < 0.001$) and Quiz~3 versus 1
@@
 mixed model (GLMM) with a logistic link function to explain the probability of
-correctly answering a question as a function of estimated knowledge for its
+correctly answering a question as a function of estimated knowledge at its
 embedding coordinate, while accounting for varied effects of individual
@@
 \textit{other} lecture. This is an especially stringent test of our approach.
-Our primary assumption in building our knowledge estimates is that knowledge
+Our primary assumption in constructing our knowledge estimates is that knowledge
 about a given concept is similar to knowledge about other concepts that are
@@
 That the knowledge predictions derived from the text embedding space reliably
-distinguish between held-out correctly versus incorrectly answered questions
+distinguish between correctly and incorrectly answered held-out questions
 (Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
@@
 embedding space, how does the likelihood that the participant does \textit{not}
-know about a coordinate's content change with distance? We reasoned that,
+know about the content at a given coordinate change with distance? We reasoned that,
 assuming our embedding space is capturing something about how individuals
@@
 embedded very close to $x$ should tend to be similar to their ability to answer
-the question embedded \textit{at} $x$. Whereas at another extreme, once we
+the question embedded \textit{at} $x$. But once we
 reach some sufficiently large distance from $x$, our ability to infer whether
@@
 \textit{overall} proportion of correctly answered questions. In other words,
-beyond the maximum distance at which the participant's ability to answer the
+beyond the maximum distance at which a participant's ability to answer the
 question at $x$ is informative of their ability to answer a second question at
-location $y$, then guessing the outcome at $y$ based on $x$ should be no more
+location $y$, guessing the outcome at $y$ based on the outcome at $x$ should be no more
 successful than guessing based on a measure that does not consider
@@
 
-With these ideas in mind, we asked: conditioned on answering a question
-correctly, what proportion of all questions (within some radius, $r$, of that
-question's embedding coordinate) were answered correctly? We plotted this
-proportion as a function of $r$. Similarly, we could ask, conditioned on
-answering a question incorrectly, how the proportion of correct responses
-changed with $r$. As shown in Figure~\ref{fig:smoothness}, we found that quiz
-performance falls off smoothly with distance, and the ``rate'' of the falloff
-does not appear to change across the different quizzes, as measured by the
+With these ideas in mind, we asked: conditioned on a participant's ability to
+answer a given question correctly, what proportion of all questions within some
+radius $r$ of its embedding coordinate were they able to answer correctly? We
+plotted this proportion as a function of $r$ for questions that participants
+answered correctly, and for questions they answered incorrectly.
+As shown in Figure~\ref{fig:smoothness}, we found that quiz
+performance falls off smoothly with distance, and the ``rate'' at which it falls off
+does not appear to differ across quizzes, as measured by the
 distance at which performance becomes statistically indistinguishable from a
 simple proportion-correct score (see~\nameref{subsec:smoothness}). This
-suggests that, at least within the region of text embedding space covered by
-the questions our participants answered (and as characterized using our topic
+suggests that, at least within the region of text embedding space spanned by
+the questions our study's participants answered (and as characterized using our topic
 model), the rate at which knowledge changes with distance is relatively
 constant, even as participants' overall level of knowledge varies across
-quizzes or regions of the embedding space.
+quizzes and regions of the embedding space.
 
@@
 not precisely the same as) that contained in the two lectures used to train the
-model. We note that we used these 2D maps solely for visualization; all relevant
-comparisons, distance computations, and statistical tests we report above were
-carried out in the original 15-dimensional space, using the 15-topic model.
-Aside from increasing the number of topics from 15 to 100, all other procedures
+model. Aside from increasing the number of topics from 15 to 100, all other procedures
 and model parameters were carried over from the preceding analyses. As in our
@@
     \textbf{A. Average ``knowledge maps'' estimated using each quiz.} Each map
-    displays a 2D projection of the estimated knowledge about the content
+    displays a 2D projection of participants' estimated knowledge about the content
     reflected by \textit{all} regions of topic space (see
     \nameref{subsec:knowledge-maps}). The topic trajectories of the two
-    lectures are indicated by dotted lines (blue: Lecture 1; green: Lecture 2),
+    lectures are indicated by dotted lines (blue: Lecture~1; green: Lecture~2),
     and the coordinates of each question are indicated by dots (light blue:
-    Lecture 1-related; light green: Lecture 2-related; purple: general physics
+    Lecture~1-related; light green: Lecture~2-related; purple: general physics
     knowledge). Each map reflects an average across all participants. For
@@
     the words' relative sizes correspond to their relative weights at the
-    starred location, and their colors indicate their relative weights in
+    starred location, and their colors indicate their relative weights in the
     \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}
@@
 We projected the resulting 100-dimensional topic vectors (for each second of
-video and each quiz question) onto a shared 2-dimensional plane (see
+the lectures and each quiz question) onto a shared 2-dimensional plane (see
 \nameref{subsec:knowledge-maps}). Next, we sampled points from a $100 \times
 100$ grid of coordinates that evenly tiled a rectangle enclosing the 2D
-projections of the videos and questions. We used
+projections of the lectures and questions. We then used
 Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
@@
 model at the point in time when they completed that quiz. 
+We note that we used these 2D maps solely for visualization; all relevant
+comparisons, distance computations, and statistical tests we report above were
+carried out in the original 15-dimensional space, using the 15-topic model.
 
@@
 the knowledge maps estimated from responses to a successive pair of quizzes
-yields a \textit{learning map} that describes the \textit{change} in knowledge
-estimates from one quiz to the next. These learning maps highlight that the
+yields a \textit{learning map} that describes the \textit{change} in estimated
+knowledge from one quiz to the next. These learning maps highlight that the
 estimated knowledge increases we observed across maps were specific to the
@@
 the \textit{Birth of Stars} embedding (orange), and a third point between the
-two lectures' embeddings (pink). As shown in the word clouds in the panel, the
+two lectures' embeddings (pink). As shown in the word clouds in Panel C, the
 top-weighted words at the example coordinate near the \textit{Four Fundamental
@@
 the \textit{Birth of Stars} embedding tended to be weighted more heavily by the
-topics expressed in \textit{that} lecture. And the top-weighted words at the
+topics expressed in \textit{that} lecture. The top-weighted words at the
 example coordinate between the two lectures' embeddings show a roughly even mix
@@
 estimate moment-by-moment ``knowledge traces'' that reflect the degree of
-knowledge participants have about each video's time-varying content, and
+knowledge participants have about each lecture's time-varying content, and
 capture temporally specific increases in knowledge after viewing each lecture
-(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
+(Fig.~\ref{fig:knowledge-timeseries}). We then show that these knowledge
 estimates can generalize to held-out questions and predict participants'
@@
 our study shows that knowledge about a given concept implies knowledge about
-related concepts, and we also show how estimated knowledge falls off with
-distance in text embedding space.
+related concepts, and how far this implication extends in text embedding space.
 
 In our study, we characterize the ``coordinates'' of participants' knowledge
-using a relatively simple ``bag of words'' text embedding model~\citep[LDA;
+using a relatively simple ``bag-of-words'' text embedding model~\citep[LDA;
 ][]{BleiEtal03}. More sophisticated text embedding models, such as
@@
 our goal had been to choose a model that generalized to many different content 
-areas, we would expect our LDA model to perform comparatively poorly to BERT or 
+areas simultaneously, we would expect our LDA model to perform comparatively poorly to BERT or 
 other much larger general-purpose models. We suggest that bridging this tradeoff 
@@
 afford low resolution at the scale of individual course lectures and questions 
-because they ``zoom out'' too far, simpler word-matching measures yield low 
+because they ``zoom out'' too far, simpler word-matching measures afford low 
 resolution because they ``zoom \textit{in}'' too far. In this way, we view our 
@@
 generation of interactive tutoring systems that are able to adapt to learners'
-needs in real time, and that are able to provide more nuanced feedback about
+needs in real time, and provide more nuanced feedback about
 what learners know and what they do not know.
@@
 
-Within the past several years, the global pandemic forced many educators to
+Within the past several years, a global pandemic forced many educators to
 suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21,
@@
 Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II
-(18 participants); Biology, AP Biology; or High school Biology (15
-participants); Health and Medicine (1 participant); or other videos not listed
+(18 participants); Biology, AP Biology, or High school Biology (15
+participants); Health and Medicine (1 participant); and other videos not listed
 in our survey (5 participants). We also asked participants whether they had
@@
 participants reported that they had not watched the \textit{Four Fundamental
-Forces} video, and 1 participant reported that they were not sure whether they
+Forces} video and 1 participant reported that they were not sure whether they
 had watched it. All participants reported that they had not watched the
@@
 preparation (27 participants), Economics and finance (26 participants),
-Computing (14 participants), College and careers (7 participants), or other
+Computing (14 participants), College and careers (7 participants), and other
 courses not listed in our survey (6 participants).
@@
 then write a question about that concept. The general physics questions were
-drawn our team's prior coursework and areas of interest, along with internet
+drawn from our team's prior coursework and areas of interest, along with internet
 searches and brainstorming with the project team and other members of J.R.M.'s
@@
 understanding that each question ``requires'' to answer is somewhat subjective,
-and might even come down to the ``strategy'' a given participant uses to answer
+and might even come down to the ``strategy'' a given participant used to answer
 the question at that particular moment. The full set of questions and answer
@@
 representational space. Briefly, our approach uses a topic model~\citep[Latent
-Dirichlet Allocation; ][]{BleiEtal03} trained on a set of documents, to
+Dirichlet Allocation; ][]{BleiEtal03} trained on a set of documents to
 discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is
 defined as a distribution of weights over words in the model's vocabulary
-(i.e., the union of all unique words, across all documents, excluding ``stop
+(i.e., the union of all unique words across all documents, excluding ``stop
 words''). Conceptually, each topic is intended to give larger weights to words
@@
 the model's vocabulary, may be represented as a $k$-dimensional vector
-describing how much the document (most probably) reflects each topic. To select
+describing how much that document (most probably) reflects each topic. To select
 an appropriate $k$ for our model, as a starting point, we identified the
@@
 via YouTube, and when those lines would appear). We defined a sliding window
-length of (up to) $w = 30$ transcript lines, and assigned each window a
+length of (up to) $w = 30$ transcript lines and assigned each window a
 timestamp corresponding to the midpoint between the timestamps for its first
@@
 remaining words, and lasting for an average of 62.22~seconds. We treated the
-text from each sliding window as a single ``document,'' and combined these
+text from each sliding window as a single ``document'' and combined these
 documents across the two videos' windows to create a single training corpus for
@@
 
-After fitting a topic model to the two videos' transcripts, we could use the
+After fitting the topic model to the two videos' transcripts, we could use the
 trained model to transform arbitrary (potentially new) documents into

### 2025-05-24 paper/main.tex

@@
 All of the statistical tests performed in our study were two-sided. The 95\%
-confidence intervals we reported for each correlation were estimated from
+confidence intervals we report for each correlation were estimated from
 bootstrap distributions of 10,000 correlation coefficients obtained by
@@
 
-As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
-corpus of documents using overlapping sliding windows that span each video's
+As illustrated in Figure~\ref{fig:sliding-windows}A, we started by building up a
+corpus of documents using overlapping sliding windows that spanned each lecture's
 transcript. Khan Academy provides professionally created, manual transcriptions
-of all videos for closed captioning. However, such transcripts would not be
+of all lecture videos for closed captioning. However, such transcripts would not be
 readily available in all contexts to which our framework could potentially be
@@
 We fetched these automated transcripts using the
-\texttt{youtube-transcript-api} Python package~\citep{Depo18}. The transcripts
+\texttt{youtube-transcript-api} Python package~\citep{Depo18}. Each transcript
 consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
-standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
+standard deviation: 0.83~s) of spoken content in the lecture (i.e., corresponding
 to each individual caption that would appear on-screen if viewing the lecture
@@
 ``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
-``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
-remaining words, and lasting for an average of 62.22~seconds. We treated the
+``thing,'' and ``two.'' This yielded sliding windows containing an average of 73.8
+remaining words, and spanning an average of 62.22~seconds. We treated the
 text from each sliding window as a single ``document'' and combined these
-documents across the two videos' windows to create a single training corpus for
+documents across the two lectures' windows to create a single training corpus for
 the topic model.
 
-After fitting the topic model to the two videos' transcripts, we could use the
+After fitting the topic model to the two lectures' transcripts, we could use the
 trained model to transform arbitrary (potentially new) documents into
@@
 resulting time series to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (see Supp.~Tab.~\questions).
-Taken together, we obtained a \textit{trajectory} for each video, describing
+obtain topic vectors for each quiz question in our pool (see Supp.~Tab.~\questions).
+Taken together, we obtained a \textit{trajectory} for each lecture video, describing
 its path through topic space, and a single coordinate for each question
-(Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
+(Fig.~\ref{fig:sliding-windows}C). Embedding both lectures and all of the
 questions using a common model enables us to compare the content from different
-moments of videos, compare the content across videos, and estimate potential
-associations between specific questions and specific moments of video.
+moments of the lectures, compare the content across lectures, and estimate potential
+associations between specific questions and specific moments of lecture content.
 
@@
 and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
-correlations between any lecture timepoint and question, taken over all
+correlations between the topic vectors for any lecture timepoint and quiz question, taken over all
 timepoints in the given lecture and all questions \textit{about} that
@@
 $s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
-Here $t$ indexes the set of lecture topic vectors $L$, and $i$ and $j$ index
-the topic vectors of questions $Q$ used to estimate the knowledge trace. Note
+Here $t$ indexes the time series of lecture topic vectors $L$, and $i$ and $j$ index
+the topic vectors of questions $Q$ used to estimate the participant's knowledge. Note
 that ``$\mathrm{correct}$'' denotes the set of indices of the questions the
@@
 estimates we compute based on the quiz questions' embedding coordinates do
-\textit{not} provide useful information about participants' abilities to answer
+\textit{not} provide useful information about participants' abilities to correctly answer
 those questions---in other words, that there is no meaningful difference (on
 average) between the knowledge estimates we compute for questions participants
-answered correctly and those they answered incorrectly. Specifically, since we
+answered correctly versus incorrectly. Specifically, since we
 estimate knowledge for a given embedding coordinate as a weighted
@@
 \textit{unweighted} proportion of correctly answered questions used to compute
-them. In general, for a given participant and quiz, this expected value (i.e.,
+them. In general, for a given participant and quiz, this expected null value (i.e.,
 that participant's proportion-correct score on that quiz) is the same for any
@@
 single \textit{correctly} answered question as the target, the proportion of
-remaining questions answered correctly would be $\frac{n - 1}{q - 1}$. Whereas
+remaining questions answered correctly would be $\frac{n - 1}{q - 1}$, whereas
 if we hold out a single \textit{incorrectly} answered question, the proportion
@@
 
-To correct for this baseline inverse relationship between a participant's
-success on a target question and their estimated knowledge for it, we used a
+To correct for this baseline difference under our null hypothesis, we used a
 rebalancing procedure that ensured our knowledge estimates for questions each
@@
 \textit{same} proportion of correctly answered questions. For each target
-question on a given participant's quiz, we identified all remaining questions
+question on a given participant's quiz, we first identified all remaining questions
 with the opposite ``correctness'' label (i.e., if the target question was
@@
 correctly answered question and one incorrectly answered question from the
-participant's quiz, if the participant correctly answered $n$ out of $q$
+participant's quiz responses, if the participant correctly answered $n$ out of $q$
 questions total, then their proportion-correct score on each subset of questions
-used to estimate their knowledge for the target question is $\frac{n-1}{q-2}$,
+used to estimate their knowledge would be $\frac{n-1}{q-2}$,
 regardless of whether they answered the target question correctly or
-incorrectly. Finally, averaging over these per-subset knowledge estimates
-yielded a rebalanced estimate of the participant's knowledge for the target
+incorrectly. Finally, we averaged over these per-subset knowledge estimates
+to obtain a rebalanced estimate of the participant's knowledge for the target
 question that leveraged information from all remaining questions' embedding
@@
 observe between participants' estimated knowledge for individual quiz questions
-and their abilities to correctly answer them are attributable to the predictive
-power of the embedding-space distances used to weight questions' contributions
-to the knowledge estimates, rather than an artifact of our estimation procedure.
+and their abilities to correctly answer them reflect the predictive
+power of the embedding-space distances we use to weight questions' contributions
+to the knowledge estimates, rather than an artifact of our testing procedure.
 Note that if a participant answered all or no questions on a given quiz
@@
 questions did \textit{not} systematically differ, on average. Specifically, we
-used the same sets of observations with which we fit each ``full'' model to fit
-a second ``null'' model that had the same random effects structure, but in which
-the coefficient for the fixed effect of ''\texttt{knowledge}'' was fixed at 0
+used the same sets of observations to which we fit each ``full'' model to fit
+a second ``null'' model with the same random effects structure, but with
+the coefficient for the fixed effect of ''\texttt{knowledge}'' constrained to zero
 (i.e., we removed this term from the null model). We then compared each full
@@
 An important feature of our approach is that, given a trained text embedding
-model and participants' quiz performance on each question, we can estimate
+model and participants' performance on each quiz question, we can estimate
 their knowledge about \textit{any} content expressible by the embedding
@@
 question (i.e., we included one RBF for each question). At coordinate $x$, the
-value of an RBF centered on a question's coordinate $\mu$, is given by:
+value of an RBF centered on a question's coordinate $\mu$ is given by:
 \begin{equation}

### 2025-05-24 paper/supplement.tex

@@
 embeddings. This indicates that the LDA embeddings are capturing specific 
-``matches'' between individual quiz questions and relatively well defined time 
+``matches'' between individual quiz questions and relatively well-defined time 
 periods of lecture content, whereas the BERT embeddings appear to blur these 
@@
 subtle distinctions between concepts conveyed within the span of a single course 
-lecture, thereby affording a ``lower resolution'' depiction of its contents.
+lecture, thereby affording a ``lower-resolution'' depiction of its contents.
 
@@
 such superficial content matches in the more scattered, brief, and weak 
-``peaks'' they exhibit. As an example, panel E displays text of the two quiz 
+``peaks'' they exhibit. As an example, panel E displays the text of the two quiz 
 questions highlighted in green and purple in panels A through D, along with the 

### 2025-05-25 paper/main.tex
add a few more changes to main text

@@
 conceptual knowledge. Our approach embeds each concept in a high-dimensional
-representation space, where nearby coordinates reflect similar or related
+representation space where nearby coordinates reflect similar or related
 concepts. We test our approach using behavioral data from participants who
 answered small sets of multiple-choice quiz questions interleaved between
-watching two course videos from the Khan Academy platform. We apply our
+watching two Khan Academy course videos. We apply our
 framework to the videos' transcripts and the text of the quiz questions to
@@
 this claim. For each quiz question a participant answered, in turn, we used
-Equation~\ref{eqn:prop} to estimate their knowledge at the given question's
+Equation~\ref{eqn:prop} to estimate their knowledge at that question's
 embedding-space coordinate based on other questions that participant answered
@@
 participants' knowledge for each quiz question. First, we estimated knowledge
-at each question's embedding coordinate using \textit{all} other questions
+at each held-out question's embedding coordinate using \textit{all} other questions
 answered by the same participant on the same quiz (``All questions'';
@@
 We observed a similar set of results when we restricted our estimates of
-participants' knowledge for questions about each lecture to consider only
+participants' knowledge to consider only
 their performance on other questions about the \textit{same} lecture.
@@
 Stars}-related questions ($OR = 9.775,\ 95\%\ \textnormal{CI} = [2.93,\
-25.08],\ \lambda_{LR} = 13.924,\ p = 0.001$). These within-lecture knowledge
-estimates also predicted success on questions about both lectures when we
-computed them analogously for Quiz~2 (\textit{Four Fundamental Forces}: $OR =
+25.08],\ \lambda_{LR} = 13.924,\ p = 0.001$). These results also held for
+participants' Quiz~2 responses (\textit{Four Fundamental Forces}: $OR =
 35.126,\ 95\%\ \textnormal{CI} = [5.113,\ 123.868],\ \lambda_{LR} = 32.251,\
 p < 0.001$; \textit{Birth of Stars}: $OR = 4.717,\ 95\%\ \textnormal{CI} =
-[2.021,\ 9.844],\ \lambda_{LR} = 16.788,\ p < 0.001$). For Quiz~3, we found that
-within-lecture knowledge estimates predicted participants' success on
-\textit{Birth of Stars}-related questions ($OR = 16.902,\ 95\%\ \textnormal{CI}
-= [3.353,\ 53.265],\ \lambda_{LR} = 23.233,\ p < 0.001$) but not on \textit{Four
-Fundamental Forces}-related questions ($OR = 2.485,\ 95\%\ \textnormal{CI} =
-[0.724,\ 8.366],\ \lambda_{LR} = 1.984,\ p = 0.170$). This may indicate that the
-within-lecture knowledge estimates are susceptible to ceiling effects in
+[2.021,\ 9.844],\ \lambda_{LR} = 16.788,\ p < 0.001$) and partially for 
+their Quiz~3 responses (\textit{Birth of Stars}: $OR = 16.902,\ 95\%\ 
+\textnormal{CI} = [3.353,\ 53.265],\ \lambda_{LR} = 23.233,\ p < 0.001$; 
+\textit{Four Fundamental Forces}: $OR = 2.485,\ 95\%\ \textnormal{CI} =
+[0.724,\ 8.366],\ \lambda_{LR} = 1.984,\ p = 0.170$). Speculatively, the Quiz~3 
+results suggest that the within-lecture knowledge estimates may be 
+susceptible to ceiling effects in
 participants' quiz performance. On Quiz~3, after viewing both lectures, no
@@
 fewer incorrectly. (This was the only subset of questions about either lecture, 
-across all three quizzes, for which this was true.) Because of this, for 90\% of 
+across all three quizzes, for which this was true.) Consequently, for 90\% of 
 participants, our within-lecture estimates of their knowledge for \textit{Four 
@@
 distinguish them from the far more numerous aspects of the lecture content they 
-now \textit{did} know about. Taken together, these results suggest that our 
+now \textit{did} know about. Taken together, these within-lecture results suggest that our 
 knowledge estimates can reliably distinguish between questions about different
@@
 
-Finally, we estimated participants' knowledge for each question about one
-lecture using their performance on questions (from the same quiz) about the
+Finally, we estimated participants' knowledge for each question about each
+lecture using only their performance on questions (from the same quiz) about the
 \textit{other} lecture. This is an especially stringent test of our approach.
@@
 distinguish between correctly and incorrectly answered held-out questions
-(Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
+(Fig.~\ref{fig:predictions}) suggests that geometric relationships within this
 space can help explain what participants know. But how far does this
@@
 the domain of physics lectures and questions) \textit{and} sufficiently broad 
-as to enable them to cover a wide range of domains. Essentially, these 
-``larger'' language models learn these more complex features of language through 
+as to enable them to cover a wide range of domains. Essentially, 
+``larger'' language models learn more complex features of language through 
 training on enormous and diverse text corpora. But as a result, their 
@@
 when we are specifically interested in capturing subtle conceptual differences 
-at the level of a single course lecture or quiz question. On the other hand, if 
+at the level of a single, narrowly focused course lecture or quiz question. On the other hand, if 
 our goal had been to choose a model that generalized to many different content 
@@
 other much larger general-purpose models. We suggest that bridging this tradeoff 
-between high resolution within a single content area and the ability to 
+between achieving high resolution within a single content area and the ability to 
 generalize to many diverse content areas will be an important challenge for 
@@
 analogous matches based on the Jaccard similarity between each question's text 
-and each sliding window from the corresponding lecture's transcript. Similarly 
-to the embeddings derived from BERT, we found that this approach also blurred 
+and each sliding window from the corresponding lecture's transcript. As for 
+the embeddings derived from BERT, we found that this word-matching approach also blurred 
 meaningful distinctions between concepts presented in different parts of each 
